---
title: "Lagginess Index"
author: "Evelyn Sanchez"
date: "2/27/2020"
output:
  html_document: default
---
```{r setup, include=FALSE}
# Define the working directory for the entire markdown file to enable relative path
knitr::opts_knit$set(root.dir = "/Users/eves/Dropbox/LATAM_WorldBank")
```

```{r, message=FALSE}
#load libraries
library(BAMMtools)
library(BBmisc)
library(classInt)
library(cowplot)
library(data.table)
library(doBy)
library(foreign)
library(ggplot2)
library(mapproj)
library(maptools)
library(plyr)
library(dplyr)
library(raster)
library(rgeos)
library(RColorBrewer)
library(rgdal)
library(shapefiles)
library(sp)
library(stringr)
library(tidyr)
library(tidyverse)
library(viridis)
library(viridisLite)
library(readstata13)
```

1. Load and merge required databases

Define path
```{r, message=FALSE}
#Set working directories
dir_shp <- "./Boundaries/LATAM/"                     #Confirm path
dir_shp_country <- "./Boundaries/BOL/"               #Confirm path
dir_cap <- "./Boundaries/Capitals/"                  #Confirm path
dir_raw <- "./Index/Raw/"                            #Confirm path
dir_mrk <- "./Index/BOL/Output/"                     #Confirm path
dir_out <- "./Index/BOL/Output2/"                    #Confirm path
dir_fig <- "./Index/BOL/Maps/"                       #Confirm path

#confirm working directory
getwd()
```

Read HDD data set (which includes Poverty, Nightlights, Disaster Risk and other indicators)
```{r, message=FALSE}
data_base<- read.csv(paste0(dir_raw, "Index_base_032020.csv"),  header=TRUE)     #Confirm filename
```

Transform and rename variables of interest
```{r}
#transform variables to numeric type
data_base$y230<- as.numeric(as.character(data_base$y230))
data_base$y207<- as.numeric(as.character(data_base$y207))
data_base$y36<- as.numeric(as.character(data_base$y36))
data_base$y9<- as.numeric(as.character(data_base$y9))
data_base$VIIRS<- as.numeric(as.character(data_base$VIIRS))

#set variables names
colnames(data_base)[colnames(data_base)=="y207"] <- "area_sqkm2"
colnames(data_base)[colnames(data_base)=="y230"] <- "water_sh"
colnames(data_base)[colnames(data_base)=="y34"] <- "forest_km"
colnames(data_base)[colnames(data_base)=="y32"] <- "flood_num"
```

Process Nightlight data 
```{r}
#Nighlights by area (VIIRS_dens2)
data_base$VIIRS_d_km= data_base$VIIRS/data_base$area_sqkm2

#Nightlights per capita (VIIRS_pc)
data_base$VIIRS_pc= data_base$VIIRS/data_base$Pop

#Generate inverse value of nighlights 
#Total nighlights inv_VIIRS
data_base$inv_VIIRS= 1/data_base$VIIRS
#Nighlights per capita (inv_VIIRS_pc)
data_base$inv_VIIRS_pc= 1/(data_base$VIIRS_pc+1)

#Check inv_VIIRS_pc mean
mean(data_base$inv_VIIRS_pc, na.rm= TRUE)
```
Filter data for the country of interest (Example: Bolivia)
```{r}
data_country <- data_base[data_base$ISO == "BOL", ] 
```

Load Market Access Index and join with HDD data set (generated in the First Step)
```{r}
# Load dataset 
Market_country <- read.csv(paste0(dir_mrk, "MKT_Access_BOL_Stats.csv"),  header=TRUE)  #Confirm filename

#Subset Market Access data
Market_country<-Market_country%>%
  dplyr::select(TARGET_FID, median, mean)
colnames(Market_country)[colnames(Market_country)=="median"] <- "Acc_median"
colnames(Market_country)[colnames(Market_country)=="mean"] <- "Acc_mean"

#Merge using "TARGET_FID"
data_country<- data_country %>% left_join(Market_country, by="TARGET_FID")
```

Calculate inverse value of Market Access
```{r}
data_country$inv_Acc_median= 1/(data_country$Acc_median+1)
```

2. Lagginess index calculation
 
Calculate z-score for poverty, nightlights and market access
```{r, warning= FALSE}
#Eliminate all inf values generate by 1/var dividisions
data_country[sapply(data_country, is.infinite)] <- NA

#Select variables of interest
vars<-c("poor_ppp55", "inv_VIIRS", "inv_VIIRS_pc", "inv_Acc_median")

#Save data_country as back up dataset
index_all<-data_country

#Calculate mean, median and sd for the z-score
index_all<- index_all%>%
  group_by(NAME_0) %>%
   dplyr::mutate_at(.funs = funs(z=(. - mean(., na.rm=TRUE))/sd(., na.rm=TRUE)), .vars=vars)
```

Add z-scores to create lagginess index
```{r}
index_all <- mutate(index_all, z_score_den = poor_ppp55_z
                                     + inv_Acc_median_z
                                     + inv_VIIRS_pc_z)

mean(index_all$z_score_den, na.rm=TRUE)
sd(index_all$z_score_den, na.rm=TRUE)

#Get Max and Min values per country
index_all<-index_all%>%
  group_by(NAME_0)%>%
  dplyr::mutate(z_max_den = max(z_score_den, na.rm = TRUE), z_min_den = min(z_score_den, na.rm = TRUE))

#Compute lagging index
index_all <- dplyr::mutate(index_all, L_Index_den = 100*(z_score_den - z_min_den)/(z_max_den-z_min_den))
```

Calculate lagginess areas
```{r}
#Get the top 40 percentile 
top_40per<- quantile(index_all$L_Index_den, probs = 0.6)

#Define lagging areas based on the top 40 percentile
index_all<-index_all %>% 
  mutate(top40_de = ifelse( L_Index_den >= top_40per, "1", "0"))

#Eliminate all inf values generate by 1/var dividisions
index_all[sapply(index_all, is.infinite)] <- NA
```

Calculate proportion of resources in lagging areas
```{r}
#Transfor variables for calculation
index_all$water_km<- index_all$area_sqkm2*index_all$water_sh*100
index_all$risk_area[is.na(index_all$risk_area)] <- 0

#Calculate share of forest, land, people, biodiversity, and high risk between Lagging and non-Lagging areas
share_data<-index_all%>% 
  dplyr::group_by(top40_de)%>% 
  summarise(sum_forest_km=sum(forest_km),                                 #Forest
            sum_land_km=sum(area_sqkm2),                                  #Area
            sum_pop=sum(Pop),                                             #Pop
            sum_water_km=sum(water_km),                                   #Water
            sum_bio_km=sum(bio_area),                                     #Biodiversity
            sum_risk_km=sum(risk_area),                                   #Risk area
            sum_flood= sum(flood_num)                                     #Number of floods
            )%>%
  mutate(forest_sh = sum_forest_km/sum(sum_forest_km), 
         land_sh = sum_land_km/sum(sum_land_km),
         pop_sh= sum_pop/sum(sum_pop),
         water_sh_t=sum_water_km/sum(sum_water_km), 
         biod_sh_t=sum_bio_km/sum(sum_bio_km),
         risk_sh_t=sum_risk_km/sum(sum_risk_km),
         flood_sh_t=sum_flood/sum(sum_flood)
         )

share_data$top40_de[share_data$top40_de == 1]<- "Lagging"
share_data$top40_de[share_data$top40_de == 0]<- "Non_Lagging"

#Save proportions
write.csv(share_data, paste(dir_out, "Share_prop_GTM.csv", sep=""), row.names = FALSE)

```

#3. Map indicators

Load shapefiles 
```{r}
#Country shapefile
shape <- readOGR(dsn = dir_shp_country, layer = "Bolivia") %>%                                #Change filename
  spTransform(crs("+proj=longlat +datum=WGS84 +no_defs"))

#LATAM Region shapefile
reg_shape <- readOGR(dsn = dir_shp, layer = "LATAM_Boundaries") %>%                            #Change filename
  spTransform(crs("+proj=longlat +datum=WGS84 +no_defs"))

#Subset municipalities surrounding  #Chang
border_country <- reg_shape[reg_shape@data$TARGET_FID %in% c("25", "18", "17", "115", "97","104", "105", "94", "147", "134","136", "444", "449", "455", "440","474", "475", "478", "480", "482", "460", "464"), ] 

# Fortify borders (surrounding districts only)
border_country <- fortify(border_country, region="TARGET_FID") %>%    
  mutate(id=as.numeric(id))
```

Add capital layers
```{r}
#Capitals Names, shapefile
capitals <- readOGR(dsn = dir_cap, layer = "Capitals") %>%          #Change filename
  spTransform(crs("+proj=longlat +datum=WGS84 +no_defs"))

capitals<-capitals@data%>%
  dplyr::select("NAME", "ADM0_A3", "UN_FID", "UN_LAT", "UN_LONG")

#capital_filter_u <- capitals[capitals$ADM0_A3 %in% c("GTM", "SLV"),]
capital_filter <- capitals[capitals$ADM0_A3 == "BOL", ]
#Correct lat and long for the capital
capital_filter$UN_LAT<-  -16.50
capital_filter$UN_LONG<- -68.1333
```

Natural breaks function 
```{r}
#Use for natural breaks variables
breaks_fun <- function(var_in, breaks=7, dig=2){
  # Classifiy the data based on natural breaks. Using Fisher (more efficient than Jenks)
  fish_brk <- classIntervals(var_in, n=breaks, style="fisher")
  fish_brk$brks <- round(fish_brk$brks, digits = dig)
  # Use the breaks from above to decide the break points
  var_in <- round(var_in, digits = dig)
  var_out <- cut(var_in, breaks = c(fish_brk$brks), dig.lab = 7, include.lowest = TRUE, include.highest = TRUE)
  return(var_out)
}
```

Mapping preparation
```{r}
#Establish theme for map
theme_map <- function(...) {
  theme_classic() +
    theme(
      text = element_text(color = "#22211d"),
      axis.line = element_blank(),
      axis.text.x = element_blank(),
      axis.text.y = element_blank(),
      axis.ticks = element_blank(),
      axis.title.x = element_blank(),
      axis.title.y = element_blank(),
      plot.title = element_text(hjust = 0.5),
      plot.subtitle = element_text(hjust = 0.5),
      plot.caption = element_text(hjust = 0.5),
      ...
    )
}
```

##Funcion to map
Mapping function with country boundaries 

```{r}
#Assign directory for maps with country borders
dir_fig_coutry_B <-  paste0(dir_fig, "Country_B/")                                          

map_fun_test <- function(shape, index, TITLE, var_discrete=TRUE, break_type = "fisher", dir=dir_fig_coutry_B, breaks=BREAKS){
  
     if (break_type=="Lag_index") {
    index$map_var_brk <- cut(index$map_var, 
                             breaks = c(0, 20, 40, 60, 80, 100), 
                             labels = LABELS, 
                             include.lowest = TRUE)
     } else if (break_type=="manual") {
    index$map_var_brk <- cut(index$map_var, 
                             breaks = BREAKS, 
                             labels = LABELS, 
                             include.lowest = TRUE)
        } else {
          if (length(unique(index$map_var))<=5) {
            index$map_var_brk <- breaks_fun(index$map_var, breaks=4, dig=4)
          } else {
              index$map_var_brk <- breaks_fun(index$map_var, breaks=5, dig=4)
            }
        }

  
  names(COLOR) <- levels(index$map_var_brk)
  
  shape_fort <- fortify(shape, region="TARGET_FID") %>%                                      #Change varname
  mutate(id=as.numeric(id))
  
  
  colnames(index)[colnames(index)=="TARGET_FID"] <- "id"                                    #Change varname
  index$id <- as.character(index$id)
  shape_fort$id <- as.character(shape_fort$id)
  map_data <- shape_fort %>% left_join(index, by= "id")
  
#Zoom in/out area
  x_E <- max(shape_fort$long) +.02
  x_W <- min(shape_fort$long) -.2
  y_N <- max(shape_fort$lat)+ 0.2
  y_S <- min(shape_fort$lat)- 0.2
      
  map <- ggplot() +   
    geom_polygon(data= border_country, 
                     aes(x=long, y = lat, group = group), fill = "gray60", alpha=0.5, 
                 color="gray30", size= 0.1) +
    geom_polygon(data = map_data, aes(fill = map_var_brk, 
                                      x = long, 
                                      y = lat, 
                                      group = group), color = "black", size = 0.3) +
    geom_point(data=capital_filter, aes(x=UN_LONG, 
                                          y=UN_LAT), color="black", size= 1, pch = 16)+       #Adjust text position 
    geom_text(data = capital_filter, aes(UN_LONG, UN_LAT, label = NAME), size = 3, hjust= .15 ,vjust=-.9,  
              fontface=2)+
    coord_map(
      xlim = c(x_W, x_E), ylim = c(y_S, y_N)
      ) +
    theme_map() + 
    labs(x = NULL, 
         y = NULL, 
         title = TITLE, 
         subtitle = SOURCE, 
         caption = NOTE) +
    scale_fill_manual(name=LEGEND,
                      values=COLOR, na.value="#CBCBCB",
                      labels= LABELS,
                     # drop = F,
                      guide = guide_legend(
                        keyheight = unit(5, units = "mm"),
                        keywidth = unit(7, units = "mm"),
                        title.position = 'top',
                        reverse= F,
                        title.hjust = 0.2,
                        label.hjust = 0.5))


  map
  ggsave(paste(dir, paste0(TITLE, ".png"), sep = ""), height=6, width = 8, units = c("in"))
}
```

Mapping function with NO country boundaries
```{r}
#Assign directory for maps with country borders
dir_fig_coutry_NB <-  paste0(dir_fig, "Country_NB/")            

#Mapping function
map_fun_test_nb <- function(shape, index, TITLE, var_discrete=TRUE, break_type = "fisher", dir=dir_fig_coutry_NB, breaks=BREAKS){
  
     if (break_type=="Lag_index") {
    index$map_var_brk <- cut(index$map_var, 
                             breaks = c(0, 20, 40, 60, 80, 100), 
                             labels = LABELS, 
                             include.lowest = TRUE)
     } else if (break_type=="manual") {
    index$map_var_brk <- cut(index$map_var, 
                             breaks = BREAKS, 
                             labels = LABELS, 
                             include.lowest = TRUE)
        } else {
          if (length(unique(index$map_var))<=5) {
            index$map_var_brk <- breaks_fun(index$map_var, breaks=4, dig=4)
          } else {
              index$map_var_brk <- breaks_fun(index$map_var, breaks=5, dig=4)
            }
        }

  
  names(COLOR) <- levels(index$map_var_brk)
  
  shape_fort <- fortify(shape, region="TARGET_FID") %>%                                      #Change varname
  mutate(id=as.numeric(id))
  
  
  colnames(index)[colnames(index)=="TARGET_FID"] <- "id"                                    #Change varname
  index$id <- as.character(index$id)
  shape_fort$id <- as.character(shape_fort$id)
  map_data <- shape_fort %>% left_join(index, by= "id")
  
#Zoom in/out area
  x_E <- max(shape_fort$long) +.02
  x_W <- min(shape_fort$long) -.2
  y_N <- max(shape_fort$lat)+ 0.2
  y_S <- min(shape_fort$lat)- 0.2
      
  map <- ggplot() +   
    geom_polygon(data = map_data, aes(fill = map_var_brk, 
                                      x = long, 
                                      y = lat, 
                                      group = group), color = "black", size = 0.3) +
    geom_point(data=capital_filter, aes(x=UN_LONG, 
                                          y=UN_LAT), color="black", size= 1, pch = 16)+
    geom_text(data = capital_filter, aes(UN_LONG, UN_LAT, label = NAME), size = 3, hjust= .15 ,vjust=-.9,
              fontface=2)+
    coord_map(
      xlim = c(x_W, x_E), ylim = c(y_S, y_N)
      ) +
    theme_map() + 
    labs(x = NULL, 
         y = NULL, 
         title = TITLE, 
         subtitle = SOURCE, 
         caption = NOTE) +
    scale_fill_manual(name=LEGEND,
                      values=COLOR, na.value="#CBCBCB",
                      labels= LABELS,
                     # drop = F,
                      guide = guide_legend(
                        keyheight = unit(5, units = "mm"),
                        keywidth = unit(7, units = "mm"),
                        title.position = 'top',
                        reverse= F,
                        title.hjust = 0.2,
                        label.hjust = 0.5))


  map
  ggsave(paste(dir, paste0(TITLE, "NB.png"), sep = ""), height=6, width = 8, units = c("in"))
}
```

Premapping preparation 
```{r}
#Transform forest from km to proportion for better mapping
index_all$forest_sh<-(index_all$forest_km*100)/index_all$area_sqkm2

#Database for mapping should be named "indices"
indices<-index_all
```

```{r, warning=FALSE}
#Lagging regions

LEGEND <- "Lagginess Index"
SOURCE <- ""
NOTE <- "Note: Lagging areas present low economic density, scarce market accessibility,\n and high poverty rates."
LABELS <-c("0 to 20", "20 to 40", "40 to 60", "60 to 80", "80 to 100")
indices$map_var <- indices$L_Index_den
COLOR <- (brewer.pal(5,"YlGnBu"))
map_fun_test(shape, index = indices, TITLE = "Lagginess Index ", break_type= "Lag_index")
map_fun_test_nb(shape, index = indices, TITLE = "Lagginess Index ", break_type= "Lag_index")
```

```{r, warning=FALSE}
#Forest coverage
LEGEND <- "Forest Coverage"
SOURCE <- ""
NOTE <- "Note: Forest share per region."
BREAKS<- c(0, 40, 60, 80, 100)
LABELS <-c("< 40% ", "40% to 60%", "60% to 80%", "> 80%")
indices$map_var <- indices$forest_sh
COLOR <- brewer.pal(4,"Greens")
map_fun_test(shape, index = indices, TITLE = "Forest Coverage"  , 
             break_type= "manual"
             )
map_fun_test_nb(shape, index = indices, TITLE = "Forest Coverage", break_type= "manual" )

#sort(indices$forest_sh)
```

```{r, warning=FALSE}
LEGEND <- "Poverty Rate \n USD 5.5 per day"
SOURCE <- "Source: HDD Dataset"
NOTE <- "Note: Share of individuals below the 5.5 USD PPP Poverty Line."
BREAKS <- c(0, .2, .3, .4, .5)
LABELS <- c("< 20%","20% to 30%", "30% to 40%", "40% to 50%")
indices$map_var <- indices$poor_ppp55 
COLOR <- brewer.pal(5,"Reds")
map_fun_test_nb(shape, index = indices, TITLE = "Poverty Rate " ,
                break_type= "manual"
                )
map_fun_test(shape, index = indices, TITLE = "Poverty Rate ",break_type= "manual")

#sort(indices$poor_ppp55) 
```

```{r, warning=FALSE}
indices$Pop_dens<-format(round(indices$Pop_dens, 1), nsmall = 1)
indices$Pop_dens<-as.numeric(as.character(indices$Pop_dens))
LEGEND <- "Population Density \n   ppl/sqkm"
SOURCE <- "Source: World Pop, 2015"
NOTE <- "Note: Number of people per square kilometer"
BREAKS <- c(0, 5, 10, 20, 30, 40)
LABELS <-  c("<5", "5 to 10", "10 to 20", "20 to 30", "> 30")
  #Use LABELS<- waiver() in case you want to use the natural breaks values 
indices$map_var <- indices$Pop_dens
COLOR <- brewer.pal(5,"RdPu")
map_fun_test(shape, index = indices, TITLE = "Population Density",
             break_type= "manual"
             )
map_fun_test_nb(shape, index = indices, TITLE = "Population Density", 
                break_type= "manual"
                )
#sort(indices$Pop_dens)
```

```{r, warning=FALSE}
LEGEND <- "Market Access"
SOURCE <- "Source: World Bank"
NOTE <- "Note: Proxy of market accessibility based on the travel time to \n nearest markets (main cities), weighted by population."
LABELS <- c("Low", "","Medium",  "", "High")
indices$map_var <- indices$Acc_median
COLOR <- brewer.pal(5,"BuPu")
map_fun_test(shape, index = indices, TITLE = "Market Access")
map_fun_test_nb(shape, index = indices, TITLE = "Market Access")

```

```{r, warning=FALSE}
#Per capita
LEGEND <- "NTL per capita"
SOURCE <- "Source: NASA VIIRS, 2016"
NOTE <- "Note: Nighttime Lights (NTL) per capita. \n Total NTL value weighted by total population"
LABELS <-c("Very Low", "Low", "Medium", "High", "Very High")
indices$map_var <- indices$VIIRS_pc 
COLOR <- brewer.pal(5,"Purples")
map_fun_test(shape, index = indices, TITLE = "Economic Activity per capita")
map_fun_test_nb(shape, index = indices, TITLE = "Economic Activity per capita")


#Total nightlights
LEGEND <- "Economic activity"
SOURCE <- "Source: NASA VIIRS, 2016"
NOTE <- "Note: Total Nighttime Lights (NTL). \n Higher level of NTL indicates higher economic activity"
LABELS <-c("Very Low", "Low", "Medium", "High", "Very High")
indices$map_var <- indices$VIIRS 
COLOR <- brewer.pal(5,"Purples")
map_fun_test(shape, index = indices, TITLE = "Economic Activity")
map_fun_test_nb(shape, index = indices, TITLE = "Economic Activity")
```

#4.Clean data  and save it (shapefile/csv)
```{r, warning=FALSE}

index_all$TARGET_FID<-as.character(as.numeric(index_all$TARGET_FID))

index_nd<-c("OBJECTID", "Join_Count", "NAME_0", "NAME_1", "HASC_1",  "HASC_1", "HASC_1", "TYPE_1", "ENGTYPE_1", "Area", "year_sur") 
index_all_red<-index_all %>% 
  dplyr::select(-index_nd)


#Merge data with shapefile
newobj <- merge(shape, index_all_red, by.x="TARGET_FID", by.y="TARGET_FID")


#Change names to make them vissible in the shapefile (the number of characters  are limited in shapefile format)
#colnames(newobj@data)

colnames(newobj@data)[colnames(newobj@data)=="L_Index_den"] <- "Indx_den"
colnames(newobj@data)[colnames(newobj@data)=="inv_Acc_median"] <- "inAccMed"
colnames(newobj@data)[colnames(newobj@data)=="VIIRS_d_km"] <- "VIIRkm"
colnames(newobj@data)[colnames(newobj@data)=="VIIRS_pc"] <- "VIIRpc"
colnames(newobj@data)[colnames(newobj@data)=="inv_VIIRS_pc"] <- "inVIIRpc"
colnames(newobj@data)[colnames(newobj@data)=="inv_VIIRS"] <- "inVIIR"
colnames(newobj@data)[colnames(newobj@data)=="inv_Acc_median"] <- "inAccMd"

#Save shapefile
writeOGR(newobj, dsn = dir_out, layer = "BOL_Index", driver="ESRI Shapefile", overwrite_layer=TRUE)

Index<-newobj@data

#colnames(Index)
#Save in csv
write.csv(Index, paste(dir_out, "BOL_Index.csv", sep=""), row.names = FALSE)

```
