---
title: "Benchmarking_Graphs"
author: "Giuseppe Rossitti & Evelyn Sanchez"
date: "12/05/2020"
output: html_document
---

```{r setup, include=FALSE}
#knitr::opts_knit$set(root.dir = "C:/Users/####/OneDrive/")
knitr::opts_knit$set(root.dir = "/Users/eves/Dropbox/MENA/Data/Benchmarking2/")
```

```{r}
library(WDI)
library(dplyr)
library(readxl)
library(xml2)
library(rvest)
library(tidyverse)
library(data.table)
library(ggplot2)
library(grid)
library(lattice)
library(survival)
library(Formula)
library(Hmisc)
#detach(package:plyr) 
```

# Set Directories
```{r}
dir_int<-"./Integrated data/" #Folder with data generated in code Benchmarking_Data_V2
#dir_out<- "./Data/Benchmarking/SD_Profiles/Output/"              
dir_out<-"./Output/"
#In your coumputer, this directory create  separate folders for income group - ex: ./My Files/Output/lmic -./My Files/Output/umic, etc, in oder to save countries info per income group
getwd()
```

# PART 1
## CREATE PILLARS SCORES DEPENDING ON THE METHODOLOGY VERSION

#From this point the selection of indicators will produce different results

Two version of the bench marking are generated with the following code:
##v0 
Refers to a set of indicators selected and vetted by the Chief Economist Office -Sustainable Development (work led by Jason Daniel Russ). This version is updated with the criteria from November 30, 2020
##v1
Refers to a set of indicators selected by the MENA - Sustainable Development team focusing on Egypt analysis 
## v9 (MoPED)
Refers to a set of indicators selected by the MoPED (Ministry of Planning and Economic Development) in Egypt
##v2
Refers to an expanded set of indicators selected by the MENA - Sustainable Development team focusing on Egypt analysis

##v8 - Morocco
Refers to an expanded set of indicators selected by the MENA - Sustainable Development team focusing on Morocco analysis. Differences in Efficienct indicators: Global Competitiviness Index instead of Logistic Perfomance Index and addition of Maternal Mortality rate

The order of chunks has been changed to accomodate the loops that will change the V2 variable names to include the subcategory, for example (R1), in front of the name


#Set comparators -INCOME GROUP and REGIONAL GROUP and VERSION
```{r}
#Income group (select same category)
group <- 'lmics' ### HERE CHOOSE INCOME GROUP WE WANT TO COMPARE TO FROM ABOVE VARIABES ###

country="MAR"  #use one country for tests

#Set files names to read according to comparison groups

comparison_percentile <- paste0('DB_SD_',group,'_score')
comparison_score <- paste0('DB_SD_',group,'_score')

### Version indicator
#choose 0, 1 or 20. 
#v= 0 Refers to a set of indicators selected and vetted by the Chief Economist Office -Sustainable Development (work lead by Jason Daniel Russ)
# v=1 refers to a set of indicators selected by the MENA - Sustainable Development team focusing on Egypt results 
#Each version would show a different set of indicators
#v=9 refers to a set of indicators selected by the Egyptian MoPED - Ministry of Planning and Economic Development
#v=8 refers to a set of indicators selected by Morocco Team - Differences in Efficienct indicators: Global Competitiviness Index instead of Logistic Perfomance Index and addition of Maternal Mortality rate

version <- 2 #  0,1,2 or 9 for MoPED indicators
```


#Set text size for graphs to be smaller in Version 2
```{r}
if (version != 2){
  perctext <- 3.5
  pillartext <- 4.5
 
} else {
  perctext <-1.5
 pillartext <- 3
}
```


#Calculate Pillars aggregate measures from the indicators (Global calculation)

```{r}
#Retreive database with all the variables generated in "Benchmarking_V3"

integrated3 <- read.csv(paste0(dir_int, "World_SD_values_V5.csv"))

# For each version add all indicators

base <- c("country","iso3","income","region")

v0 <- c("risk_wellbeing", "risk_to_assets", "food_sec", "pop_dis", "rain_exp", "EN.POP.SLUM.UR.ZS", "pov_1016", 'SL.TLF.CACT.FE.ZS',"SH.STA.SMSS.ZS", "SH.H2O.SMDW.ZS", "HD.HCI.OVRL", "SI.POV.GINI", "SE.SEC.ENRR", "SH.IMM.IDPT", "account.t.d.7", "LGBT_acc", "wbl", "trust_ppl", "ref_idp", "conf_gov", "NY.ADJ.SVNG.GN.ZS", "EN.ATM.PM25.MC.M3", "EG.FEC.RNEW.ZS", "ER.H2O.INTR.PC","wat_qua", "WWT.new" ,"forest_loss","agri_value", "agri_land", "gdp_ghg", "gov_effect", "cont_corr", "lpi_score", "sdg9_intuse", "water_efficiency_ceo", "Tenure.insecurity" )
v0_per <- paste(v0, "_per", sep='')

v1 <- c("risk_wellbeing", "risk_to_assets", "food_sec", "pop_dis", "rain_exp", "EN.POP.SLUM.UR.ZS", "pov_1016", 'SL.TLF.CACT.FE.ZS',"SH.STA.SMSS.ZS", "SH.H2O.SMDW.ZS", "HD.HCI.OVRL", "SI.POV.GINI", "SE.SEC.ENRR", "SH.IMM.IDPT", "account.t.d.7", "LGBT_acc", "wbl", "trust_ppl", "ref_idp", "sec_aparat", "conf_gov", "EN.ATM.PM25.MC.M3", "EG.FEC.RNEW.ZS", "ER.H2O.INTR.PC","wat_qua", "WWT.new", "waste_rate", "waste_managed", "BHV.new", "FSH.new", "GIB.new", "EN.ATM.CO2E.PC" , "forest_loss", "agri_value", "agri_land", "gdp_ghg", "gov_effect", "cont_corr", "lpi_score", "sdg9_intuse", "water_efficiency_FAO", "Tenure.insecurity")
v1_per <- paste(v1, "_per", sep='')


v2 <- c("pop_dis", "rain_exp", "pov_1016", 'SL.TLF.CACT.FE.ZS', "HD.HCI.OVRL", "SI.POV.GINI", "SE.SEC.ENRR", "SH.IMM.IDPT", "account.t.d.7", "LGBT_acc", "wbl", "ref_idp", "EN.ATM.PM25.MC.M3", "EG.FEC.RNEW.ZS","wat_qua", "WWT.new", "waste_rate", "waste_managed", "BHV.new", "FSH.new", "EN.ATM.CO2E.PC" , "forest_loss", "agri_value", "agri_land", "gdp_ghg", "gov_effect", "cont_corr", "lpi_score", "water_efficiency_ceo", "SG.GEN.PARL.ZS",
"SH.MED.PHYS.ZS", "SH.UHC.SRVS.CV.XD", "acc_sani_SDG", "acc_water_SDG", "rai", "rule_law", "IT.CEL.SETS.P2", "IT.NET.USER.ZS", "rapid_trans", "displaced", "wat_stress_SDG", "glob_hunger_index", "terror", "pop_slums_SDG", "heal_01_NDG", "habi_01_NDG", "habi_02_NDG", "infr_02_NDG", "food_03_NDG", "infr_03_NDG", "heal_03_NDG", "SH.STA.AIRP.P5","SH.STA.WASH.P5","fao_withdraw_pc","ecos_04_NDG","chloroph_SDG","EG.ELC.ACCS.ZS","reg_qua","ghg_pc","pop_epid","patents","IS.SHP.GCNW.XQ","dai", "EG.EGY.PRIM.PP.KD")

v2_per <- paste(v2, "_per", sep='')

v8 <- c("pop_dis", "rain_exp", "pov_1016", 'SL.TLF.CACT.FE.ZS', "HD.HCI.OVRL", "SI.POV.GINI", "SE.SEC.ENRR", "SH.IMM.IDPT", "account.t.d.7", "LGBT_acc", "wbl", "ref_idp", "EN.ATM.PM25.MC.M3", "EG.FEC.RNEW.ZS","wat_qua", "WWT.new", "waste_rate", "waste_managed", "BHV.new", "FSH.new", "EN.ATM.CO2E.PC" , "forest_loss", "agri_value", "agri_land", "gdp_ghg", "gov_effect", "cont_corr", "water_efficiency_ceo", "SG.GEN.PARL.ZS",
"SH.MED.PHYS.ZS", "SH.UHC.SRVS.CV.XD", "acc_sani_SDG", "acc_water_SDG", "rai", "rule_law", "IT.CEL.SETS.P2", "IT.NET.USER.ZS", "rapid_trans", "displaced", "wat_stress_SDG", "glob_hunger_index", "terror", "pop_slums_SDG", "heal_01_NDG", "habi_01_NDG", "habi_02_NDG", "infr_02_NDG", "food_03_NDG", "infr_03_NDG", "heal_03_NDG", "SH.STA.AIRP.P5","SH.STA.WASH.P5","fao_withdraw_pc","ecos_04_NDG","chloroph_SDG","EG.ELC.ACCS.ZS","reg_qua","ghg_pc","pop_epid","patents","IS.SHP.GCNW.XQ","dai", "EG.EGY.PRIM.PP.KD", "gci", 'SH.STA.MMRT' )

v8_per <- paste(v8, "_per", sep='')


v9 <- c("food_sec",   "EN.POP.SLUM.UR.ZS", "SH.STA.TRAF.P5", "gdpgr_1519" ,"u_1519","infl_1519","hepat_SDG", "pov_1016", "SL.TLF.CACT.FE.ZS","acc_sani_SDG","acc_water_SDG", "SI.POV.GINI", "EG.ELC.ACCS.ZS", "SI.POV.NAHC", "SG.GEN.PARL.ZS","wom_manage_SDG", "FX.OWN.TOTL.FE.ZS" , "per_si_allsi.cov_pop_tot", "SE.ADT.LITR.FE.ZS" , "WWT.new", "waste_rate", "waste_managed", "BHV.new", "EN.ATM.CO2E.PP.GD", "sdg9_intuse", "debt_gdp_IMF", "capstock_imf", "gov_spe_edu_SDG", "balance_imf", "taxrev_imf","you_neet_1317","smes_wom")

v9_per <- paste(v9, "_per", sep='')


# Subset the database based on the indicators used in each version

if (version == 0){
  integrated3 <- subset(integrated3, select = c(base,v0,v0_per))
} else {
  if (version == 1) {
  integrated3 <- subset(integrated3, select = c(base,v1,v1_per))
  } else {
      if (version == 2) {
  integrated3 <- subset(integrated3, select = c(base,v2,v2_per))
  } else {
      if (version == 8) {
  integrated3 <- subset(integrated3, select = c(base,v8,v8_per))
  } else {
  integrated3 <- subset(integrated3, select = c(base,v9,v9_per))
}}}}  




#V0 Resilience (same set v0 and v1)
if (version==0){
integrated3<-mutate(integrated3, Resilience_v0 = rowMeans(select(integrated3, c("risk_wellbeing_per", "risk_to_assets_per", "food_sec_per", "pop_dis_per", "rain_exp_per", "EN.POP.SLUM.UR.ZS_per")), na.rm = TRUE))

#V0 Inclusion Indicators not included compared with V1: "sec_aparat" (Security Apparatus) 
integrated3<-mutate(integrated3, Inclusion_v0 = rowMeans(select(integrated3, c("pov_1016_per", 'SL.TLF.CACT.FE.ZS_per',"SH.STA.SMSS.ZS_per", "SH.H2O.SMDW.ZS_per", "HD.HCI.OVRL_per", "SI.POV.GINI_per", "SE.SEC.ENRR_per", "SH.IMM.IDPT_per", "account.t.d.7_per", "LGBT_acc_per", "wbl_per", "trust_ppl_per", "ref_idp_per", "conf_gov_per")), na.rm = TRUE))

#V0 Sustainability Indicators not included compared with V1: ,"waste_managed_per, BHV_new_per", "FSH_new_per", "GIB_new_per", "EN.ATM.CO2E.PC_per", "waste_rate_per"
#Note, forest loss is excluded when the country has very low levels of forest loss

integrated3<-mutate(integrated3, Sustainability_v0 = rowMeans(select(integrated3, c("NY.ADJ.SVNG.GN.ZS_per", "EN.ATM.PM25.MC.M3_per", "EG.FEC.RNEW.ZS_per", "ER.H2O.INTR.PC_per","wat_qua_per", "WWT.new_per" ,"forest_loss_per" )), na.rm = TRUE))

#V0 Efficiency use water_efficiency_ceo - GDP/(waterwithdral*10*9) (calculated in this code- aqua dataframe)
#Other indicators not included: "reg_qua_per"

integrated3<-mutate(integrated3, Efficiency_v0 = rowMeans(select(integrated3, c("agri_value_per", "agri_land_per", "gdp_ghg_per", "gov_effect_per", "cont_corr_per", "lpi_score_per", "sdg9_intuse_per", "water_efficiency_ceo_per", "Tenure.insecurity_per")), na.rm = TRUE))
} else {
  if (version == 1) {
    #V1 Resilience
integrated3<-mutate(integrated3, Resilience_v1 = rowMeans(select(integrated3, c("risk_wellbeing_per", "risk_to_assets_per", "food_sec_per", "pop_dis_per", "rain_exp_per", "EN.POP.SLUM.UR.ZS_per")), na.rm = TRUE))
  
  #V1 Inclusion
integrated3<-mutate(integrated3, Inclusion_v1 = rowMeans(select(integrated3, c("pov_1016_per", 'SL.TLF.CACT.FE.ZS_per',"SH.STA.SMSS.ZS_per", "SH.H2O.SMDW.ZS_per", "HD.HCI.OVRL_per", "SI.POV.GINI_per", "SE.SEC.ENRR_per", "SH.IMM.IDPT_per", "account.t.d.7_per", "LGBT_acc_per", "wbl_per", "trust_ppl_per", "ref_idp_per", "sec_aparat_per", "conf_gov_per")), na.rm = TRUE))

# V1 Sustainability Indicators not included compared with V0: "NY.ADJ.SVNG.GN.ZS_per"
#Note, forest loss is excluded when the country has very low levels of forest loss
integrated3<-mutate(integrated3, Sustainability_v1 = rowMeans(select(integrated3, c("EN.ATM.PM25.MC.M3_per", "EG.FEC.RNEW.ZS_per", "ER.H2O.INTR.PC_per","wat_qua_per", "WWT.new_per", "waste_rate_per", "waste_managed_per", "BHV.new_per", "FSH.new_per", "GIB.new_per", "EN.ATM.CO2E.PC_per" , "forest_loss_per")), na.rm = TRUE))

#v1 Efficiency use water_efficiency_FAO_per, value added per water withdrawn, expressed in USD/m3 from FAO (details also in this code)
#Other indicators not included: "reg_qua_per"
integrated3<-mutate(integrated3, Efficiency_v1 = rowMeans(select(integrated3, c("agri_value_per", "agri_land_per", "gdp_ghg_per", "gov_effect_per", "cont_corr_per", "lpi_score_per", "sdg9_intuse_per", "water_efficiency_FAO_per", "Tenure.insecurity_per")), na.rm = TRUE))
} else {
  if (version == 2) {

    #V2 Resilience
integrated3<-mutate(integrated3, Resilience_v2 = rowMeans(select(integrated3, c( "pop_dis_per", "rain_exp_per", "pop_epid_per", "pop_slums_SDG_per", "displaced_per" , "terror_per" , "heal_01_NDG_per" , "habi_01_NDG_per",  "habi_02_NDG_per",   "infr_02_NDG_per","infr_03_NDG_per" ,  "food_03_NDG_per",  "SH.MED.PHYS.ZS_per", "heal_03_NDG_per" ,"glob_hunger_index_per","wat_stress_SDG_per" )), na.rm = TRUE))
                                                                 
  
  #V2 Inclusion
integrated3<-mutate(integrated3, Inclusion_v2 = rowMeans(select(integrated3, c("pov_1016_per", 'SL.TLF.CACT.FE.ZS_per', "HD.HCI.OVRL_per", "SI.POV.GINI_per", "SE.SEC.ENRR_per", "SH.IMM.IDPT_per", "account.t.d.7_per", "LGBT_acc_per", "wbl_per",  "ref_idp_per", "SG.GEN.PARL.ZS_per","rai_per" ,"acc_sani_SDG_per", "acc_water_SDG_per","SH.UHC.SRVS.CV.XD_per", "EG.ELC.ACCS.ZS_per" )), na.rm = TRUE))

# V2 Sustainability 
integrated3<-mutate(integrated3, Sustainability_v2 = rowMeans(select(integrated3, c("EN.ATM.PM25.MC.M3_per", "EG.FEC.RNEW.ZS_per", "wat_qua_per", "WWT.new_per", "waste_rate_per", "waste_managed_per", "BHV.new_per", "FSH.new_per", "ghg_pc_per", "EN.ATM.CO2E.PC_per" , "forest_loss_per", "SH.STA.AIRP.P5_per" , "SH.STA.WASH.P5_per", "ecos_04_NDG_per", "chloroph_SDG_per", "fao_withdraw_pc_per" )), na.rm = TRUE))

#v2 Efficiency 
integrated3<-mutate(integrated3, Efficiency_v2 = rowMeans(select(integrated3, c("agri_value_per", "agri_land_per", "gdp_ghg_per", "gov_effect_per", "cont_corr_per", "lpi_score_per",  "water_efficiency_ceo_per","rule_law_per" , "IT.CEL.SETS.P2_per", "IT.NET.USER.ZS_per","rapid_trans_per" ,"EG.EGY.PRIM.PP.KD_per" , "reg_qua_per","patents_per","IS.SHP.GCNW.XQ_per","dai_per")), na.rm = TRUE))  
} else {
if (version == 8) {

    #V8 Resilience
integrated3<-mutate(integrated3, Resilience_v8 = rowMeans(select(integrated3, c( "pop_dis_per", "rain_exp_per", "pop_epid_per", "pop_slums_SDG_per", "displaced_per" , "terror_per" , "heal_01_NDG_per" , "habi_01_NDG_per",  "habi_02_NDG_per",   "infr_02_NDG_per","infr_03_NDG_per" ,  "food_03_NDG_per",  "SH.MED.PHYS.ZS_per", "heal_03_NDG_per" ,"glob_hunger_index_per","wat_stress_SDG_per" )), na.rm = TRUE))
  
  #V8 Inclusion
integrated3<-mutate(integrated3, Inclusion_v8 = rowMeans(select(integrated3, c("pov_1016_per", 'SL.TLF.CACT.FE.ZS_per', "HD.HCI.OVRL_per", "SI.POV.GINI_per", "SE.SEC.ENRR_per", "SH.IMM.IDPT_per", "account.t.d.7_per", "LGBT_acc_per", "wbl_per",  "ref_idp_per", "SG.GEN.PARL.ZS_per","rai_per" ,"acc_sani_SDG_per", "acc_water_SDG_per","SH.UHC.SRVS.CV.XD_per", "EG.ELC.ACCS.ZS_per" )), na.rm = TRUE))

# V8 Sustainability 
integrated3<-mutate(integrated3, Sustainability_v8 = rowMeans(select(integrated3, c("EN.ATM.PM25.MC.M3_per", "EG.FEC.RNEW.ZS_per", "wat_qua_per", "WWT.new_per", "waste_rate_per", "waste_managed_per", "BHV.new_per", "FSH.new_per", "ghg_pc_per", "EN.ATM.CO2E.PC_per" , "forest_loss_per", "SH.STA.AIRP.P5_per" , "SH.STA.WASH.P5_per", "ecos_04_NDG_per", "chloroph_SDG_per", "fao_withdraw_pc_per" )), na.rm = TRUE))

#v8 Efficiency 
integrated3<-mutate(integrated3, Efficiency_v8 = rowMeans(select(integrated3, c("agri_value_per", "agri_land_per", "gdp_ghg_per", "gov_effect_per", "cont_corr_per", "gci_per",  "water_efficiency_ceo_per","rule_law_per" , "IT.CEL.SETS.P2_per", "IT.NET.USER.ZS_per","rapid_trans_per", "EG.EGY.PRIM.PP.KD_per", "reg_qua_per","patents_per","IS.SHP.GCNW.XQ_per","dai_per", 'SH.STA.MMRT_per')), na.rm = TRUE)) 
    
    
} else {

#v9 (MoPED) Resilience
integrated3<-mutate(integrated3, Resilience_v9 = rowMeans(select(integrated3, c( "food_sec_per",   "EN.POP.SLUM.UR.ZS_per", "SH.STA.TRAF.P5_per", "gdpgr_1519_per","u_1519_per","infl_1519_per","hepat_SDG_per")), na.rm = TRUE))

#MoPED Inclusion
integrated3<-mutate(integrated3, Inclusion_v9 = rowMeans(select(integrated3, c("pov_1016_per", 'SL.TLF.CACT.FE.ZS_per',"acc_sani_SDG_per","acc_water_SDG_per" , "SI.POV.GINI_per", "EG.ELC.ACCS.ZS_per", "SI.POV.NAHC_per", "SG.GEN.PARL.ZS_per","wom_manage_SDG_per", "FX.OWN.TOTL.FE.ZS_per" , "per_si_allsi.cov_pop_tot_per", "SE.ADT.LITR.FE.ZS_per","you_neet_1317_per","smes_wom_per" )), na.rm = TRUE))

# MoPED Sustainability
integrated3<-mutate(integrated3, Sustainability_v9 = rowMeans(select(integrated3, c("WWT.new_per", "waste_rate_per", "waste_managed_per", "BHV.new_per", "EN.ATM.CO2E.PP.GD_per")), na.rm = TRUE))

# MoPED Efficiency
integrated3<-mutate(integrated3, Efficiency_v9 = rowMeans(select(integrated3, c("sdg9_intuse_per", "debt_gdp_IMF_per", "capstock_imf_per", "gov_spe_edu_SDG_per", "balance_imf_per", "taxrev_imf_per")), na.rm = TRUE))

}}}}


#Save all the database with raw values and percentile data (worldwide data)
write.csv(integrated3, paste0(dir_int, "World_SD_values_V5_index_v",version,".csv"), row.names = FALSE)
```



# Part II - GRAPHING INDICADORS
If the composition of the pillars for each version doesn't change, start running the code from here.
Last update of the indicators list for the two versions: Dec 5, 2020


#Dataset creation 
```{r}
# Load country dataset to create list of countries per income group that we will used in the loop

country_estimates_global <- read.csv(paste0(dir_int,"World_SD_values_V5_index_v",version,".csv"))

# Lower MICS
country_estimates <- country_estimates_global %>% filter(income=='Lower middle income')
lmics <- unique(country_estimates$iso3)
lmics <- as.character(lmics)

# Low income
country_estimates <- country_estimates_global %>% filter(income=='Low income')
lics <- unique(country_estimates$iso3)
lics <- as.character(lics)

# Upper MICS
country_estimates <- country_estimates_global %>% filter(income=='Upper middle income')
umics <- unique(country_estimates$iso3)
umics <- as.character(umics)

# High Income
country_estimates <- country_estimates_global %>% filter(income=='High income')
hics <- unique(country_estimates$iso3)
hics <- as.character(hics)

```




# Country Percentil dataset: clean and prepare 
Here we rename the variables of the raw values and the percentile ranking (all variables from the two versions)
```{r}
### COUNTRY Percentile DATASET ### 
###         World              ###

#Load raw and percentile value data generated before 
country_all <- read.csv(paste0(dir_int,"World_SD_values_V5_index_v",version,".csv"))


##country_all$pop_dis<-as.numeric(as.character(country_all$pop_dis))
##country_all$pop_dis<-format(round(country_all$pop_dis, 2), nsmall = 2)


if (version==2){
  
  ###V2 Names include subcategory for alphabetical order  
  
#Resilience
colnames(country_all)<-str_replace(colnames(country_all), "glob_hunger_index", "(R3) *Global Hunger Index")
colnames(country_all)<-str_replace(colnames(country_all), "terror", "(R3) *Deaths from conflict and terrorism (per 100,000)")
colnames(country_all)<-str_replace(colnames(country_all), "pop_dis", "(R1) *Population affected by disasters %")
colnames(country_all)<-str_replace(colnames(country_all), "pop_slums_SDG", "(R3) *Proportion of urban population living in slums")
colnames(country_all)<-str_replace(colnames(country_all), "rain_exp", "(R1) *Rainfall shock exposure %")
colnames(country_all)<-str_replace(colnames(country_all), "pop_epid", "(R3) *Population exposed to epidemics (per 100,000)")
colnames(country_all)<-str_replace(colnames(country_all), "heal_01_NDG", "(R2) *Projected change of deaths from climate change induced diseases")
colnames(country_all)<-str_replace(colnames(country_all), "habi_01_NDG", "(R2) *Projected change of warm periods")
colnames(country_all)<-str_replace(colnames(country_all), "habi_02_NDG", "(R2) *Projected change of flood hazard")
colnames(country_all)<-str_replace(colnames(country_all), "heal_03_NDG", "(R4) *Dependency on external resource for health services")
colnames(country_all)<-str_replace(colnames(country_all), "food_03_NDG", "(R4) *Food import dependency")
colnames(country_all)<-str_replace(colnames(country_all), "infr_02_NDG", "(R2) *Projected change of sea level rise impacts")
colnames(country_all)<-str_replace(colnames(country_all), "infr_03_NDG", "(R4) *Dependency on imported energy")
colnames(country_all)<-str_replace(colnames(country_all), "displaced", "(R1) *IDPs due to natural disasters (cases per 100,000)")
colnames(country_all)<-str_replace(colnames(country_all), "wat_stress_SDG", "(R1) *Water Stress SDG 6.4")
colnames(country_all)<-str_replace(colnames(country_all), "SH.MED.PHYS.ZS", "(R4) Physicians (per 1,000 people)")


#Inclusion
colnames(country_all)<-str_replace(colnames(country_all), "pov_1016", "(I1) *Extreme poverty headcount %")
colnames(country_all)<-str_replace(colnames(country_all), "SL.TLF.CACT.FE.ZS", "(I2) Female labor participation %")
colnames(country_all)<-str_replace(colnames(country_all), "HD.HCI.OVRL", "(I3) Human Capital Index")
colnames(country_all)<-str_replace(colnames(country_all), "SI.POV.GINI", "(I1) *Gini Index")
colnames(country_all)<-str_replace(colnames(country_all), "SE.SEC.ENRR", "(I3) Secondary school enrollment %")
colnames(country_all)<-str_replace(colnames(country_all), "SH.IMM.IDPT", "(I3) Immunization DPT %")
colnames(country_all)<-str_replace(colnames(country_all), "account.t.d.7", "(I1) Account ownership (poorest 40%)")
colnames(country_all)<-str_replace(colnames(country_all), "LGBT_acc", "(I2) LGBT Acceptance Index")
colnames(country_all)<-str_replace(colnames(country_all), "wbl", "(I2) Women, Business & Law Index")
colnames(country_all)<-str_replace(colnames(country_all), "ref_idp", "(I1) *Refugees & IDPs index")
colnames(country_all)<-str_replace(colnames(country_all), "SG.GEN.PARL.ZS", "(I2) Women in national parliaments %")
colnames(country_all)<-str_replace(colnames(country_all), "EG.ELC.ACCS.ZS", "(I4) Access to electricity %")
colnames(country_all)<-str_replace(colnames(country_all), "acc_sani_SDG", "(I4) Basic access to sanitation %")
colnames(country_all)<-str_replace(colnames(country_all), "acc_water_SDG", "(I4) Basic access to water %")
colnames(country_all)<-str_replace(colnames(country_all), "rai", "(I4) Rural Access Index")
colnames(country_all)<-str_replace(colnames(country_all), "SH.UHC.SRVS.CV.XD", "(I3) Universal health coverage (UHC) index %")



#Sustainability
colnames(country_all)<-str_replace(colnames(country_all), "EN.ATM.PM25.MC.M3", "(S1) *PM2.5 mean annual exposure (\U00B5g/m3)")
colnames(country_all)<-str_replace(colnames(country_all), "forest_loss", "(S4) *Forest loss %")
colnames(country_all)<-str_replace(colnames(country_all), "EG.FEC.RNEW.ZS", "(S3) Renewable energy consumption %")
colnames(country_all)<-str_replace(colnames(country_all), "wat_qua", "(S3) Water Quality SDG 6.3")
colnames(country_all)<-str_replace(colnames(country_all), "WWT.new", "(S2) Wastewater treated (primary) %")
colnames(country_all)<-str_replace(colnames(country_all), "waste_managed", "(S2) Solid waste properly disposed %")
colnames(country_all)<-str_replace(colnames(country_all), "waste_rate", "(S2) *Municipal solid waste (kg/pc/day)")
colnames(country_all)<-str_replace(colnames(country_all), "BHV.new", "(S4) Biodiversity Habitat Index")
colnames(country_all)<-str_replace(colnames(country_all), "FSH.new", "(S4) Fisheries Index")
colnames(country_all)<-str_replace(colnames(country_all), "ghg_pc", "(S1) *GHG emissions per capita (% change)")
colnames(country_all)<-str_replace(colnames(country_all), "EN.ATM.CO2E.PC", "(S1) *CO2 emissions (MT pc)")
colnames(country_all)<-str_replace(colnames(country_all), "ecos_04_NDG", "(S3) *Ecological Footprint")
colnames(country_all)<-str_replace(colnames(country_all), "fao_withdraw_pc", "(S3) *Water withdrawal per capita (m3/year pc)")
colnames(country_all)<-str_replace(colnames(country_all), "chloroph_SDG", "(S4) *Chlorophyll-a deviations in coastal water %")
colnames(country_all)<-str_replace(colnames(country_all), "SH.STA.AIRP.P5", "(S1) *Mortality due to air pollution (per 100,000)")
colnames(country_all)<-str_replace(colnames(country_all), "SH.STA.WASH.P5", "(S2) *Mortality due to unsafe WASH services (per 100,000)")


#Efficiency
colnames(country_all)<-str_replace(colnames(country_all), "agri_land", "(E4) Agri. land productivity ($/ha)")
colnames(country_all)<-str_replace(colnames(country_all), "agri_value", "(E1) Agri. value added per worker")
colnames(country_all)<-str_replace(colnames(country_all), "gdp_ghg", "(E4) Total GDP/GHG emissions")
colnames(country_all)<-str_replace(colnames(country_all), "gov_effect", "(E2) Governance effectiveness")
colnames(country_all)<-str_replace(colnames(country_all), "cont_corr", "(E2) Control of corruption")
colnames(country_all)<-str_replace(colnames(country_all), "reg_qua", "(E2) Regulatory quality")
colnames(country_all)<-str_replace(colnames(country_all), "lpi_score", "(E1) Logistic Performance Index")
colnames(country_all)<-str_replace(colnames(country_all), "IT.NET.USER.ZS", "(E3) Individuals using internet %")
colnames(country_all)<-str_replace(colnames(country_all), "IT.CEL.SETS.P2", "(E3) Mobile cellular subscriptions (per 100 people)")
colnames(country_all)<-str_replace(colnames(country_all), "rule_law", "(E2) Rule of law")
colnames(country_all)<-str_replace(colnames(country_all), "rapid_trans", "(E3) Rapid transit to resident ratio (km/million)")
colnames(country_all)<-str_replace(colnames(country_all), "EG.EGY.PRIM.PP.KD", "(E4) *Energy intensity (MJ/$)")
colnames(country_all)<-str_replace(colnames(country_all), "patents", "(E1) Patents (per 100,000 people)")  
colnames(country_all)<-str_replace(colnames(country_all), "dai", "(E1) Digital Penetration Index")  
colnames(country_all)<-str_replace(colnames(country_all), "water_efficiency_ceo", "(E4) Water productivity (GDP/m3)")
colnames(country_all)<-str_replace(colnames(country_all), "IS.SHP.GCNW.XQ", "(E3) Shipping connectivity index")
colnames(country_all)<-str_replace(colnames(country_all), "SH.STA.MMRT", "(E4) *Maternal mortality (per 100,000 live births)")


} else {
if (version == 8) {
  
  ###V2 Names include subcategory for alphabetical order  
  
#Resilience
colnames(country_all)<-str_replace(colnames(country_all), "glob_hunger_index", "(R3) *Global Hunger Index")
colnames(country_all)<-str_replace(colnames(country_all), "terror", "(R3) *Deaths from conflict and terrorism (per 100,000)")
colnames(country_all)<-str_replace(colnames(country_all), "pop_dis", "(R1) *Population affected by disasters %")
colnames(country_all)<-str_replace(colnames(country_all), "pop_slums_SDG", "(R3) *Proportion of urban population living in slums")
colnames(country_all)<-str_replace(colnames(country_all), "rain_exp", "(R1) *Rainfall shock exposure %")
colnames(country_all)<-str_replace(colnames(country_all), "pop_epid", "(R3) *Population exposed to epidemics (per 100,000)")
colnames(country_all)<-str_replace(colnames(country_all), "heal_01_NDG", "(R2) *Projected change of deaths from climate change induced diseases")
colnames(country_all)<-str_replace(colnames(country_all), "habi_01_NDG", "(R2) *Projected change of warm periods")
colnames(country_all)<-str_replace(colnames(country_all), "habi_02_NDG", "(R2) *Projected change of flood hazard")
colnames(country_all)<-str_replace(colnames(country_all), "heal_03_NDG", "(R4) *Dependency on external resource for health services")
colnames(country_all)<-str_replace(colnames(country_all), "food_03_NDG", "(R4) *Food import dependency")
colnames(country_all)<-str_replace(colnames(country_all), "infr_02_NDG", "(R2) *Projected change of sea level rise impacts")
colnames(country_all)<-str_replace(colnames(country_all), "infr_03_NDG", "(R4) *Dependency on imported energy")
colnames(country_all)<-str_replace(colnames(country_all), "displaced", "(R1) *IDPs due to natural disasters (cases per 100,000)")
colnames(country_all)<-str_replace(colnames(country_all), "wat_stress_SDG", "(R1) *Water Stress SDG 6.4")
colnames(country_all)<-str_replace(colnames(country_all), "SH.MED.PHYS.ZS", "(R4) Physicians (per 1,000 people)")


#Inclusion
colnames(country_all)<-str_replace(colnames(country_all), "pov_1016", "(I1) *Extreme poverty headcount %")
colnames(country_all)<-str_replace(colnames(country_all), "SL.TLF.CACT.FE.ZS", "(I2) Female labor participation %")
colnames(country_all)<-str_replace(colnames(country_all), "HD.HCI.OVRL", "(I3) Human Capital Index")
colnames(country_all)<-str_replace(colnames(country_all), "SI.POV.GINI", "(I1) *Gini Index")
colnames(country_all)<-str_replace(colnames(country_all), "SE.SEC.ENRR", "(I3) Secondary school enrollment %")
colnames(country_all)<-str_replace(colnames(country_all), "SH.IMM.IDPT", "(I3) Immunization DPT %")
colnames(country_all)<-str_replace(colnames(country_all), "account.t.d.7", "(I1) Account ownership (poorest 40%)")
colnames(country_all)<-str_replace(colnames(country_all), "LGBT_acc", "(I2) LGBT Acceptance Index")
colnames(country_all)<-str_replace(colnames(country_all), "wbl", "(I2) Women, Business & Law Index")
colnames(country_all)<-str_replace(colnames(country_all), "ref_idp", "(I1) *Refugees & IDPs index")
colnames(country_all)<-str_replace(colnames(country_all), "SG.GEN.PARL.ZS", "(I2) Women in national parliaments %")
colnames(country_all)<-str_replace(colnames(country_all), "EG.ELC.ACCS.ZS", "(I4) Access to electricity %")
colnames(country_all)<-str_replace(colnames(country_all), "acc_sani_SDG", "(I4) Basic access to sanitation %")
colnames(country_all)<-str_replace(colnames(country_all), "acc_water_SDG", "(I4) Basic access to water %")
colnames(country_all)<-str_replace(colnames(country_all), "rai", "(I4) Rural Access Index")
colnames(country_all)<-str_replace(colnames(country_all), "SH.UHC.SRVS.CV.XD", "(I3) Universal health coverage (UHC) index %")


#Sustainability
colnames(country_all)<-str_replace(colnames(country_all), "EN.ATM.PM25.MC.M3", "(S1) *PM2.5 mean annual exposure (\U00B5g/m3)")
colnames(country_all)<-str_replace(colnames(country_all), "forest_loss", "(S4) *Forest loss %")
colnames(country_all)<-str_replace(colnames(country_all), "EG.FEC.RNEW.ZS", "(S3) Renewable energy consumption %")
colnames(country_all)<-str_replace(colnames(country_all), "wat_qua", "(S3) Water Quality SDG 6.3")
colnames(country_all)<-str_replace(colnames(country_all), "WWT.new", "(S2) Wastewater treated (primary) %")
colnames(country_all)<-str_replace(colnames(country_all), "waste_managed", "(S2) Solid waste properly disposed %")
colnames(country_all)<-str_replace(colnames(country_all), "waste_rate", "(S2) *Municipal solid waste (kg/pc/day)")
colnames(country_all)<-str_replace(colnames(country_all), "BHV.new", "(S4) Biodiversity Habitat Index")
colnames(country_all)<-str_replace(colnames(country_all), "FSH.new", "(S4) Fisheries Index")
colnames(country_all)<-str_replace(colnames(country_all), "ghg_pc", "(S1) *GHG emissions per capita (% change)")
colnames(country_all)<-str_replace(colnames(country_all), "EN.ATM.CO2E.PC", "(S1) *CO2 emissions (MT pc)")
colnames(country_all)<-str_replace(colnames(country_all), "ecos_04_NDG", "(S3) *Ecological Footprint")
colnames(country_all)<-str_replace(colnames(country_all), "fao_withdraw_pc", "(S3) *Water withdrawal per capita (m3/year pc)")
colnames(country_all)<-str_replace(colnames(country_all), "chloroph_SDG", "(S4) *Chlorophyll-a deviations in coastal water %")
colnames(country_all)<-str_replace(colnames(country_all), "SH.STA.AIRP.P5", "(S1) *Mortality due to air pollution (per 100,000)")
colnames(country_all)<-str_replace(colnames(country_all), "SH.STA.WASH.P5", "(S2) *Mortality due to unsafe WASH services (per 100,000)")


#Efficiency
colnames(country_all)<-str_replace(colnames(country_all), "agri_land", "(E4) Agri. land productivity ($/ha)")
colnames(country_all)<-str_replace(colnames(country_all), "agri_value", "(E1) Agri. value added per worker")
colnames(country_all)<-str_replace(colnames(country_all), "gdp_ghg", "(E4) Total GDP/GHG emissions")
colnames(country_all)<-str_replace(colnames(country_all), "gov_effect", "(E2) Governance effectiveness")
colnames(country_all)<-str_replace(colnames(country_all), "cont_corr", "(E2) Control of corruption")
colnames(country_all)<-str_replace(colnames(country_all), "reg_qua", "(E2) Regulatory quality")
colnames(country_all)<-str_replace(colnames(country_all), "gci", "(E1) Global Competitiveness Index")
colnames(country_all)<-str_replace(colnames(country_all), "IT.NET.USER.ZS", "(E3) Individuals using internet %")
colnames(country_all)<-str_replace(colnames(country_all), "IT.CEL.SETS.P2", "(E3) Mobile cellular subscriptions (per 100 people)")
colnames(country_all)<-str_replace(colnames(country_all), "rule_law", "(E2) Rule of law")
colnames(country_all)<-str_replace(colnames(country_all), "rapid_trans", "(E3) Rapid transit to resident ratio (km/million)")
colnames(country_all)<-str_replace(colnames(country_all), "EG.EGY.PRIM.PP.KD", "(E4) *Energy intensity (MJ/$)")
colnames(country_all)<-str_replace(colnames(country_all), "patents", "(E1) Patents (per 100,000 people)")  
colnames(country_all)<-str_replace(colnames(country_all), "dai", "(E1) Digital Penetration Index")  
colnames(country_all)<-str_replace(colnames(country_all), "water_efficiency_ceo", "(E4) Water productivity (GDP/m3)")
colnames(country_all)<-str_replace(colnames(country_all), "IS.SHP.GCNW.XQ", "(E3) Shipping connectivity index")
colnames(country_all)<-str_replace(colnames(country_all), "SH.STA.MMRT", "(E4) *Maternal mortality (per 100,000 live births)")

} else {
  

#Assign names to variables
#Resilience
colnames(country_all)<-str_replace(colnames(country_all), "food_sec", "Food Security Index")
colnames(country_all)<-str_replace(colnames(country_all), "risk_wellbeing", "*Risk to wellbeing %")
colnames(country_all)<-str_replace(colnames(country_all), "risk_to_assets", "*Risk to asset %")
colnames(country_all)<-str_replace(colnames(country_all), "pop_dis", "*Population affected by disasters %")
colnames(country_all)<-str_replace(colnames(country_all), "EN.POP.SLUM.UR.ZS", "*Urban slum population %")
colnames(country_all)<-str_replace(colnames(country_all), "rain_exp", "*Rainfall shock exposure %")
colnames(country_all)<-str_replace(colnames(country_all), "SH.STA.TRAF.P5", "*Mortality road traffic injury (per 100,000)")
colnames(country_all)<-str_replace(colnames(country_all), "gdpgr_1519", "GDP per capita growth (annual %)")
colnames(country_all)<-str_replace(colnames(country_all), "u_1519", "*Unemployment (% labor force)")
colnames(country_all)<-str_replace(colnames(country_all), "infl_1519", "*Inflation, consumer prices (annual %)")
colnames(country_all)<-str_replace(colnames(country_all), "hepat_SDG", "*Hepatitis B prevalence %")


#Inclusion
colnames(country_all)<-str_replace(colnames(country_all), "pov_1016", "*Extreme poverty headcount %")
colnames(country_all)<-str_replace(colnames(country_all), "SL.TLF.CACT.FE.ZS", "Female labor participation %")
colnames(country_all)<-str_replace(colnames(country_all), "SH.STA.SMSS.ZS", "Safely managed sanitation %")
colnames(country_all)<-str_replace(colnames(country_all), "SH.H2O.SMDW.ZS", "Safely managed drinking water %")
colnames(country_all)<-str_replace(colnames(country_all), "HD.HCI.OVRL", "Human Capital Index")
colnames(country_all)<-str_replace(colnames(country_all), "SI.POV.GINI", "*Gini Index")
colnames(country_all)<-str_replace(colnames(country_all), "SE.SEC.ENRR", "Secondary school enrollment %")
colnames(country_all)<-str_replace(colnames(country_all), "SH.IMM.IDPT", "Immunization DPT %")
colnames(country_all)<-str_replace(colnames(country_all), "account.t.d.7", "Account ownership (poorest 40%)")
colnames(country_all)<-str_replace(colnames(country_all), "LGBT_acc", "LGBT Acceptance Index")
colnames(country_all)<-str_replace(colnames(country_all), "wbl", "Women, Business & Law Index")
colnames(country_all)<-str_replace(colnames(country_all), "trust_ppl", "Most ppl. can be trusted %")
colnames(country_all)<-str_replace(colnames(country_all), "ref_idp", "*Refugees & IDPs index")
colnames(country_all)<-str_replace(colnames(country_all), "sec_aparat", "*Security apparatus index")
colnames(country_all)<-str_replace(colnames(country_all), "conf_gov", "Confidence in the government")

colnames(country_all)<-str_replace(colnames(country_all), "SI.POV.NAHC", "*Poverty headcount %")
colnames(country_all)<-str_replace(colnames(country_all), "SG.GEN.PARL.ZS", "Women in national parliaments %")
colnames(country_all)<-str_replace(colnames(country_all), "wom_manage_SDG", "Women in managerial positions %")
colnames(country_all)<-str_replace(colnames(country_all), "FX.OWN.TOTL.FE.ZS", "Women account ownership %")
colnames(country_all)<-str_replace(colnames(country_all), "EG.ELC.ACCS.ZS", "Access to electricity %")
colnames(country_all)<-str_replace(colnames(country_all), "per_si_allsi.cov_pop_tot", "Population covered by social insurance %")
colnames(country_all)<-str_replace(colnames(country_all), "SE.ADT.LITR.FE.ZS", "Women literacy rate %")
colnames(country_all)<-str_replace(colnames(country_all), "acc_sani_SDG", "Basic access to sanitation %")
colnames(country_all)<-str_replace(colnames(country_all), "acc_water_SDG", "Basic access to water %")
colnames(country_all)<-str_replace(colnames(country_all), "you_neet_1317", "Youth NEET %")
colnames(country_all)<-str_replace(colnames(country_all), "smes_wom", "SMEs owned by women %")


#Sustainability

colnames(country_all)<-str_replace(colnames(country_all), "NY.ADJ.SVNG.GN.ZS", "Adjusted net savings %")
colnames(country_all)<-str_replace(colnames(country_all), "EN.ATM.PM25.MC.M3", "*PM2.5 mean annual exposure (\U00B5g/m3)")
colnames(country_all)<-str_replace(colnames(country_all), "EG.FEC.RNEW.ZS", "Renewable energy consumption %")
colnames(country_all)<-str_replace(colnames(country_all), "ER.H2O.INTR.PC", "Renewable internal freshwater (m3 pc)")
colnames(country_all)<-str_replace(colnames(country_all), "wat_qua", "Water Quality SDG 6.3")
colnames(country_all)<-str_replace(colnames(country_all), "WWT.new",  "Wastewater treated (primary) %") #before (%) treatment capacity
colnames(country_all)<-str_replace(colnames(country_all), "waste_managed", "Solid waste properly disposed %") #previously "Waste properly managed %"
colnames(country_all)<-str_replace(colnames(country_all), "waste_rate", "*Municipal solid waste (kg/pc/day)")
colnames(country_all)<-str_replace(colnames(country_all), "BHV.new", "Biodiversity Habitat Index")
colnames(country_all)<-str_replace(colnames(country_all), "FSH.new", "Fisheries Index")
colnames(country_all)<-str_replace(colnames(country_all), "GIB.new", "GHG intensity growth rate")
colnames(country_all)<-str_replace(colnames(country_all), "EN.ATM.CO2E.PC", "*CO2 emissions (MT pc)")
colnames(country_all)<-str_replace(colnames(country_all), "forest_loss", "*Forest loss %")

#colnames(country_all)<-str_replace(colnames(country_all), "DT.TDS.DECT.GN.ZS", "Total debt service")

colnames(country_all)<-str_replace(colnames(country_all), "EN.ATM.CO2E.PP.GD", "*CO2 emissions (kg/$GDP)")

#Efficiency
colnames(country_all)<-str_replace(colnames(country_all), "agri_land", "Agri. land productivity ($/ha)")
colnames(country_all)<-str_replace(colnames(country_all), "agri_value", "Agri. value added per worker")
colnames(country_all)<-str_replace(colnames(country_all), "gdp_ghg", "Total GDP/GHG emissions")
colnames(country_all)<-str_replace(colnames(country_all), "gov_effect", "Governance effectiveness")
colnames(country_all)<-str_replace(colnames(country_all), "cont_corr", "Control of corruption")
#colnames(country_all)<-str_replace(colnames(country_all), "reg_qua", "Regulatory quality")
colnames(country_all)<-str_replace(colnames(country_all), "lpi_score", "Logistic Performance Index")
colnames(country_all)<-str_replace(colnames(country_all), "sdg9_intuse", "Pop. using internet %")
colnames(country_all)<-str_replace(colnames(country_all), "lpi_score", "Logistic Performance Index")
colnames(country_all)<-str_replace(colnames(country_all), "Tenure.insecurity", "*Tenure insecurity %")
colnames(country_all)<-str_replace(colnames(country_all), "water_efficiency_FAO", "Water use efficiency (USD/m3)")
colnames(country_all)<-str_replace(colnames(country_all), "water_efficiency_ceo", "Water use efficiency (GDP/m3)")


colnames(country_all)<-str_replace(colnames(country_all), "gov_spe_edu_SDG", "Gov spending on essential services, education %")
colnames(country_all)<-str_replace(colnames(country_all), "debt_gdp_IMF", "*Gross debt (% GDP)")
colnames(country_all)<-str_replace(colnames(country_all), "balance_imf", "Budget balance (% GDP)")
colnames(country_all)<-str_replace(colnames(country_all), "taxrev_imf", "Tax revenues (% tot revenues)")
colnames(country_all)<-str_replace(colnames(country_all), "capstock_imf", "*Capital stock (% GDP)")

}}




```

# Get the aggregate values of median income group (to use in the table comparison we will create in excel)
```{r}
options(scipen=999) #remove scientific notation

#Short income group name for graphs
country_all$income_red <- ifelse(country_all$income == "High income", "HIC",
                                ifelse(country_all$income ==  "Upper middle income", 'UMIC',
                                       ifelse(country_all$income ==  "Lower middle income", 'LMIC',
                                               ifelse(country_all$income ==  "Low income", 'LIC', 'Other'))))

#Aspirational income group: income group "one level up"
country_all$income_aspiration <- ifelse(country_all$income_red == "HIC", "HIC",
                                ifelse(country_all$income_red == 'UMIC', "HIC", 
                                       ifelse(country_all$income_red == 'LMIC', 'UMIC',
                                               ifelse(country_all$income_red == 'LIC', 'LMIC', 'Other'))))


#Short regional group for graphs
country_all$region_red <- ifelse(country_all$region == "South Asia", "SSA",
                                ifelse(country_all$region ==  "Europe & Central Asia", 'ECA',
                                       ifelse(country_all$region ==  "Middle East & North Africa", 'MENA',
                                              ifelse(country_all$region ==  "Sub-Saharan Africa", 'SSA',
                                                     ifelse(country_all$region ==  "Latin America & Caribbean", 'LAC',
                                                        ifelse(country_all$region ==  "East Asia & Pacific", 'EAP',  
                                               ifelse(country_all$region ==  "North America", 'NAC', 'Other')))))))


# MEDIAN
#Income group
income_median <- country_all%>%  group_by(income_red)%>%
  select(-matches('_per'))%>% dplyr::summarise(across(where(is.numeric), list(median= ~median(., na.rm = T)), .names = "{col}"))
income_median<- reshape2::melt(income_median, id.vars=c("income_red"), variable.name="indicator", value.name="median")

#Regional group
region_median <- country_all%>%  group_by(region_red)%>%
  select(-matches('_per'))%>% dplyr::summarise(across(where(is.numeric), list(median= ~median(., na.rm = T)), .names = "{col}"))
region_median<- reshape2::melt(region_median, id.vars=c("region_red"), variable.name="indicator", value.name="median")

#Filter the region it belongs 
country2<-country
region_country<-country_all%>% filter(iso3==country2)%>% summarise((region_red))
region_country<-region_country[1,1]
region_median<-region_median%>% filter(region_red==region_country)
```
# Loop to GET MEDIAN for PPT TABLE for the income, aspirational and regional group
```{r}

for(i in country){

#Get country income group
income_country<-country_all%>% filter(iso3==i)%>% summarise((income_red))
income_country<-income_country[1,1]

#Get country aspirational group
income_aspi<-country_all%>% filter(iso3==i)%>% summarise((income_aspiration))
income_aspi<-income_aspi[1,1]


#Use raw data to compare

country_val<- read.csv(file=paste0(dir_out, group,'/',i,"_percentil_v",version,".csv"), header=TRUE, sep=",")%>%
  select(-percentil)
country_val<-country_val%>%dplyr::select(category, indicator, raw_value)

income_median_country<-income_median%>%
  filter(income_red == income_country)%>%
  dplyr::select(-income_red)

  income_median_country<-left_join(country_val, income_median_country,  by="indicator")%>%
  filter(!is.na(category))%>%
  arrange(category, indicator)
names(income_median_country)[names(income_median_country) == 'median'] <- paste0("median_", income_country)

income_median_aspiration<-income_median%>%
  filter(income_red == income_aspi)%>%
  dplyr::select(-income_red)
names(income_median_aspiration)[names(income_median_aspiration) == 'median'] <- paste0("median_", income_aspi)  

region_median_stats<-region_median%>%
  dplyr::select(-region_red)
names(region_median_stats)[names(region_median_stats) == 'median'] <- paste0("median_", region_country)  

income_median_country<-left_join(income_median_country, income_median_aspiration, by="indicator")
income_median_country<-left_join(income_median_country, region_median_stats, by="indicator")

income_median_country<-income_median_country%>% mutate_if(is.numeric, round, digits=1)
names(income_median_country)[names(income_median_country) == 'raw_value'] <- "country value" 

write.csv(income_median_country,paste0(dir_out, group,'/',i,"_tables_data_v",version,".csv"), row.names = FALSE)
}
```
# Prepare data for PERCENTILE RANKING BAR GRAPH
```{r}
#Duplicate a version of country_all for transformation- country_all needs to remain the same to be use in the percentile rank graph

country_all2<-country_all

#Select ranking values
country_all2<-country_all2%>% select(country, iso3, income_red, region_red, paste0("Resilience_v",version), paste0("Inclusion_v",version), paste0("Sustainability_v",version), paste0("Efficiency_v",version))

#Transform to long format for graph
country_long_complete <- reshape2::melt(country_all2,
        # ID variables - all the variables to keep but not split apart on
    id.vars=c("country", "iso3","income_red", "region_red"),
    variable.name="pillar",
    value.name="percentil"
)

#Get the median value for income group & transform to long format - this would be use for the graph bars 
median_income<- country_all2 %>%
  group_by(income_red)%>%
    dplyr::summarise(across(where(is.numeric), function(x){ median(x, na.rm=TRUE)}))

median_income_long <- reshape2::melt(median_income,
        # ID variables - all the variables to keep but not split apart on
    id.vars=c("income_red"),
    variable.name="pillar",
    value.name="median_income")

#Join data 
country_long_complete<-left_join(country_long_complete, median_income_long, by=c("pillar", "income_red"))
```

# From this point the selection between versions will affect the outcomes 

#Function for PERCENTILE RANKING BAR GRAPH -
```{r}
for(i in country){
  #Duplicate  a version of country long for subsetting 
  country_long<-country_long_complete

  country_long<-country_long%>% filter(str_detect(pillar, paste0("v",version)))
  median_income_filter<-median_income_long%>% filter(str_detect(pillar, paste0("v",version)))


#Get varible to identify the country in the graph
country_long<-country_long%>%
  mutate(country_ind = ifelse(iso3 == i , 1, 0))

##Get regional group
regional_group_df<-country_long%>%
  filter(iso3 == i)%>%
  select(region_red)

regional_group<-regional_group_df[1,1]

#Filter country and arrange percentiles values for graph (since it is a facet graph, percentile arrangement gets messy)
#Establish regional group beforehand
country_long<-country_long%>%
  dplyr::filter(region_red==regional_group)%>%
  dplyr::filter(!is.na(percentil))%>%
  ungroup() %>%
  arrange(pillar, (desc(percentil)))%>%
  mutate(r = row_number())%>%
  mutate(pillar_name = str_replace(pillar, "_v0|_v1|_v2|_v9|_v8", ""))

country_long$pillar_name_f<- factor(country_long$pillar_name, levels= c("Resilience", "Inclusion", "Sustainability", "Efficiency"))

#Once filtered by region, get regional median graph and for the next graph  
country_long<-country_long%>%
  group_by(pillar)%>%
  mutate(median_regional= median(percentil, na.rm=T))

# prepare regional median for next graph 
regional_median<-country_long%>%
  group_by(pillar)%>%
  dplyr::summarise(percentil_median= median(percentil, na.rm=T))%>%
  mutate(group = regional_group)%>%
  select(group, everything())

#Median_income database 
country_long_median<-country_long%>%
  filter(iso3 == i)

  
#Graph regional comparison percentil ranking
reg<-  ggplot(country_long, aes(x = r, y = percentil*100, fill = pillar_name_f, color = as.factor(country_ind), group=income_red)) + 
  geom_col(size=1.2, alpha=0.7)+
  #Blue line REGIONAL MEDIAN -ADD LINE LEGENDS IN PPT
  geom_hline(aes(yintercept = median_regional*100), color="turquoise3", size=1.5)+ 
  #Grey line INCOME MEDIAN- ADD LINE LEGENDS IN PPT
  geom_hline(data=country_long_median, aes(yintercept = median_income*100), color="grey", size=1.5)+ 
  facet_grid(~pillar_name_f, scales = "free")+
  #scale_y_continuous(labels = value, breks= value)+
    labs(y = "Percentile rank in the world",
  title = "")+
theme_minimal()+
  theme(strip.text.x = element_text(size = 19, face = "bold"),
  axis.text.y = element_text(size = 14, hjust = .5, vjust = .5),
  plot.title=element_text(size=14, face = "bold"),
               axis.title.x=element_blank(),
  axis.text.x = element_text(angle = 90, hjust = 1, size= 14),
                 legend.position = "none",
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank())+
  scale_fill_manual(values = c("darkcyan", "red2" ,"goldenrod1", "darkmagenta"))+
  scale_color_manual(values=c("grey25","greenyellow"))+
  scale_x_continuous(breaks = country_long$r, labels = country_long$country) +
  geom_text(aes(x=r, y=(percentil*100)+3 , label= as.integer(percentil*100)), color="black",alpha=1, size=6, inherit.aes = FALSE )
  

ggsave(reg, file=paste0(dir_out, group,'/',i,"_barplot_per_v",version,".png"), width=25, height=10)
ggsave(reg, file=paste0(dir_out, group,'/',i,"_barplot_per_v",version,".pdf"), width=25, height=10)



#Rename col, add iso3 and merge bases

colnames(median_income_filter)<-c("group", "pillar", "percentil_median")
median_income_filter$iso3<-"AAAA" # name like this to make sure it maintains graph color order

regional_median$iso3<-"AAAA" # name like this to make sure it maintains graph color order

country_median_filter<-country_long_median%>%
  dplyr::select(country, pillar, percentil, iso3)
colnames(country_median_filter)<-c("group",  "pillar", "percentil_median", "iso3")

#Merge regional median/income median/country median
graph_bar2<-rbind(country_median_filter, median_income_filter, regional_median)

#Prepare for graph
graph_bar2<-graph_bar2%>%
  dplyr::filter(!is.na(percentil_median))%>%
  ungroup() %>%
  arrange(pillar, (desc(percentil_median)))%>%
  mutate(r = row_number())%>%
  mutate(pillar_name = str_replace(pillar, "_v0|_v1|_v2|_v9|_v8", ""))

graph_bar2$pillar_name_f<- factor(graph_bar2$pillar_name, levels= c("Resilience", "Inclusion", "Sustainability", "Efficiency"))

graph2  <-  ggplot(graph_bar2, aes(x = r, y = percentil_median*100, fill = pillar_name_f, color = as.factor(iso3))) + 
  geom_col(size=1.2, alpha=0.7)+
  #Red line (m)
  geom_hline( yintercept = 50 , color="red3", size=1)+ 
  facet_grid(~pillar_name_f, scales = "free")+
  #scale_y_continuous(labels = value, breks= value)+
    labs(y = "Median percentile rank",
  title = "")+
theme_minimal()+
  theme(strip.text.x = element_text(size = 19, face = "bold"),
  axis.text.y = element_text(size = 16, hjust = .5, vjust = .5),
  plot.title=element_text(size=14, face = "bold"),
               axis.title.x=element_blank(),
  axis.text.x = element_text(size= 14),
                 legend.position = "none",
  panel.grid.minor = element_blank(), 
  panel.grid.major = element_blank())+
  scale_fill_manual(values = c("darkcyan", "red2" ,"goldenrod1", "darkmagenta"))+
  scale_color_manual(values=c("grey25", "green3"))+
  scale_x_continuous(breaks = graph_bar2$r, labels = str_wrap(graph_bar2$group, width = 7)) +
  geom_text(aes(x=r, y=(percentil_median*100)+3 , label= as.integer(percentil_median*100)), color="black",alpha=1, size=6, inherit.aes = FALSE )
  
ggsave(graph2, file=paste0(dir_out, group,'/',i,"_barplot_per_group_v",version,".png"), width=25, height=10)
ggsave(graph2, file=paste0(dir_out, group,'/',i,"_barplot_per_group_v",version,".pdf"), width=25, height=10)

} 

```

# Loop to prepare data for SCORE PILLARS COMPARISON GRAPH - CIRCULAR (PER PILLARS)
```{r}
### COUNTRY Percentile DATASET ###

for(i in country){

country_tot<-country_all  
country_tot<- country_tot[country_tot$iso3 == i, ]
country_percent<-country_tot %>% select(matches('_per'))
country_percent <- as.data.frame(t(as.matrix(country_percent)))
country_percent <- country_percent %>% rownames_to_column("indicator")
colnames(country_percent)<-c("indicator", "percentil")
country_percent$indicator<-str_replace(country_percent$indicator, "_per", "")


#### Country Data Raw values ####

country_values<-country_tot %>% select(-matches('_per'))
country_values <- as.data.frame(t(as.matrix(country_values)))
country_values <- country_values %>% rownames_to_column("indicator")
colnames(country_values)<-c("indicator", "raw_value")


#Set indicators categories

efficiency<-c("Agri. land productivity ($/ha)", "Agri. value added per worker", "Total GDP/GHG emissions","Governance effectiveness", "Control of corruption", "Logistic Performance Index", "Pop. using internet %", "Water use efficiency (USD/m3)", "Logistic Performance Index", "*Tenure insecurity %", "Water use efficiency (USD/m3)", "Water use efficiency (GDP/m3)", "Gov spending on essential services, education %", "*Gross debt (% GDP)", "Budget balance (% GDP)", "Tax revenues (% tot revenues)", "*Capital stock (% GDP)","(E4) Agri. land productivity ($/ha)", "(E1) Agri. value added per worker", "(E4) Total GDP/GHG emissions", "(E2) Governance effectiveness", "(E2) Control of corruption", "(E2) Regulatory quality", "(E1) Logistic Performance Index", "(E3) Individuals using internet %", "(E3) Mobile cellular subscriptions (per 100 people)", "(E2) Rule of law", "(E3) Rapid transit to resident ratio (km/million)", "(E4) *Energy intensity (MJ/$)", "(E1) Patents (per 100,000 people)", "(E1) Digital Penetration Index", "(E4) Water productivity (GDP/m3)","(E3) Shipping connectivity index", "(E1) Global Competitiveness Index", "(E4) *Maternal mortality (per 100,000 live births)")

sustainability<-c("Adjusted net savings %", "*PM2.5 mean annual exposure (\U00B5g/m3)", "Renewable energy consumption %", "Renewable internal freshwater (m3 pc)", "Water Quality SDG 6.3", "Wastewater treated (primary) %", "Solid waste properly disposed %", "*Municipal solid waste (kg/pc/day)", "Biodiversity Habitat Index", "Fisheries Index", "GHG intensity growth rate", "*CO2 emissions (MT pc)", "*Forest loss %", "*CO2 emissions (kg/$GDP)","(S1) *PM2.5 mean annual exposure (\U00B5g/m3)", "(S4) *Forest loss %", "(S3) Renewable energy consumption %","(S2) Wastewater treated (primary) %","(S2) Solid waste properly disposed %","(S2) *Municipal solid waste (kg/pc/day)","(S4) Biodiversity Habitat Index","(S4) Fisheries Index", "(S1) *GHG emissions per capita (% change)", "(S1) *CO2 emissions (MT pc)","(S3) *Ecological Footprint","(S3) *Water withdrawal per capita (m3/year pc)","(S4) *Chlorophyll-a deviations in coastal water %","(S1) *Mortality due to air pollution (per 100,000)","(S2) *Mortality due to unsafe WASH services (per 100,000)", "(S3) Water Quality SDG 6.3")

inclusion<-c("*Extreme poverty headcount %", "*Gini Index", "Immunization DPT %", "Safely managed sanitation %", "Safely managed drinking water %", "Immunization DPT %",  "Secondary school enrollment %", "Human Capital Index", "Account ownership (poorest 40%)", "Female labor participation %", "Women, Business & Law Index",  "LGBT Acceptance Index",  "Most ppl. can be trusted %", "*Refugees & IDPs index", "*Security apparatus index", "Confidence in the government",  "*Poverty headcount %", "Women in national parliaments %", "Women in managerial positions %", "Women account ownership %", "Access to electricity %", "Population covered by social insurance %", "Women literacy rate %", "Youth NEET %","SMEs owned by women %", "(I1) *Extreme poverty headcount %", "SL.TLF.CACT.FE.ZS", "(I2) Female labor participation %", "(I3) Human Capital Index", "(I1) *Gini Index","(I3) Secondary school enrollment %", "(I3) Immunization DPT %", "(I1) Account ownership (poorest 40%)","(I2) LGBT Acceptance Index"
, "(I2) Women, Business & Law Index", "(I1) *Refugees & IDPs index", "(I2) Women in national parliaments %", "(I4) Access to electricity %", "(I4) Basic access to sanitation %", "(I4) Basic access to water %", "(I4) Rural Access Index", "(I3) Universal health coverage (UHC) index %", "Basic access to sanitation %", "Basic access to water %" )

resilience<-c("Food Security Index", "*Risk to wellbeing %", "*Risk to asset %","*Population affected by disasters %", "*Rainfall shock exposure %", "*Urban slum population %","*Mortality road traffic injury (per 100,000)", "GDP per capita growth (annual %)", "*Unemployment (% labor force)",  "*Inflation, consumer prices (annual %)", "*Hepatitis B prevalence %","(R3) *Global Hunger Index", "(R3) *Deaths from conflict and terrorism (per 100,000)", "(R1) *Population affected by disasters %","(R3) *Proportion of urban population living in slums", "(R1) *Rainfall shock exposure %", "(R3) *Population exposed to epidemics (per 100,000)", "(R2) *Projected change of deaths from climate change induced diseases", "habi_01_NDG", "(R2) *Projected change of warm periods", "(R2) *Projected change of flood hazard", "(R4) *Dependency on external resource for health services", "(R4) *Food import dependency", "(R2) *Projected change of sea level rise impacts", "(R4) *Dependency on imported energy", "(R1) *IDPs due to natural disasters (cases per 100,000)", "(R1) *Water Stress SDG 6.4", "(R4) Physicians (per 1,000 people)")

#Assign categories (number set to appear in the RISE order in the graph)

country_percent$category <- ifelse(country_percent$indicator %in% efficiency, '2.Efficiency',
                                   ifelse(country_percent$indicator %in% sustainability, '3.Sustainability',
                                          ifelse(country_percent$indicator %in% resilience, '4.Resilience', 
                                                 ifelse(country_percent$indicator %in% inclusion, '1.Inclusion', 'Other'))))

country_percent <- country_percent%>% filter(category!='Other') 

#Join percentage and raw value
country_percent <-left_join(country_percent, country_values, by="indicator")
country_percent$raw_value<-as.numeric(as.character(country_percent$raw_value))
country_percent$raw_value<-format(round(country_percent$raw_value, 2), nsmall = 2)


# Format score data for graphs
#country_percent <- country_percent[,c(3,1,2,4)]
country_percent$percentil <- as.numeric(as.character(country_percent$percentil))
country_percent$percentil<-country_percent$percentil*100
country_percent <- country_percent[order(country_percent$category),]

#create first databases for percentile ranking (global)

country_percent$percentil<-as.integer(country_percent$percentil)
country_percent<-country_percent%>% select(indicator, percentil, raw_value, category)
write.csv(country_percent,paste0(dir_out, group,'/',i,"_percentil_v",version,".csv"), row.names = FALSE)
}



### COUNTRY SCORE DATASET ###

country_score <- read.csv(paste0(dir_int, comparison_score,".csv"))

#Subset Country score to include only variables for the version in question

if (version == 0){
  country_score <- subset(country_score, select = c(base,v0))
} else {
  if (version == 1) {
  country_score <- subset(country_score, select = c(base,v1))
  } else {
      if (version == 2) {
  country_score <- subset(country_score, select = c(base,v2))
  } else {
      if (version == 8) {
  country_score <- subset(country_score, select = c(base,v8))
  } else {
  country_score <- subset(country_score, select = c(base,v9))
}}}}  


if (version == 2){

  ###V2 Names include subcategory for alphabetical order  
  
#Resilience
colnames(country_score)<-str_replace(colnames(country_score), "glob_hunger_index", "(R3) *Global Hunger Index")
colnames(country_score)<-str_replace(colnames(country_score), "terror", "(R3) *Deaths from conflict and terrorism (per 100,000)")
colnames(country_score)<-str_replace(colnames(country_score), "pop_dis", "(R1) *Population affected by disasters %")
colnames(country_score)<-str_replace(colnames(country_score), "pop_slums_SDG", "(R3) *Proportion of urban population living in slums")
colnames(country_score)<-str_replace(colnames(country_score), "rain_exp", "(R1) *Rainfall shock exposure %")
colnames(country_score)<-str_replace(colnames(country_score), "pop_epid", "(R3) *Population exposed to epidemics (per 100,000)")
colnames(country_score)<-str_replace(colnames(country_score), "heal_01_NDG", "(R2) *Projected change of deaths from climate change induced diseases")
colnames(country_score)<-str_replace(colnames(country_score), "habi_01_NDG", "(R2) *Projected change of warm periods")
colnames(country_score)<-str_replace(colnames(country_score), "habi_02_NDG", "(R2) *Projected change of flood hazard")
colnames(country_score)<-str_replace(colnames(country_score), "heal_03_NDG", "(R4) *Dependency on external resource for health services")
colnames(country_score)<-str_replace(colnames(country_score), "food_03_NDG", "(R4) *Food import dependency")
colnames(country_score)<-str_replace(colnames(country_score), "infr_02_NDG", "(R2) *Projected change of sea level rise impacts")
colnames(country_score)<-str_replace(colnames(country_score), "infr_03_NDG", "(R4) *Dependency on imported energy")
colnames(country_score)<-str_replace(colnames(country_score), "displaced", "(R1) *IDPs due to natural disasters (cases per 100,000)")
colnames(country_score)<-str_replace(colnames(country_score), "wat_stress_SDG", "(R1) *Water Stress SDG 6.4")
colnames(country_score)<-str_replace(colnames(country_score), "SH.MED.PHYS.ZS", "(R4) Physicians (per 1,000 people)")


#Inclusion
colnames(country_score)<-str_replace(colnames(country_score), "pov_1016", "(I1) *Extreme poverty headcount %")
colnames(country_score)<-str_replace(colnames(country_score), "SL.TLF.CACT.FE.ZS", "(I2) Female labor participation %")
colnames(country_score)<-str_replace(colnames(country_score), "HD.HCI.OVRL", "(I3) Human Capital Index")
colnames(country_score)<-str_replace(colnames(country_score), "SI.POV.GINI", "(I1) *Gini Index")
colnames(country_score)<-str_replace(colnames(country_score), "SE.SEC.ENRR", "(I3) Secondary school enrollment %")
colnames(country_score)<-str_replace(colnames(country_score), "SH.IMM.IDPT", "(I3) Immunization DPT %")
colnames(country_score)<-str_replace(colnames(country_score), "account.t.d.7", "(I1) Account ownership (poorest 40%)")
colnames(country_score)<-str_replace(colnames(country_score), "LGBT_acc", "(I2) LGBT Acceptance Index")
colnames(country_score)<-str_replace(colnames(country_score), "wbl", "(I2) Women, Business & Law Index")
colnames(country_score)<-str_replace(colnames(country_score), "ref_idp", "(I1) *Refugees & IDPs index")
colnames(country_score)<-str_replace(colnames(country_score), "SG.GEN.PARL.ZS", "(I2) Women in national parliaments %")
colnames(country_score)<-str_replace(colnames(country_score), "EG.ELC.ACCS.ZS", "(I4) Access to electricity %")
colnames(country_score)<-str_replace(colnames(country_score), "acc_sani_SDG", "(I4) Basic access to sanitation %")
colnames(country_score)<-str_replace(colnames(country_score), "acc_water_SDG", "(I4) Basic access to water %")
colnames(country_score)<-str_replace(colnames(country_score), "rai", "(I4) Rural Access Index")
colnames(country_score)<-str_replace(colnames(country_score), "SH.UHC.SRVS.CV.XD", "(I3) Universal health coverage (UHC) index %")



#Sustainability
colnames(country_score)<-str_replace(colnames(country_score), "EN.ATM.PM25.MC.M3", "(S1) *PM2.5 mean annual exposure (\U00B5g/m3)")
colnames(country_score)<-str_replace(colnames(country_score), "forest_loss", "(S4) *Forest loss %")
colnames(country_score)<-str_replace(colnames(country_score), "EG.FEC.RNEW.ZS", "(S3) Renewable energy consumption %")
colnames(country_score)<-str_replace(colnames(country_score), "wat_qua", "(S3) Water Quality SDG 6.3")
colnames(country_score)<-str_replace(colnames(country_score), "WWT.new", "(S2) Wastewater treated (primary) %")
colnames(country_score)<-str_replace(colnames(country_score), "waste_managed", "(S2) Solid waste properly disposed %")
colnames(country_score)<-str_replace(colnames(country_score), "waste_rate", "(S2) *Municipal solid waste (kg/pc/day)")
colnames(country_score)<-str_replace(colnames(country_score), "BHV.new", "(S4) Biodiversity Habitat Index")
colnames(country_score)<-str_replace(colnames(country_score), "FSH.new", "(S4) Fisheries Index")
colnames(country_score)<-str_replace(colnames(country_score), "ghg_pc", "(S1) *GHG emissions per capita (% change)")
colnames(country_score)<-str_replace(colnames(country_score), "EN.ATM.CO2E.PC", "(S1) *CO2 emissions (MT pc)")
colnames(country_score)<-str_replace(colnames(country_score), "ecos_04_NDG", "(S3) *Ecological Footprint")
colnames(country_score)<-str_replace(colnames(country_score), "fao_withdraw_pc", "(S3) *Water withdrawal per capita (m3/year pc)")
colnames(country_score)<-str_replace(colnames(country_score), "chloroph_SDG", "(S4) *Chlorophyll-a deviations in coastal water %")
colnames(country_score)<-str_replace(colnames(country_score), "SH.STA.AIRP.P5", "(S1) *Mortality due to air pollution (per 100,000)")
colnames(country_score)<-str_replace(colnames(country_score), "SH.STA.WASH.P5", "(S2) *Mortality due to unsafe WASH services (per 100,000)")


#Efficiency
colnames(country_score)<-str_replace(colnames(country_score), "agri_land", "(E4) Agri. land productivity ($/ha)")
colnames(country_score)<-str_replace(colnames(country_score), "agri_value", "(E1) Agri. value added per worker")
colnames(country_score)<-str_replace(colnames(country_score), "gdp_ghg", "(E4) Total GDP/GHG emissions")
colnames(country_score)<-str_replace(colnames(country_score), "gov_effect", "(E2) Governance effectiveness")
colnames(country_score)<-str_replace(colnames(country_score), "cont_corr", "(E2) Control of corruption")
colnames(country_score)<-str_replace(colnames(country_score), "reg_qua", "(E2) Regulatory quality")
colnames(country_score)<-str_replace(colnames(country_score), "lpi_score", "(E1) Logistic Performance Index")
colnames(country_score)<-str_replace(colnames(country_score), "IT.NET.USER.ZS", "(E3) Individuals using internet %")
colnames(country_score)<-str_replace(colnames(country_score), "IT.CEL.SETS.P2", "(E3) Mobile cellular subscriptions (per 100 people)")
colnames(country_score)<-str_replace(colnames(country_score), "rule_law", "(E2) Rule of law")
colnames(country_score)<-str_replace(colnames(country_score), "rapid_trans", "(E3) Rapid transit to resident ratio (km/million)")
colnames(country_score)<-str_replace(colnames(country_score), "EG.EGY.PRIM.PP.KD", "(E4) *Energy intensity (MJ/$)")
colnames(country_score)<-str_replace(colnames(country_score), "patents", "(E1) Patents (per 100,000 people)")  
colnames(country_score)<-str_replace(colnames(country_score), "dai", "(E1) Digital Penetration Index")  
colnames(country_score)<-str_replace(colnames(country_score), "water_efficiency_ceo", "(E4) Water productivity (GDP/m3)")
colnames(country_score)<-str_replace(colnames(country_score), "IS.SHP.GCNW.XQ", "(E3) Shipping connectivity index")
colnames(country_score)<-str_replace(colnames(country_score), "SH.STA.MMRT", "(E4) *Maternal mortality (per 100,000 live births)")
} else {
  if (version == 8) {  
#Resilience
colnames(country_score)<-str_replace(colnames(country_score), "glob_hunger_index", "(R3) *Global Hunger Index")
colnames(country_score)<-str_replace(colnames(country_score), "terror", "(R3) *Deaths from conflict and terrorism (per 100,000)")
colnames(country_score)<-str_replace(colnames(country_score), "pop_dis", "(R1) *Population affected by disasters %")
colnames(country_score)<-str_replace(colnames(country_score), "pop_slums_SDG", "(R3) *Proportion of urban population living in slums")
colnames(country_score)<-str_replace(colnames(country_score), "rain_exp", "(R1) *Rainfall shock exposure %")
colnames(country_score)<-str_replace(colnames(country_score), "pop_epid", "(R3) *Population exposed to epidemics (per 100,000)")
colnames(country_score)<-str_replace(colnames(country_score), "heal_01_NDG", "(R2) *Projected change of deaths from climate change induced diseases")
colnames(country_score)<-str_replace(colnames(country_score), "habi_01_NDG", "(R2) *Projected change of warm periods")
colnames(country_score)<-str_replace(colnames(country_score), "habi_02_NDG", "(R2) *Projected change of flood hazard")
colnames(country_score)<-str_replace(colnames(country_score), "heal_03_NDG", "(R4) *Dependency on external resource for health services")
colnames(country_score)<-str_replace(colnames(country_score), "food_03_NDG", "(R4) *Food import dependency")
colnames(country_score)<-str_replace(colnames(country_score), "infr_02_NDG", "(R2) *Projected change of sea level rise impacts")
colnames(country_score)<-str_replace(colnames(country_score), "infr_03_NDG", "(R4) *Dependency on imported energy")
colnames(country_score)<-str_replace(colnames(country_score), "displaced", "(R1) *IDPs due to natural disasters (cases per 100,000)")
colnames(country_score)<-str_replace(colnames(country_score), "wat_stress_SDG", "(R1) *Water Stress SDG 6.4")
colnames(country_score)<-str_replace(colnames(country_score), "SH.MED.PHYS.ZS", "(R4) Physicians (per 1,000 people)")


#Inclusion
colnames(country_score)<-str_replace(colnames(country_score), "pov_1016", "(I1) *Extreme poverty headcount %")
colnames(country_score)<-str_replace(colnames(country_score), "SL.TLF.CACT.FE.ZS", "(I2) Female labor participation %")
colnames(country_score)<-str_replace(colnames(country_score), "HD.HCI.OVRL", "(I3) Human Capital Index")
colnames(country_score)<-str_replace(colnames(country_score), "SI.POV.GINI", "(I1) *Gini Index")
colnames(country_score)<-str_replace(colnames(country_score), "SE.SEC.ENRR", "(I3) Secondary school enrollment %")
colnames(country_score)<-str_replace(colnames(country_score), "SH.IMM.IDPT", "(I3) Immunization DPT %")
colnames(country_score)<-str_replace(colnames(country_score), "account.t.d.7", "(I1) Account ownership (poorest 40%)")
colnames(country_score)<-str_replace(colnames(country_score), "LGBT_acc", "(I2) LGBT Acceptance Index")
colnames(country_score)<-str_replace(colnames(country_score), "wbl", "(I2) Women, Business & Law Index")
colnames(country_score)<-str_replace(colnames(country_score), "ref_idp", "(I1) *Refugees & IDPs index")
colnames(country_score)<-str_replace(colnames(country_score), "SG.GEN.PARL.ZS", "(I2) Women in national parliaments %")
colnames(country_score)<-str_replace(colnames(country_score), "EG.ELC.ACCS.ZS", "(I4) Access to electricity %")
colnames(country_score)<-str_replace(colnames(country_score), "acc_sani_SDG", "(I4) Basic access to sanitation %")
colnames(country_score)<-str_replace(colnames(country_score), "acc_water_SDG", "(I4) Basic access to water %")
colnames(country_score)<-str_replace(colnames(country_score), "rai", "(I4) Rural Access Index")
colnames(country_score)<-str_replace(colnames(country_score), "SH.UHC.SRVS.CV.XD", "(I3) Universal health coverage (UHC) index %")


#Sustainability
colnames(country_score)<-str_replace(colnames(country_score), "EN.ATM.PM25.MC.M3", "(S1) *PM2.5 mean annual exposure (\U00B5g/m3)")
colnames(country_score)<-str_replace(colnames(country_score), "forest_loss", "(S4) *Forest loss %")
colnames(country_score)<-str_replace(colnames(country_score), "EG.FEC.RNEW.ZS", "(S3) Renewable energy consumption %")
colnames(country_score)<-str_replace(colnames(country_score), "wat_qua", "(S3) Water Quality SDG 6.3")
colnames(country_score)<-str_replace(colnames(country_score), "WWT.new", "(S2) Wastewater treated (primary) %")
colnames(country_score)<-str_replace(colnames(country_score), "waste_managed", "(S2) Solid waste properly disposed %")
colnames(country_score)<-str_replace(colnames(country_score), "waste_rate", "(S2) *Municipal solid waste (kg/pc/day)")
colnames(country_score)<-str_replace(colnames(country_score), "BHV.new", "(S4) Biodiversity Habitat Index")
colnames(country_score)<-str_replace(colnames(country_score), "FSH.new", "(S4) Fisheries Index")
colnames(country_score)<-str_replace(colnames(country_score), "ghg_pc", "(S1) *GHG emissions per capita (% change)")
colnames(country_score)<-str_replace(colnames(country_score), "EN.ATM.CO2E.PC", "(S1) *CO2 emissions (MT pc)")
colnames(country_score)<-str_replace(colnames(country_score), "ecos_04_NDG", "(S3) *Ecological Footprint")
colnames(country_score)<-str_replace(colnames(country_score), "fao_withdraw_pc", "(S3) *Water withdrawal per capita (m3/year pc)")
colnames(country_score)<-str_replace(colnames(country_score), "chloroph_SDG", "(S4) *Chlorophyll-a deviations in coastal water %")
colnames(country_score)<-str_replace(colnames(country_score), "SH.STA.AIRP.P5", "(S1) *Mortality due to air pollution (per 100,000)")
colnames(country_score)<-str_replace(colnames(country_score), "SH.STA.WASH.P5", "(S2) *Mortality due to unsafe WASH services (per 100,000)")


#Efficiency
colnames(country_score)<-str_replace(colnames(country_score), "agri_land", "(E4) Agri. land productivity ($/ha)")
colnames(country_score)<-str_replace(colnames(country_score), "agri_value", "(E1) Agri. value added per worker")
colnames(country_score)<-str_replace(colnames(country_score), "gdp_ghg", "(E4) Total GDP/GHG emissions")
colnames(country_score)<-str_replace(colnames(country_score), "gov_effect", "(E2) Governance effectiveness")
colnames(country_score)<-str_replace(colnames(country_score), "cont_corr", "(E2) Control of corruption")
colnames(country_score)<-str_replace(colnames(country_score), "reg_qua", "(E2) Regulatory quality")
colnames(country_score)<-str_replace(colnames(country_score), "gci", "(E1) Global Competitiveness Index")
colnames(country_score)<-str_replace(colnames(country_score), "IT.NET.USER.ZS", "(E3) Individuals using internet %")
colnames(country_score)<-str_replace(colnames(country_score), "IT.CEL.SETS.P2", "(E3) Mobile cellular subscriptions (per 100 people)")
colnames(country_score)<-str_replace(colnames(country_score), "rule_law", "(E2) Rule of law")
colnames(country_score)<-str_replace(colnames(country_score), "rapid_trans", "(E3) Rapid transit to resident ratio (km/million)")
colnames(country_score)<-str_replace(colnames(country_score), "EG.EGY.PRIM.PP.KD", "(E4) *Energy intensity (MJ/$)")
colnames(country_score)<-str_replace(colnames(country_score), "patents", "(E1) Patents (per 100,000 people)")  
colnames(country_score)<-str_replace(colnames(country_score), "dai", "(E1) Digital Penetration Index")  
colnames(country_score)<-str_replace(colnames(country_score), "water_efficiency_ceo", "(E4) Water productivity (GDP/m3)")
colnames(country_score)<-str_replace(colnames(country_score), "IS.SHP.GCNW.XQ", "(E3) Shipping connectivity index")
colnames(country_score)<-str_replace(colnames(country_score), "SH.STA.MMRT", "(E4) *Maternal mortality (per 100,000 live births)")

  } else {   
#Assign names to variables
#Resilience
colnames(country_score)<-str_replace(colnames(country_score), "food_sec", "Food Security Index")
colnames(country_score)<-str_replace(colnames(country_score), "risk_wellbeing", "*Risk to wellbeing %")
colnames(country_score)<-str_replace(colnames(country_score), "risk_to_assets", "*Risk to asset %")
colnames(country_score)<-str_replace(colnames(country_score), "pop_dis", "*Population affected by disasters %")
colnames(country_score)<-str_replace(colnames(country_score), "EN.POP.SLUM.UR.ZS", "*Urban slum population %")
colnames(country_score)<-str_replace(colnames(country_score), "rain_exp", "*Rainfall shock exposure %")

colnames(country_score)<-str_replace(colnames(country_score), "SH.STA.TRAF.P5", "*Mortality road traffic injury (per 100,000)")
colnames(country_score)<-str_replace(colnames(country_score), "gdpgr_1519", "GDP per capita growth (annual %)")
colnames(country_score)<-str_replace(colnames(country_score), "u_1519", "*Unemployment (% labor force)")
colnames(country_score)<-str_replace(colnames(country_score), "infl_1519", "*Inflation, consumer prices (annual %)")
colnames(country_score)<-str_replace(colnames(country_score), "hepat_SDG", "*Hepatitis B prevalence %")


#Inclusion
colnames(country_score)<-str_replace(colnames(country_score), "pov_1016", "*Extreme poverty headcount %")
colnames(country_score)<-str_replace(colnames(country_score), "SL.TLF.CACT.FE.ZS", "Female labor participation %")
colnames(country_score)<-str_replace(colnames(country_score), "SH.STA.SMSS.ZS", "Safely managed sanitation %")
colnames(country_score)<-str_replace(colnames(country_score), "SH.H2O.SMDW.ZS", "Safely managed drinking water %")
colnames(country_score)<-str_replace(colnames(country_score), "HD.HCI.OVRL", "Human Capital Index")
colnames(country_score)<-str_replace(colnames(country_score), "SI.POV.GINI", "*Gini Index")
colnames(country_score)<-str_replace(colnames(country_score), "SE.SEC.ENRR", "Secondary school enrollment %")
colnames(country_score)<-str_replace(colnames(country_score), "SH.IMM.IDPT", "Immunization DPT %")
colnames(country_score)<-str_replace(colnames(country_score), "account.t.d.7", "Account ownership (poorest 40%)")
colnames(country_score)<-str_replace(colnames(country_score), "LGBT_acc", "LGBT Acceptance Index")
colnames(country_score)<-str_replace(colnames(country_score), "wbl", "Women, Business & Law Index")
colnames(country_score)<-str_replace(colnames(country_score), "trust_ppl", "Most ppl. can be trusted %")
colnames(country_score)<-str_replace(colnames(country_score), "ref_idp", "*Refugees & IDPs index")
colnames(country_score)<-str_replace(colnames(country_score), "sec_aparat", "*Security apparatus index")
colnames(country_score)<-str_replace(colnames(country_score), "conf_gov", "Confidence in the government")

colnames(country_score)<-str_replace(colnames(country_score), "SI.POV.NAHC", "*Poverty headcount %")
colnames(country_score)<-str_replace(colnames(country_score), "SG.GEN.PARL.ZS", "Women in national parliaments %")
colnames(country_score)<-str_replace(colnames(country_score), "wom_manage_SDG", "Women in managerial positions %")
colnames(country_score)<-str_replace(colnames(country_score), "FX.OWN.TOTL.FE.ZSr", "Women account ownership %")
colnames(country_score)<-str_replace(colnames(country_score), "EG.ELC.ACCS.ZS", "Access to electricity %")
colnames(country_score)<-str_replace(colnames(country_score), "per_si_allsi.cov_pop_tot", "Population covered by social insurance %")
colnames(country_score)<-str_replace(colnames(country_score), "SE.ADT.LITR.FE.ZS", "Women literacy rate %")
colnames(country_score)<-str_replace(colnames(country_score), "acc_sani_SDG", "Basic access to sanitation %")
colnames(country_score)<-str_replace(colnames(country_score), "acc_water_SDG", "Basic access to water %")
colnames(country_score)<-str_replace(colnames(country_score), "you_neet_1317", "Youth NEET %")
colnames(country_score)<-str_replace(colnames(country_score), "smes_wom", "SMEs owned by women %")



#Sustainability
#colnames(country_score)<-str_replace(colnames(country_score), "DT.TDS.DECT.GN.ZS", "Total debt service")
colnames(country_score)<-str_replace(colnames(country_score), "NY.ADJ.SVNG.GN.ZS", "Adjusted net savings %")
colnames(country_score)<-str_replace(colnames(country_score), "EN.ATM.PM25.MC.M3", "*PM2.5 mean annual exposure (\U00B5g/m3)")
colnames(country_score)<-str_replace(colnames(country_score), "forest_loss", "*Forest loss %")
colnames(country_score)<-str_replace(colnames(country_score), "EG.FEC.RNEW.ZS", "Renewable energy consumption %")
colnames(country_score)<-str_replace(colnames(country_score), "ER.H2O.INTR.PC", "Renewable internal freshwater (m3 pc)")
colnames(country_score)<-str_replace(colnames(country_score), "wat_qua", "Water Quality SDG 6.3")
colnames(country_score)<-str_replace(colnames(country_score), "WWT.new", "Wastewater treated (primary) %")
colnames(country_score)<-str_replace(colnames(country_score), "waste_managed", "Solid waste properly disposed %")
colnames(country_score)<-str_replace(colnames(country_score), "waste_rate", "*Municipal solid waste (kg/pc/day)")
colnames(country_score)<-str_replace(colnames(country_score), "BHV.new", "Biodiversity Habitat Index")
colnames(country_score)<-str_replace(colnames(country_score), "FSH.new", "Fisheries Index")
colnames(country_score)<-str_replace(colnames(country_score), "GIB.new", "GHG intensity growth rate")
colnames(country_score)<-str_replace(colnames(country_score), "EN.ATM.CO2E.PC", "*CO2 emissions (MT pc)")
colnames(country_score)<-str_replace(colnames(country_score), "EN.ATM.CO2E.PP.GD", "*CO2 emissions (kg/$GDP)")


#Efficiency
colnames(country_score)<-str_replace(colnames(country_score), "agri_land", "Agri. land productivity ($/ha)")
colnames(country_score)<-str_replace(colnames(country_score), "agri_value", "Agri. value added per worker")
colnames(country_score)<-str_replace(colnames(country_score), "gdp_ghg", "Total GDP/GHG emissions")
colnames(country_score)<-str_replace(colnames(country_score), "gov_effect", "Governance effectiveness")
colnames(country_score)<-str_replace(colnames(country_score), "cont_corr", "Control of corruption")
#colnames(country_score)<-str_replace(colnames(country_score), "reg_qua", "Regulatory quality")
colnames(country_score)<-str_replace(colnames(country_score), "lpi_score", "Logistic Performance Index")
colnames(country_score)<-str_replace(colnames(country_score), "sdg9_intuse", "Pop. using internet %")
colnames(country_score)<-str_replace(colnames(country_score), "lpi_score", "Logistic Performance Index")
colnames(country_score)<-str_replace(colnames(country_score), "Tenure.insecurity", "*Tenure insecurity %")
colnames(country_score)<-str_replace(colnames(country_score), "water_efficiency_FAO", "Water use efficiency (USD/m3)")
colnames(country_score)<-str_replace(colnames(country_score), "water_efficiency_ceo", "Water use efficiency (GDP/m3)")

colnames(country_score)<-str_replace(colnames(country_score), "gov_spe_edu_SDG", "Gov spending on essential services, education %")
colnames(country_score)<-str_replace(colnames(country_score), "debt_gdp_IMF", "*Gross debt (% GDP)")
colnames(country_score)<-str_replace(colnames(country_score), "balance_imf", "Budget balance (% GDP)")
colnames(country_score)<-str_replace(colnames(country_score), "taxrev_imf", "Tax revenues (% tot revenues)")
colnames(country_score)<-str_replace(colnames(country_score), "capstock_imf", "*Capital stock (% GDP)")
}}
  


for(i in country){
country_score <- country_score[country_score$iso3 == i, ]
country_score <- as.data.frame(t(as.matrix(country_score)))
country_score <- country_score %>% rownames_to_column("indicator")
colnames(country_score)<-c("indicator", "score")
country_score$category <- ifelse(country_score$indicator %in% efficiency, '2.Efficiency',
                                   ifelse(country_score$indicator %in% sustainability, '3.Sustainability',
                                          ifelse(country_score$indicator %in% resilience, '4.Resilience', 
                                                 ifelse(country_score$indicator %in% inclusion, '1.Inclusion', 'Other'))))


country_score <- country_score%>% filter(category!='Other') 

#Join percentage and raw value
country_score <-left_join(country_score, country_values, by="indicator")
country_score$raw_value<-as.numeric(as.character(country_score$raw_value))
country_score$raw_value<-format(round(country_score$raw_value, 2), nsmall = 2)

# Format score data for graphs

country_score$score <- as.numeric(as.character(country_score$score))
country_score$score<-country_score$score*100
country_score <- country_score[order(country_score$category),]

#Create the second database for graph pillars (regional/income)

#Get inverse values for score graph - For the individual pillars graphs we need to get the value of the indicator and the inverse value, to create the circular graph as an stacked plot #in the score_graph_data, score will be the inverse value and 
country_score$score <- with(country_score, (100-score))
country_score$values <- with(country_score, (100-score))

country_score$score <- as.integer(country_score$score)
country_score$values <- as.integer(country_score$values)

write.csv(country_score, paste0(dir_out, group,'/',i,"_score_graphs_v",version,".csv"), row.names = FALSE)
}

```

# Loop to prepare data for PERCENTIL RANKING GRAPH - CIRCULAR (ALL PILLARS- Global data)
```{r}

for(i in country){
# Load dataset from data generated in the previous section
  country_percent <- read.csv(file=paste0(dir_out, group,'/',i,"_percentil_v",version,".csv"), header=TRUE, sep=",")

  
  
data3<-country_percent

#Arrange data and filter NA
data3 <- data3 %>% 
  filter(!is.na(percentil))%>% 
  arrange(category, percentil)
data3$id <- seq(1, nrow(data3))

#Create labels for each column and angles (no need to adjust. With this method labels are aligned automatically)
label_data3 <- data3
number_of_bar3 <- nrow(label_data3)
angle3 <- 90 - 360 * (label_data3$id-0.5) /number_of_bar3     # I substract 0.5 because the letter must have the angle of the center of the bars. Not extreme right(1) or extreme left (0)
label_data3$hjust <- ifelse(angle3 < -90, 1, 0)
label_data3$angle <- ifelse(angle3 < -90, angle3+180, angle3)

# prepare a data frame for pillars names
base_data3 <- data3 %>% 
  group_by(category) %>% 
  dplyr::summarize(start=min(id), end=max(id)) %>% 
  rowwise() %>% 
  mutate(title=mean(c(start, end)))

#Remove numbers to the  pillar category name 
base_data3$category2<-str_replace(base_data3$category, "1.|2.|3.|4.", "")

#Paste indicators labels with  percentil rank values (ej, 35.- Labor market)
label_data3$test <- paste(data3$percentil, "-", data3$indicator)

com <- ggplot(data3) +      
  
  # Add the stacked bar
  geom_bar(aes(x=as.factor(id), y=percentil, fill=category, colour=category), stat="identity", alpha=0.7, size=0.2) +
  #colors used by the CEO in their first draft of the benchmarking
  #scale_fill_manual(values=c("hotpink1","gold1","steelblue2", "green3")) +
  scale_fill_manual(values=c("red2" ,"darkmagenta", "goldenrod1","darkcyan"))+
  scale_colour_manual(values=c("black","black", "black","black")) +
  
    geom_label(x = 0, y = -50, label = i, hjust=0.5, fontface="bold", size=7) +
  
  ylim(-50,120) +
  theme_minimal() +
  theme(
    legend.position = "none",
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = margin(-3,-3,-3,-3, "cm") 
  ) +
  coord_polar() +
  
  ####Remember to put a if that makes it smaller for v2  PLACEHOLDER 
  
   # Add labels on top of each bar
  geom_text(data=label_data3, aes(x=id, y=percentil+2, label= str_wrap(test, width = 20), hjust=label_data3$hjust), color="black", fontface="bold",alpha=1, size=perctext, angle= label_data3$angle, inherit.aes = FALSE ) +

  # Add base line information
geom_segment(data=base_data3, aes(x = start, y = -5, xend = end, yend = -5), colour = "black", alpha=0.8, size=0.6 , inherit.aes = FALSE )  +
  geom_text(data=base_data3, aes(x = title, y = -18, label=category2), hjust=c(0.5,0.5,0.5,0.5), angle=c(-60, 15, -65, 40), colour = "black", alpha=0.8, size=4, fontface="bold", inherit.aes = FALSE)


ggsave(com, file=paste0(dir_out, group,'/',i,"_percentil_global_v",version,".png"), width=12, height=13)
ggsave(com, file=paste0(dir_out, group,'/',i,"_percentil_global_v",version,".pdf"), width=12, height=13)

}
```



#Graphs per pillars (RISE) - SUSTAINABILITY
```{r}
    ##########
  # Sustainability#    #Different set of indicators for V0 AND V1
    ##########

for(i in country){
# Load dataset with country scores generated in the previous section
  country_score <- read.csv(file=paste0(dir_out, group,'/',i,"_score_graphs_v",version,".csv"), header=TRUE, sep=",")
  

#Split data for graphs 
country_score_graph1 <- country_score %>% filter(category== '3.Sustainability')

data2<-country_score_graph1
data2$order <- seq(1, nrow(data2))

# Move order column to the front so it does not get rejected when transforming to long format (column necessary to keep order of dimensions for the graph)
data2 <- data2 %>% 
  filter(!is.na(score))%>%
  select(order, everything())

# Transform data in a tidy format (long format)
data2 <- stats::reshape(data2, 
                direction = "long",
                varying = c("score", "values"),
                v.names = "value",
                idvar = c("order", "indicator", "category", "raw_value"),
                timevar = "observation",
                times = 1:2)

# Set a number of 'empty bar' to add at the end of each group
empty_bar <- 2
nObsType <- nlevels(as.factor(data2$observation))
to_add <- data.frame( matrix(NA, empty_bar*nlevels(as.factor(data2$category))*nObsType*.5, ncol(data2)))
colnames(to_add) <- colnames(data2)
to_add$category <- rep(levels(as.factor(data2$category)), each=empty_bar*nObsType*.5 )
data2 <- rbind(data2, to_add)

grpid = function(x) match(x, unique(x))
data2 <- data2 %>% mutate(group_id = group_indices(., category) %>% grpid)

#To group inverse and no inverse value
data2<- data2 %>% mutate(group_order=case_when(
  group_id == 1 ~ "A",
  TRUE ~ NA_character_ # all else are NA
))

data2 <- data2[order(data2$indicator),]

data2$id <- rep( seq(1, nrow(data2)/nObsType) , each=nObsType)

#Create labels for each column and angles (no need to adjust. With this method labels are aligned automatically)
label_data2 <- data2 %>% dplyr::group_by(id, indicator, raw_value) %>% dplyr::summarize(tot=sum(value))
number_of_bar2 <- nrow(label_data2)
angle2 <- 90 - 360 * (label_data2$id-0.5) /number_of_bar2     # I substract 0.5 because the letter must have the angle of the center of the bars. Not extreme right(1) or extreme left (0)
label_data2$hjust <- ifelse(angle2 < -90, 1, 0)
label_data2$angle <- ifelse(angle2 < -90, angle2+180, angle2)

# prepare a data frame for base lines
base_data2 <- data2 %>% 
  group_by(group_order) %>% 
  dplyr::summarize(start=min(id), end=max(id) 
            - empty_bar
          ) %>% 
  rowwise() %>% 
  mutate(title=mean(c(start, end)))

# prepare a data frame for grid (scales)
grid_data2 <- base_data2
grid_data2$end <- grid_data2$end[ c( nrow(grid_data2), 1:nrow(grid_data2)-1)] + 1.4
grid_data2$start <- grid_data2$start - .4
#grid_data2 <- grid_data2[-1,]

#Paste categories and raw values

data2$inv  <- ifelse(grepl("\\) \\*",data2$indicator), 1, 0)
data2$inv[is.na(data2$indicator)] <- NA

data2$cat <- paste(data2$observation,data2$group_order,data2$inv)

label_data2$ind_value<-paste(label_data2$raw_value, "-", label_data2$indicator)



s <- ggplot(data2) +      
  
  # Add the stacked bar
  geom_bar(aes(x=as.factor(id), y=value, fill=cat, colour=cat), stat="identity", alpha=0.5, size=0.2) +
  #scale_fill_manual(values=c("white","steelblue1")) +
  scale_fill_manual(values=c("white","white","goldenrod1","lightgoldenrod1")) +
  scale_colour_manual(values=c("black","black","black","black")) +

  # Add a val=100/75/50/25 lines. I do it at the beginning to make sur barplots are OVER it.
  #geom_segment(data=grid_data2, aes(x = end, y = 100, xend = start, yend = 100), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data2, aes(x = end, y = 80, xend = start, yend = 80), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data2, aes(x = end, y = 60, xend = start, yend = 60), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data2, aes(x = end, y = 40, xend = start, yend = 40), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data2, aes(x = end, y = 20, xend = start, yend = 20), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  
    geom_label(x = 0, y = 0, label = i, hjust=0.5, fontface="bold", size=10) +
    annotate("text", x = rep(max(data2$id),5), y = c(20, 40, 60, 80, 100), label = c("20", "40", "60", "80", "100") , color="grey", size=5 , angle=0, fontface="bold", hjust=.5) +
  
  ylim(0 , 120) +
  theme_minimal() +
  theme(
    legend.position = "none",
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = margin(-3,-3,-3,-3, "cm") 
  ) +
  coord_polar() +
  
   # Add labels on top of each bar
  
  geom_text(data=label_data2, aes(x=id, y=tot-50, label= str_wrap(ind_value, width = 22), hjust=label_data2$hjust), color="black", fontface="bold",alpha=1, size=pillartext, angle= label_data2$angle, inherit.aes = FALSE ) 


ggsave(s, file=paste0(dir_out, group,'/',i,"_score_graph_sust_v",version,".png"), width=10, height=10)
ggsave(s, file=paste0(dir_out, group,'/',i,"_score_graph_sust_v",version,".pdf"), width=10, height=10)


}
```


# Graphs per pillars (RISE) -INCLUSION
```{r}
      ##########
     # Inclusion #    #Different set of indicators for V0 AND V1
      ##########

#detach(package:plyr)
  
for(i in country){
# Load dataset with country scores generated in the previous section
  country_score <- read.csv(file=paste0(dir_out, group,'/',i,"_score_graphs_v",version,".csv"), header=TRUE, sep=",")



#Split data for graphs 
country_score_graph2 <- country_score %>% filter(category== '1.Inclusion')

data2<-country_score_graph2
data2$order <- seq(1, nrow(data2))

# Move order column to the front so it does not get rejected when transforming to long format (column necessary to keep order of dimensions for the graph)
data2 <- data2 %>% 
  filter(!is.na(score))%>%
  select(order, everything())

# Transform data in a tidy format (long format)
data2 <- stats::reshape(data2, 
                direction = "long",
                varying = c("score", "values"),
                v.names = "value",
                idvar = c("order", "indicator", "category", "raw_value"),
                timevar = "observation",
                times = 1:2)

# Set a number of 'empty bar' to add at the end of each group
empty_bar <- 2
nObsType <- nlevels(as.factor(data2$observation))
to_add <- data.frame( matrix(NA, empty_bar*nlevels(as.factor(data2$category))*nObsType*.5, ncol(data2)))
colnames(to_add) <- colnames(data2)
to_add$category <- rep(levels(as.factor(data2$category)), each=empty_bar*nObsType*.5 )
data2 <- rbind(data2, to_add)

grpid = function(x) match(x, unique(x))
data2 <- data2 %>% mutate(group_id = group_indices(., category) %>% grpid)

#To group inverse and no inverse value
data2<- data2 %>% mutate(group_order=case_when(
  group_id == 1 ~ "A",
  TRUE ~ NA_character_ # all else are NA
))

data2 <- data2[order(data2$indicator),]

data2$id <- rep( seq(1, nrow(data2)/nObsType) , each=nObsType)

#Create labels for each column and angles (no need to adjust. With this method labels are aligned automatically)
label_data2 <- data2 %>% dplyr::group_by(id, indicator, raw_value) %>% dplyr::summarize(tot=sum(value))
number_of_bar2 <- nrow(label_data2)
angle2 <- 90 - 360 * (label_data2$id-0.5) /number_of_bar2     # I substract 0.5 because the letter must have the angle of the center of the bars. Not extreme right(1) or extreme left (0)
label_data2$hjust <- ifelse(angle2 < -90, 1, 0)
label_data2$angle <- ifelse(angle2 < -90, angle2+180, angle2)

# prepare a data frame for base lines
base_data2 <- data2 %>% 
  group_by(group_order) %>% 
  dplyr::summarize(start=min(id), end=max(id) 
            - empty_bar
          ) %>% 
  rowwise() %>% 
  mutate(title=mean(c(start, end)))

# prepare a data frame for grid (scales)
grid_data2 <- base_data2
grid_data2$end <- grid_data2$end[ c( nrow(grid_data2), 1:nrow(grid_data2)-1)] + 1.4
grid_data2$start <- grid_data2$start - .4
#grid_data2 <- grid_data2[-1,]

#Paste categories and raw values
data2$inv  <- ifelse(grepl("\\) \\*",data2$indicator), 1, 0)
data2$inv[is.na(data2$indicator)] <- NA

data2$cat <- paste(data2$observation,data2$group_order,data2$inv)
label_data2$ind_value<-paste(label_data2$raw_value, "-", label_data2$indicator)

inc <- ggplot(data2) +      
  
  # Add the stacked bar
  geom_bar(aes(x=as.factor(id), y=value, fill=cat, colour=cat), stat="identity", alpha=0.5, size=0.2) +
  #scale_fill_manual(values=c("white","hotpink1")) +
  scale_fill_manual(values=c("white","white","red2","coral")) +
  scale_colour_manual(values=c("black","black","black","black")) +

  # Add a val=100/75/50/25 lines. I do it at the beginning to make sur barplots are OVER it.
  #geom_segment(data=grid_data2, aes(x = end, y = 100, xend = start, yend = 100), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data2, aes(x = end, y = 80, xend = start, yend = 80), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data2, aes(x = end, y = 60, xend = start, yend = 60), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data2, aes(x = end, y = 40, xend = start, yend = 40), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data2, aes(x = end, y = 20, xend = start, yend = 20), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  
    geom_label(x = 0, y = 0, label = i, hjust=0.5, fontface="bold", size=10) +
    annotate("text", x = rep(max(data2$id),5), y = c(20, 40, 60, 80, 100), label = c("20", "40", "60", "80", "100") , color="grey", size=5 , angle=0, fontface="bold", hjust=.5) +
  
  ylim(0 , 120) +
  theme_minimal() +
  theme(
    legend.position = "none",
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = margin(-3,-3,-3,-3, "cm") 
  ) +
  coord_polar() +
  
   # Add labels on top of each bar
  
  geom_text(data=label_data2, aes(x=id, y=tot-50, label= str_wrap(ind_value, width = 22), hjust=label_data2$hjust), color="black", fontface="bold",alpha=1, size=pillartext, angle= label_data2$angle, inherit.aes = FALSE ) 


ggsave(inc, file=paste0(dir_out, group,'/',i,"_score_graph_incl_v",version,".png"), width=10, height=10)
ggsave(inc, file=paste0(dir_out, group,'/',i,"_score_graph_incl_v",version,".pdf"), width=10, height=10)

}

```


# Graphs per pillars (RISE) - Efficiency
```{r}
    ##########
# 2. Efficiency  # Same set of indicators for V0 and V1 (still using version control in case the indicators change)
    ##########
#detach(package:plyr)
  
for(i in country){
# Load dataset with country scores generated in the previous section
  country_score <- read.csv(file=paste0(dir_out, group,'/',i,"_score_graphs_v",version,".csv"), header=TRUE, sep=",")


#Split data for graphs 
country_score_graph2 <- country_score %>% filter(category== '2.Efficiency')

data2<-country_score_graph2
data2$order <- seq(1, nrow(data2))

# Move order column to the front so it does not get rejected when transforming to long format (column necessary to keep order of dimensions for the graph)
data2 <- data2 %>% 
  filter(!is.na(score))%>%
  select(order, everything())

# Transform data in a tidy format (long format)
data2 <- stats::reshape(data2, 
                direction = "long",
                varying = c("score", "values"),
                v.names = "value",
                idvar = c("order", "indicator", "category", "raw_value"),
                timevar = "observation",
                times = 1:2)

# Set a number of 'empty bar' to add at the end of each group
empty_bar <- 2
nObsType <- nlevels(as.factor(data2$observation))
to_add <- data.frame( matrix(NA, empty_bar*nlevels(as.factor(data2$category))*nObsType*.5, ncol(data2)))
colnames(to_add) <- colnames(data2)
to_add$category <- rep(levels(as.factor(data2$category)), each=empty_bar*nObsType*.5 )
data2 <- rbind(data2, to_add)

grpid = function(x) match(x, unique(x))
data2 <- data2 %>% mutate(group_id = group_indices(., category) %>% grpid)

#To group inverse and no inverse value
data2<- data2 %>% mutate(group_order=case_when(
  group_id == 1 ~ "A",
  TRUE ~ NA_character_ # all else are NA
))

data2 <- data2[order(data2$indicator),]

data2$id <- rep( seq(1, nrow(data2)/nObsType) , each=nObsType)

#Create labels for each column and angles (no need to adjust. With this method labels are aligned automatically)
label_data2 <- data2 %>% dplyr::group_by(id, indicator, raw_value) %>% dplyr::summarize(tot=sum(value))
number_of_bar2 <- nrow(label_data2)
angle2 <- 90 - 360 * (label_data2$id-0.5) /number_of_bar2     # I substract 0.5 because the letter must have the angle of the center of the bars. Not extreme right(1) or extreme left (0)
label_data2$hjust <- ifelse(angle2 < -90, 1, 0)
label_data2$angle <- ifelse(angle2 < -90, angle2+180, angle2)

# prepare a data frame for base lines
base_data2 <- data2 %>% 
  group_by(group_order) %>% 
  dplyr::summarize(start=min(id), end=max(id) 
            - empty_bar
          ) %>% 
  rowwise() %>% 
  mutate(title=mean(c(start, end)))

# prepare a data frame for grid (scales)
grid_data2 <- base_data2
grid_data2$end <- grid_data2$end[ c( nrow(grid_data2), 1:nrow(grid_data2)-1)] + 1.4
grid_data2$start <- grid_data2$start - .4
#grid_data2 <- grid_data2[-1,]

#Paste categories and raw values
data2$inv  <- ifelse(grepl("\\) \\*",data2$indicator), 1, 0)
data2$inv[is.na(data2$indicator)] <- NA

data2$cat <- paste(data2$observation,data2$group_order,data2$inv)
label_data2$ind_value<-paste(label_data2$raw_value, "-", label_data2$indicator)

e <- ggplot(data2) +      
  
  # Add the stacked bar
  geom_bar(aes(x=as.factor(id), y=value, fill=cat, colour=cat), stat="identity", alpha=0.5, size=0.2) +
  #scale_fill_manual(values=c("white","gold1")) +
  scale_fill_manual(values=c("white","white","darkmagenta","plum")) +
  scale_colour_manual(values=c("black","black","black","black")) +

  # Add a val=100/75/50/25 lines. I do it at the beginning to make sur barplots are OVER it.
  #geom_segment(data=grid_data2, aes(x = end, y = 100, xend = start, yend = 100), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data2, aes(x = end, y = 80, xend = start, yend = 80), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data2, aes(x = end, y = 60, xend = start, yend = 60), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data2, aes(x = end, y = 40, xend = start, yend = 40), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data2, aes(x = end, y = 20, xend = start, yend = 20), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  
    geom_label(x = 0, y = 0, label = i, hjust=0.5, fontface="bold", size=10) +
    annotate("text", x = rep(max(data2$id),5), y = c(20, 40, 60, 80, 100), label = c("20", "40", "60", "80", "100") , color="grey", size=5 , angle=0, fontface="bold", hjust=.5) +
  
  ylim(0 , 120) +
  theme_minimal() +
  theme(
    legend.position = "none",
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = margin(-3,-3,-3,-3, "cm") 
  ) +
  coord_polar() +
  
   # Add labels on top of each bar
  
  geom_text(data=label_data2, aes(x=id, y=tot-50, label= str_wrap(ind_value, width = 22), hjust=label_data2$hjust), color="black", fontface="bold",alpha=1, size=pillartext, angle= label_data2$angle, inherit.aes = FALSE ) 


ggsave(e, file=paste0(dir_out, group,'/',i,"_score_graph_eff_v",version,".png"), width=10, height=10)
ggsave(e, file=paste0(dir_out, group,'/',i,"_score_graph_eff_v",version,".pdf"), width=10, height=10)

}
```



#Graphs per pillars (RISE) - Resilience
```{r}
    ##########
#   RESILIENCE #    # Same set of indicators for V0 and V1 (still using version control in case it indicators change)
    ##########
#detach(package:plyr)
  
for(i in country){
# Load dataset with country scores generated in the previous section
  country_score <- read.csv(file=paste0(dir_out, group,'/',i,"_score_graphs_v",version,".csv"), header=TRUE, sep=",")

  
  
##### Resilience #######

#Split data for graphs 
country_score_graph2 <- country_score %>% filter(category== '4.Resilience')

data2<-country_score_graph2
data2$order <- seq(1, nrow(data2))

# Move order column to the front so it does not get rejected when transforming to long format (column necessary to keep order of dimensions for the graph)
data2 <- data2 %>% 
  filter(!is.na(score))%>%
  select(order, everything())

# Transform data in a tidy format (long format)
data2 <- stats::reshape(data2, 
                direction = "long",
                varying = c("score", "values"),
                v.names = "value",
                idvar = c("order", "indicator", "category", "raw_value"),
                timevar = "observation",
                times = 1:2)

# Set a number of 'empty bar' to add at the end of each group
empty_bar <- 2
nObsType <- nlevels(as.factor(data2$observation))
to_add <- data.frame( matrix(NA, empty_bar*nlevels(as.factor(data2$category))*nObsType*.5, ncol(data2)))
colnames(to_add) <- colnames(data2)
to_add$category <- rep(levels(as.factor(data2$category)), each=empty_bar*nObsType*.5 )
data2 <- rbind(data2, to_add)

grpid = function(x) match(x, unique(x))
data2 <- data2 %>% mutate(group_id = group_indices(., category) %>% grpid)

#To group inverse and no inverse value
data2<- data2 %>% mutate(group_order=case_when(
  group_id == 1 ~ "A",
  TRUE ~ NA_character_ # all else are NA
))

data2 <- data2[order(data2$indicator),]

data2$id <- rep( seq(1, nrow(data2)/nObsType) , each=nObsType)

#Create labels for each column and angles (no need to adjust. With this method labels are aligned automatically)
label_data2 <- data2 %>% dplyr::group_by(id, indicator, raw_value) %>% dplyr::summarize(tot=sum(value))
number_of_bar2 <- nrow(label_data2)
angle2 <- 90 - 360 * (label_data2$id-0.5) /number_of_bar2     # I substract 0.5 because the letter must have the angle of the center of the bars. Not extreme right(1) or extreme left (0)
label_data2$hjust <- ifelse(angle2 < -90, 1, 0)
label_data2$angle <- ifelse(angle2 < -90, angle2+180, angle2)

# prepare a data frame for base lines
base_data2 <- data2 %>% 
  group_by(group_order) %>% 
  dplyr::summarize(start=min(id), end=max(id) 
            - empty_bar
          ) %>% 
  rowwise() %>% 
  mutate(title=mean(c(start, end)))

# prepare a data frame for grid (scales)
grid_data2 <- base_data2
grid_data2$end <- grid_data2$end[ c( nrow(grid_data2), 1:nrow(grid_data2)-1)] + 1.4
grid_data2$start <- grid_data2$start - .4
#grid_data2 <- grid_data2[-1,]

#Paste categories and raw values
data2$inv  <- ifelse(grepl("\\) \\*",data2$indicator), 1, 0)
data2$inv[is.na(data2$indicator)] <- NA

data2$cat <- paste(data2$observation,data2$group_order,data2$inv)

label_data2$ind_value<-paste(label_data2$raw_value, "-", label_data2$indicator)

r <- ggplot(data2) +      
  
  # Add the stacked bar
  geom_bar(aes(x=as.factor(id), y=value, fill=cat, colour=cat), stat="identity", alpha=0.5, size=0.2) +
  #scale_fill_manual(values=c("white","green3")) +
  scale_fill_manual(values=c("white","white","darkcyan","lightblue2")) +
  scale_colour_manual(values=c("black","black","black","black")) +

  # Add a val=100/75/50/25 lines. I do it at the beginning to make sur barplots are OVER it.
  #geom_segment(data=grid_data2, aes(x = end, y = 100, xend = start, yend = 100), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data2, aes(x = end, y = 80, xend = start, yend = 80), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data2, aes(x = end, y = 60, xend = start, yend = 60), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data2, aes(x = end, y = 40, xend = start, yend = 40), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data2, aes(x = end, y = 20, xend = start, yend = 20), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  
    geom_label(x = 0, y = 0, label = i, hjust=0.5, fontface="bold", size=10) +
    annotate("text", x = rep(max(data2$id),5), y = c(20, 40, 60, 80, 100), label = c("20", "40", "60", "80", "100") , color="grey", size=5 , angle=0, fontface="bold", hjust=.5) +
  
  ylim(0 , 120) +
  theme_minimal() +
  theme(
    legend.position = "none",
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = margin(-3,-3,-3,-3, "cm") 
  ) +
  coord_polar() +
  
   # Add labels on top of each bar
  
  geom_text(data=label_data2, aes(x=id, y=tot-50, label= str_wrap(ind_value, width = 22), hjust=label_data2$hjust), color="black", fontface="bold",alpha=1, size=pillartext, angle= label_data2$angle, inherit.aes = FALSE ) 


ggsave(r, file=paste0(dir_out, group,'/',i,"_score_graph_res_v",version,".png"), width=10, height=10)
ggsave(r, file=paste0(dir_out, group,'/',i,"_score_graph_res_v",version,".pdf"), width=10, height=10)

}

```



# Removing all temporary excels generated (leaving only tables and graphs)

```{r}


file.remove(paste0(dir_out, group,'/',i,"_percentil_v",version,".csv"))
file.remove(paste0(dir_out, group,'/',i,"_score_graphs_v",version,".csv"))


```


<!-- #Principal component contribution for version 2 using imputePCA -->
<!-- ```{r} -->

<!-- if (version == 2){ -->

<!-- country_all <- country_all[!is.na(country_all$Resilience_v2),] -->


<!-- RISE <- paste0(c("Resilience","Inclusion","Sustainability","Efficiency"),"_v2") -->

<!-- sensitivity <- select(country_all,RISE) -->
<!-- colnames(sensitivity) <- c("R","I","S","E") -->


<!-- lett <- c("R","I","S","E") -->
<!-- numm <- c("1","2","3","4")        -->

<!-- lettnumm <- CJ(lett, numm)[, paste(lett, numm,sep="")] -->

<!-- newcols0 <- tidyselect::vars_select(names(country_all), ends_with("_per")) -->
<!-- country_all5 <- select(country_all,newcols0) -->
<!-- newcols <- as.data.frame(sapply(lettnumm, function(x) rowMeans(country_all5[grep(x, names(country_all5))],na.rm=TRUE))) -->
<!-- newcols2 <- as.data.frame(sapply(lett, function(x) rowMeans(newcols[grep(x, names(newcols))],na.rm=TRUE))) -->


<!-- colnames(newcols2) <- paste0(c("R","I","S","E")," sc") -->


<!-- sensitivity <- cbind(sensitivity,newcols2) -->



<!-- library(pcaMethods) -->
<!-- library(grDevices) -->

<!-- #Set indicators categories -->

<!-- effi<- list("(E4) Agri. land productivity ($/ha)", "(E1) Agri. value added per worker", "(E4) Total GDP/GHG emissions", "(E2) Governance effectiveness", "(E2) Control of corruption", "(E2) Regulatory quality", "(E1) Logistic Performance Index", "(E3) Individuals using internet %", "(E3) Mobile cellular subscriptions (per 100 people)", "(E2) Rule of law", "(E3) Rapid transit to resident ratio (km/million)", "(E4) *Energy intensity (% change)", "(E1) Patents (per 100,000 people)",  "(E1) Digital Penetration Index", "(E4) Water productivity (GDP/m3)", "(E3) Shipping connectivity index") -->
<!-- effi <- paste0((effi),"_per") -->

<!-- pceffi <- select(country_all,effi) -->
<!-- names(pceffi) <- str_replace(names(pceffi),"_per","") -->
<!-- pceffi <- pceffi[rowSums(is.na(pceffi)) !=ncol(pceffi), ] -->

<!-- names(pceffi) <- c("Land prod", "Agri VA", "GDP/GHG", "Gov eff", "Corrupt", "Reg qual", "Log perf", "Internet", "Mobile", "Rule law", "Rapid trans", "Energ int", "Patents", "DAI", "Water eff","Shipping") -->



<!-- sust<-list("(S1) *PM2.5 mean annual exposure (\U00B5g/m3)", "(S4) *Forest loss %", "(S3) Renewable energy consumption %","(S2) Wastewater treatment capacity %","(S2) Waste properly managed %","(S2) *Municipal solid waste (kg/pc/day)","(S4) Biodiversity Habitat Index","(S4) Fisheries Index", "(S1) *GHG emissions per capita (% change)", "(S1) *CO2 emissions (MT pc)","(S3) *Ecological Footprint","(S3) *Water withdrawal per capita (m3/year pc)","(S4) *Chlorophyll-a deviations in coastal water %","(S1) *Mortality due to air pollution (per 100,000)","(S2) *Mortality due to unsafe WASH services (per 100,000)", "(S3) Water Quality SDG 6.3") -->
<!-- sust <- paste0((sust),"_per") -->

<!-- pcsust <- select(country_all,sust) -->
<!-- names(pcsust) <- str_replace(names(pcsust),"_per","") -->
<!-- pcsust <- pcsust[rowSums(is.na(pcsust)) !=ncol(pcsust), ] -->

<!-- names(pcsust) <- c("PM2.5", "Forest loss", "Renew energ", "Wastewat", "Waste prop", "Solid waste", "Biodiv", "Fish", "GHG growth", "CO2","Eco footprint","Wat withdraw","Chloroph","Deaths air","Deaths WASH", "Water qua") -->


<!-- incl<-list("(I1) *Extreme poverty headcount %", "(I2) Female labor participation %", "(I3) Human Capital Index", "(I1) *Gini Index","(I3) Secondary school enrollment %", "(I3) Immunization DPT %", "(I1) Account ownership (poorest 40%)","(I2) LGBT Acceptance Index", "(I2) Women, Business & Law Index", "(I1) *Refugees & IDPs index", "(I2) Women in national parliaments %", "(I4) Access to electricity %", "(I4) Basic access to sanitation %", "(I4) Basic access to water %", "(I4) Rural Access Index", "(I3) Universal health coverage (UHC) index %" ) -->
<!-- incl <- paste0((incl),"_per") -->
<!-- pcincl <- select(country_all,incl) -->
<!-- names(pcincl) <- str_replace(names(pcincl),"_per","") -->
<!-- pcincl <- pcincl[rowSums(is.na(pcincl)) !=ncol(pcincl), ] -->

<!-- names(pcincl) <- c("Extreme pov", "Female labor", "HCI", "Gini","Sec school", "Immuni", "Account poor","LGBT", "WBL", "Ref & IDPs", "Women gov", "Electricity", "Sanitation", "Water", "RAI", "UHC" ) -->



<!-- resi<-list("(R2) *Global Hunger Index", "(R2) *Deaths from conflict and terrorism (per 100,000)", "(R1) *Population affected by disasters %","(R2) *Proportion of urban population living in slums", "(R1) *Rainfall shock exposure %", "(R2) *Population exposed to epidemics (per 100,000)", "(R3) *Projected change of deaths from climate change induced diseases", "(R3) *Projected change of warm periods", "(R3) *Projected change of flood hazard", "(R4) *Dependency on external resource for health services", "(R4) *Food import dependency", "(R3) *Projected change of sea level rise impacts", "(R4) *Dependency on imported energy", "(R1) *IDPs due to natural disasters (cases per 100,000)", "(R1) *Water Stress SDG 6.4", "(R4) Physicians (per 1,000 people)") -->

<!-- resi <- paste0((resi),"_per") -->
<!-- pcresi <- select(country_all,resi) -->
<!-- names(pcresi) <- str_replace(names(pcresi),"_per","") -->
<!-- pcresi <- pcresi[rowSums(is.na(pcresi)) !=ncol(pcresi), ] -->

<!-- names(pcresi) <- c("GHI", "Conf terror", "Disasters","Urban slums", "Rainfall", "Epidemics", "Clim change disease", "Warm periods", "Flood hazard", "Depend health", "Food depend", "Sea level", "Depend energ", "IDPs disast", "Wat stress", "Physicians") -->

<!-- library(FactoMineR) -->
<!-- library(factoextra) -->
<!-- library(missMDA) -->
<!-- library(corrplot) -->

<!-- nb = estim_ncpPCA(pcresi,ncp.max=5) -->
<!-- res.comp = imputePCA(pcresi,ncp=4) -->
<!-- res.pca = PCA(res.comp$completeObs,ncp=4) -->
<!-- var <- get_pca_var(res.pca) -->


<!-- score <-  res.pca$ind$coord -->
<!-- scoreres <- as.data.frame(score[,1]) -->
<!-- colnames(scoreres) <- "R_pca" -->
<!-- scoreres$R_pca2 <- score[,1]+score[,2] -->
<!-- scoreres$R_pca4 <- rowSums(score) -->


<!-- head(var$contrib, 4) -->
<!-- pdf(file = paste0(dir_out,"pcacorr_resi.pdf")) -->
<!-- corrplot(var$contrib, method = "circle", tl.col="black",tl.cex =0.6,cl.cex=0.6,cl.align.text="l",col=c("azure1","aquamarine1","aquamarine3"), is.corr = FALSE ) -->


<!-- nb = estim_ncpPCA(pcincl,ncp.max=5) -->
<!-- res.comp = imputePCA(pcincl,ncp.max=5,ncp=4) -->
<!-- res.pca = PCA(res.comp$completeObs,ncp=4) -->
<!-- var <- get_pca_var(res.pca) -->

<!-- score <-  res.pca$ind$coord -->
<!-- scoreincl <- as.data.frame(score[,1]) -->
<!-- colnames(scoreincl) <- "I_pca" -->
<!-- scoreincl$I_pca2 <- score[,1]+score[,2] -->
<!-- scoreincl$I_pca4 <- rowSums(score) -->


<!-- pdf(file = paste0(dir_out,"pcacorr_incl.pdf")) -->
<!-- corrplot(var$contrib, method = "circle", tl.col="black",tl.cex =0.6,cl.cex=0.6,cl.align.text="l",col=c("floralwhite","lightcoral","red3"), is.corr = FALSE  ) -->



<!-- nb = estim_ncpPCA(pcsust,ncp.max=5) -->
<!-- res.comp = imputePCA(pcsust,ncp=4) -->
<!-- res.pca = PCA(res.comp$completeObs,ncp=4) -->
<!-- var <- get_pca_var(res.pca) -->

<!-- score <-  res.pca$ind$coord -->
<!-- scoresust <- as.data.frame(score[,1]) -->
<!-- colnames(scoresust) <- "S_pca" -->
<!-- scoresust$S_pca2 <- score[,1]+score[,2] -->
<!-- scoresust$S_pca4 <- rowSums(score) -->


<!-- pdf(file = paste0(dir_out,"pcacorr_sust.pdf")) -->
<!-- corrplot(var$contrib, method = "circle", tl.col="black",tl.cex =0.6,cl.cex=0.6,cl.align.text="l",col=c("lightgoldenrodyellow","lightgoldenrod","gold3"), is.corr = FALSE  ) -->


<!-- nb = estim_ncpPCA(pceffi,ncp.max=5) -->
<!-- res.comp = imputePCA(pceffi,ncp=4) -->
<!-- res.pca = PCA(res.comp$completeObs,ncp=4) -->
<!-- var <- get_pca_var(res.pca) -->

<!-- score <-  res.pca$ind$coord -->
<!-- scoreeff <- as.data.frame(score[,1]) -->
<!-- colnames(scoreeff) <- "E_pca" -->
<!-- scoreeff$E_pca2 <- score[,1]+score[,2] -->
<!-- scoreeff$E_pca4 <- rowSums(score) -->


<!-- pdf(file = paste0(dir_out,"pcacorr_effi.pdf")) -->
<!-- corrplot(var$contrib, method = "circle", tl.col="black",tl.cex =0.6,cl.cex=0.6,cl.align.text="l",col=c("pink","plum1","plum3"), is.corr = FALSE  ) -->


<!-- sensitivity <- cbind(sensitivity,scoreres,scoreincl,scoresust,scoreeff) -->

<!-- colnames(sensitivity) <- str_replace(colnames(sensitivity),"_"," ") -->

<!-- M <- as.matrix(sensitivity) -->



<!-- library(RColorBrewer) -->


<!-- M1 <- cor(M,use = "pairwise.complete.obs") -->
<!-- pdf(pointsize=3, file = paste0(dir_out,"sensitivity.pdf")) -->
<!-- corrplot.mixed(M1, number.cex = .8, order = "hclust",tl.col="black") -->



<!-- } -->
<!-- ``` -->




<!-- # Additional analysis for Egypt -->
<!-- ```{r} -->
<!-- #Compare against countries with higher GDP per capita growth Vietnam, Peru, Indonesia -->

<!-- i="EGY" -->

<!-- country_long<-country_long_complete -->

<!-- country_long<-country_long%>% filter(str_detect(pillar, "v1")) -->
<!-- median_income_filter<-median_income_long %>% filter(str_detect(pillar, "v1")) -->

<!-- regional_group_df<-country_long%>% -->
<!--   filter(iso3 == i)%>% -->
<!--   select(region_red) -->

<!-- regional_group<-regional_group_df[1,1] -->

<!-- #Filter country and arrange percentiles values for graph (since it is a facet graph, percentil arrange gets messy) -->
<!-- #Establish regional group beforehand -->
<!-- country_long<-country_long%>% -->
<!--   dplyr::filter(region_red==regional_group)%>% -->
<!--   dplyr::filter(!is.na(percentil))%>% -->
<!--   ungroup() %>% -->
<!--   arrange(pillar, (desc(percentil)))%>% -->
<!--   mutate(r = row_number())%>% -->
<!--   mutate(pillar_name = str_replace(pillar, "_v0|_v1", "")) -->

<!-- country_long$pillar_name_f<- factor(country_long$pillar_name, levels= c("Resilience", "Inclusion", "Sustainability", "Efficiency")) -->

<!-- country_comparators<-country_long_complete%>% -->
<!--   filter(iso3 %in% c("IDN", "VNM", "PER"))%>% -->
<!--   filter(str_detect(pillar, "v1"))%>% -->
<!--   mutate(pillar_name = str_replace(pillar, "_v0|_v1", "")) -->
<!-- country_comparators$pillar_name_f<- factor(country_comparators$pillar_name, levels= c("Resilience", "Inclusion", "Sustainability", "Efficiency")) -->

<!-- #Once filtered by region, get regional median graph and for the next graph -->
<!-- country_long<-country_long%>% -->
<!--   group_by(pillar)%>% -->
<!--   mutate(median_regional= median(percentil, na.rm=T)) -->

<!-- # prepare regional median for next graph -->
<!-- regional_median<-country_long%>% -->
<!--   group_by(pillar)%>% -->
<!--   dplyr::summarise(percentil_median= median(percentil, na.rm=T))%>% -->
<!--   mutate(group = regional_group)%>% -->
<!--   select(group, everything()) -->

<!-- #Median_income database -->
<!-- country_long_median<-country_long%>% -->
<!--   filter(iso3 == i) -->


<!-- #Rename col, add iso3 and merge bases -->

<!-- colnames(median_income_filter)<-c("group", "pillar", "percentil_median") -->
<!-- median_income_filter$iso3<-"AAAA" # name like this to make sure it mantains graph color order -->

<!-- regional_median$iso3<-"AAAA" # name like this to make sure it mantains graph color order -->

<!-- country_median_filter<-country_long_median%>% -->
<!--   dplyr::select(country, pillar, percentil, iso3) -->
<!-- colnames(country_median_filter)<-c("group",  "pillar", "percentil_median", "iso3") -->

<!-- #Merge regional median/income median/country median -->
<!-- graph_bar3<-rbind(country_median_filter, median_income_filter, regional_median) -->

<!-- #Prepare for graph -->
<!-- graph_bar3<-graph_bar3%>% -->
<!--   dplyr::filter(!is.na(percentil_median))%>% -->
<!--   ungroup() %>% -->
<!--   arrange(pillar, (desc(percentil_median)))%>% -->
<!--   mutate(r = row_number())%>% -->
<!--   mutate(pillar_name = str_replace(pillar, "_v0|_v1", "")) -->

<!-- graph_bar3$pillar_name_f<- factor(graph_bar3$pillar_name, levels= c("Resilience", "Inclusion", "Sustainability", "Efficiency")) -->

<!-- graph3  <-  ggplot(graph_bar3, aes(x = r, y = percentil_median*100, fill = pillar_name_f, color = as.factor(iso3))) + -->
<!--   geom_col(size=1.2, alpha=0.7)+ -->
<!--   geom_hline(data=country_comparators, aes(yintercept = percentil*100, linetype= as.factor(iso3)), size=1.5)+ -->
<!--   facet_grid(~pillar_name_f, scales = "free")+ -->
<!--   #scale_y_continuous(labels = value, breks= value)+ -->
<!--     labs(y = "Median percentil rank", -->
<!--   title = "")+ -->
<!-- theme_minimal()+ -->
<!--   theme(strip.text.x = element_text(size = 19, face = "bold"), -->
<!--   axis.text.y = element_text(size = 16, hjust = .5, vjust = .5), -->
<!--   plot.title=element_text(size=14, face = "bold"), -->
<!--                axis.title.x=element_blank(), -->
<!--   axis.text.x = element_text(size= 14), -->
<!--                  legend.position = "none", -->
<!--   panel.grid.minor = element_blank(), -->
<!--   panel.grid.major = element_blank())+ -->
<!--   scale_fill_manual(values = c("darkcyan", "red2" ,"goldenrod1", "darkmagenta"))+ -->
<!--   scale_color_manual(values=c("grey25", "green3" -->
<!--                              # , "grey17", "hotpink1", "blue" -->
<!--                              ))+ -->
<!--   scale_linetype_manual(values=c("solid", "twodash", "dotted"))+ -->
<!--   scale_x_continuous(breaks = graph_bar3$r, labels = str_wrap(graph_bar3$group, width = 7)) + -->
<!--   geom_text(aes(x=r, y=(percentil_median*100)+3 , label= as.integer(percentil_median*100)), color="black",alpha=1, size=6, inherit.aes = FALSE ) -->

<!-- ggsave(graph3, file=paste0(dir_out, group,'/',i,"_barplot_per_comparison_v1_color.png"), width=25, height=10) -->
<!-- #"chocolate1", "hotpink1", "blue" -->
<!-- ``` -->




<!-- # Additional analysis (Comparative measures of Water efficiency and land efficiency) -->
<!-- ```{r} -->

<!-- i="MAR" -->
<!-- #Get country income group -->
<!-- income_country<-country_all%>% filter(iso3==i)%>% summarise((income_red)) -->
<!-- income_country<-income_country[1,1] -->

<!-- #Get country aspiratinal group -->
<!-- income_aspi<-country_all%>% filter(iso3==i)%>% summarise((income_aspiration)) -->
<!-- income_aspi<-income_aspi[1,1] -->

<!-- #Get country aspiratinal group -->
<!-- region<-country_all%>% filter(iso3==i)%>% summarise((region_red)) -->
<!-- region_g<-region[1,1] -->

<!-- #Pull country data -->
<!-- country_val<- read.csv(file=paste0(dir_out, group,'/',i,"_percentil.csv"), header=TRUE, sep=",")%>% -->
<!--   select(-percentil) -->

<!-- country_val<-country_val%>% -->
<!-- filter(indicator == "Water use efficiency (USD/m3)"| indicator == "Agri. land productivity ($/ha)") -->
<!-- colnames(country_val)[colnames(country_val)=="raw_value"] <- "value" -->
<!-- country_val$region<- i   -->
<!-- country_val$category<-NULL -->

<!-- #country_aspi -->
<!-- income_info_country<-income_info%>% -->
<!--   filter(income_red == income_country | income_red == income_aspi) -->

<!-- income_info_country<-income_info_country%>% -->
<!--   filter(indicator == "Water use efficiency (USD/m3)"| indicator == "Agri. land productivity ($/ha)") -->

<!-- income_info_country<-income_info_country%>% -->
<!--   select(indicator, median, income_red) -->
<!-- colnames(income_info_country)<-c("indicator", "value", "region") -->

<!-- mena_info <- country_all%>%  group_by(region_red)%>% -->
<!--   select(-matches('_per'))%>% dplyr::summarise(across(where(is.numeric), list(median= ~median(., na.rm = T)), .names = "{col}")) -->
<!-- mena_info<- reshape2::melt(mena_info, id.vars=c("region_red"), variable.name="indicator", value.name="median") -->
<!-- mena_info<-mena_info%>% -->
<!--   filter(region_red== region_g)%>% -->
<!-- filter(indicator == "Water use efficiency (USD/m3)"| indicator == "Agri. land productivity ($/ha)") -->
<!-- mena_info<-mena_info%>% -->
<!--   select(indicator, median, region_red) -->

<!-- colnames(mena_info)<-c("indicator", "value", "region") -->
<!-- graph_eff<-rbind(mena_info, income_info_country, country_val) -->

<!-- graph_eff$value<-as.numeric(graph_eff$value) -->
<!-- graph_eff$value<-format(round(graph_eff$value, 2), nsmall = 2) -->
<!-- graph_eff$value<-as.numeric(graph_eff$value) -->

<!-- graph_eff%>% -->
<!--   filter(indicator == "Water use efficiency (USD/m3)")%>% -->
<!--   filter(region != region_g)%>% -->
<!-- ggplot(aes(x = reorder(region, -value), y = value)) +  -->
<!--     geom_bar(stat = "identity",position = "dodge", fill="steelblue")+ -->
<!--     geom_text(aes(label=value), position=position_dodge(width=0.9), vjust=-0.25, size= 3)+ -->
<!--   labs( -->
<!--   y = "(USD/m3)", -->
<!--   x= "", -->
<!--   title = "Water use efficiency (USD/m3)", -->
<!--   caption= "Source: FAO, 2017")+ -->
<!--   theme_light() -->
<!-- ggsave(paste0(dir_out, "Water_Efficiency", i, ".png"), height=6, width = 8, units = c("in")) -->

<!-- graph_eff%>% -->
<!--   filter(indicator == "Agri. land productivity ($/ha)")%>% -->
<!--   #filter(region != region_g)%>% -->
<!-- ggplot(aes(x = reorder(region, -value), y = value)) +  -->
<!--     geom_bar(stat = "identity",position = "dodge", fill="darkcyan")+ -->
<!--   geom_text(aes(label=value), position=position_dodge(width=0.9), vjust=-0.25, size= 3)+ -->
<!--   labs( -->
<!--   y = "$/ha", -->
<!--   x= "", -->
<!--   title = "Agri. land productivity ($/ha)", -->
<!--   caption= "Source: Calculations using Gross Production Value and Total Agricultural Land from FAO, 2016")+ -->
<!--   theme_light() -->
<!-- ggsave(paste0(dir_out, "Land productivity", i, ".png"), height=6, width = 8, units = c("in")) -->

<!-- graph_eff%>% -->
<!--   filter(indicator == "Agri. land productivity ($/ha)")%>% -->
<!--   filter(region != region_g)%>% -->
<!-- ggplot(aes(x = reorder(region, -value), y = value)) +  -->
<!--     geom_bar(stat = "identity",position = "dodge", fill="darkcyan")+ -->
<!--     geom_text(aes(label=value), position=position_dodge(width=0.9), vjust=-0.25, size= 3)+ -->
<!--   labs( -->
<!--   y = "$/ha", -->
<!--   x= "", -->
<!--   title = "Agri. land productivity ($/ha)", -->
<!--   caption= "Source: Calculations using Gross Production Value and Total Agricultural Land from FAO, 2016")+ -->
<!--   theme_light() -->

<!-- ggsave(paste(dir_out, "Land productivity", "income",i , ".png"), height=6, width = 8, units = c("in")) -->
<!-- ``` -->

