---
title: "Benchmarking_Graphs"
author: "Evelyn Sanchez"
date: "10/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = "C:/User/####/OneDrive/")
```

```{r}
library(WDI)
library(dplyr)
library(readxl)
library(rvest)
library(tidyverse)
library(data.table)
library(ggplot2)
library(grid)
library(Hmisc)
#detach(package:plyr) ---- DETACH OR SOME FORMULAS WONT WORK
```

# Set Directories
```{r}
dir_int<-"./My Files/Integrated data/"  #Folder with data generated in code Benchmarking_Data_V3        
dir_out<-"./My Files/Output/"
#In your coumputer, in this directory create separate folders for income group - ex: ./My Files/Output/lmic -./My Files/Output/umic, etc, in oder to save countries info per income group
getwd()
```
# Create list of countries per income group
```{r}
# Load country dataset to create list of countries used in the loop

country_estimates_global <- read.csv(paste0(dir_int, "World_SD_values_V4.csv"))

# Lower MICS
country_estimates <- country_estimates_global %>% filter(income=='Lower middle income')
lmics <- unique(country_estimates$iso3)
lmics <- as.character(lmics)

# Low income
country_estimates <- country_estimates_global %>% filter(income=='Low income')
linc <- unique(country_estimates$iso3)
linc <- as.character(linc)

# Upper MICS
country_estimates <- country_estimates_global %>% filter(income=='Upper middle income')
umics <- unique(country_estimates$iso3)
umics <- as.character(umics)

# Lower MICS
country_estimates <- country_estimates_global %>% filter(income=='Lower middle income')
lmics <- unique(country_estimates$iso3)
lmics <- as.character(lmics)

```

# Set comparators -INCOME GROUP and REGIONAL GROUP and VERSION
```{r}
#Income group (select same category)
country <- lmics ### HERE CHOOSE INCOME GROUP WE WANT TO COMPARE TO FROM ABOVE VARIABES ###
group <- 'lmics' ### HERE CHOOSE INCOME GROUP WE WANT TO COMPARE TO FROM ABOVE VARIABES ###

#Set files names to read according to comparison groups
comparison_percentile <- paste0('DB_SD_',group,'_score')
comparison_score <- paste0('DB_SD_',group,'_score')

### Version indicator
#choose 0 or 1. 
#v= 0 Refers to a set of indicators selected and vetted by the Chief Economist Office -Sustainable Development (work lead by Jason Daniel Russ)
# v=1 refers to a set of indicators selected by the MENA - Sustainable Development team focusing on Egypt results 
#Each version would show a different set of indicators
version <- 1 # or 1
```

# Country Percentil dataset: clean and prepare 
Here we rename the variables of the raw values and the percetile ranking (all variables from the two versions)
```{r}
### COUNTRY Percentile DATASET ### 
###         World              ###

#Load raw and percentile value data generated before 
country_all <- read.csv(paste0(dir_int,"World_SD_values_V4.csv"))

#Arrange values 
country_all$pop_dis<-as.numeric(as.character(country_all$pop_dis))
country_all$pop_dis<-format(round(country_all$pop_dis, 2), nsmall = 2)


#Assign names to variables
#Resilience
colnames(country_all)<-str_replace(colnames(country_all), "food_sec", "Food Security Index")
colnames(country_all)<-str_replace(colnames(country_all), "risk_wellbeing", "*Risk to wellbeing %")
colnames(country_all)<-str_replace(colnames(country_all), "risk_to_assets", "*Risk to asset %")
colnames(country_all)<-str_replace(colnames(country_all), "pop_dis", "*Pop. affected by disasters %")
colnames(country_all)<-str_replace(colnames(country_all), "EN.POP.SLUM.UR.ZS", "*Urban slum population %")
colnames(country_all)<-str_replace(colnames(country_all), "rain_exp", "*Rainfall shock exposure %")

#Inclusion
colnames(country_all)<-str_replace(colnames(country_all), "pov_1016", "*Poverty headcount %")
colnames(country_all)<-str_replace(colnames(country_all), "SL.TLF.CACT.FE.ZS", "Female labor part.%")
colnames(country_all)<-str_replace(colnames(country_all), "SH.STA.SMSS.ZS", "Safely managed sanitation %")
colnames(country_all)<-str_replace(colnames(country_all), "SH.H2O.SMDW.ZS", "Safely managed drinking water %")
colnames(country_all)<-str_replace(colnames(country_all), "HD.HCI.OVRL", "Human Capital index")
colnames(country_all)<-str_replace(colnames(country_all), "SI.POV.GINI", "*Gini index")
colnames(country_all)<-str_replace(colnames(country_all), "SE.SEC.ENRR", "Secondary school enrollment %")
colnames(country_all)<-str_replace(colnames(country_all), "SH.IMM.IDPT", "Immunization DPT %")
colnames(country_all)<-str_replace(colnames(country_all), "account.t.d.7", "Account income, poorest 40%")
colnames(country_all)<-str_replace(colnames(country_all), "LGBT_acc", "LGBT acceptance index")
colnames(country_all)<-str_replace(colnames(country_all), "wbl", "Women, Business & Law index")
colnames(country_all)<-str_replace(colnames(country_all), "trust_ppl", "Most ppl. can be trusted %")
colnames(country_all)<-str_replace(colnames(country_all), "ref_idp", "*Refugees & IDPs index")
colnames(country_all)<-str_replace(colnames(country_all), "sec_aparat", "*Security apparatus index")

#Sustainability

colnames(country_all)<-str_replace(colnames(country_all), "NY.ADJ.SVNG.GN.ZS", "Adjusted net savings %")
colnames(country_all)<-str_replace(colnames(country_all), "EN.ATM.PM25.MC.M3", "*PM2.5 mean annual exposure mg/m3")
colnames(country_all)<-str_replace(colnames(country_all), "EG.FEC.RNEW.ZS", "Renewal energy consumption %")
colnames(country_all)<-str_replace(colnames(country_all), "ER.H2O.INTR.PC", "Renewal internal freshwater(pc)")
colnames(country_all)<-str_replace(colnames(country_all), "wat_qua", "Water Quality SDG 6.3")
colnames(country_all)<-str_replace(colnames(country_all), "WWT.new", "Wastewater treated %")
colnames(country_all)<-str_replace(colnames(country_all), "waste_managed", "Waste properly managed %")
colnames(country_all)<-str_replace(colnames(country_all), "waste_rate", "*Municipal soild waste (kg/pc/day)")
colnames(country_all)<-str_replace(colnames(country_all), "BHV.new", "Biodiversity & Habitat index")
colnames(country_all)<-str_replace(colnames(country_all), "FSH.new", "Fisheries index")
colnames(country_all)<-str_replace(colnames(country_all), "GIB.new", "*GHG intensity growth rate")
colnames(country_all)<-str_replace(colnames(country_all), "EN.ATM.CO2E.PC", "*CO2 emissions (mtr/ton pc)")

#Indicators no longer use in any version
#colnames(country_all)<-str_replace(colnames(country_all), "forest_loss", "Forest loss")
#colnames(country_all)<-str_replace(colnames(country_all), "DT.TDS.DECT.GN.ZS", "Total debt service")

#Inclusion
colnames(country_all)<-str_replace(colnames(country_all), "agri_land", "Agri. land productivity $/ha")
colnames(country_all)<-str_replace(colnames(country_all), "agri_value", "Agri. value added per worker $")
colnames(country_all)<-str_replace(colnames(country_all), "gini_ghg", "Total GNI/GHG emission")
colnames(country_all)<-str_replace(colnames(country_all), "gov_effect", "Governance effectivness")
colnames(country_all)<-str_replace(colnames(country_all), "cont_corr", "Control of corruption")
colnames(country_all)<-str_replace(colnames(country_all), "reg_qua", "Regulatory quality")
colnames(country_all)<-str_replace(colnames(country_all), "lpi_score", "Logistic performance index")
colnames(country_all)<-str_replace(colnames(country_all), "sdg9_intuse", "Pop. using internet %")
colnames(country_all)<-str_replace(colnames(country_all), "lpi_score", "Logistic performance index")
colnames(country_all)<-str_replace(colnames(country_all), "Tenure.insecurity", "*Tenure insecurity %")
colnames(country_all)<-str_replace(colnames(country_all), "water_efficiency_FAO", "Water use efficiency (USD/m3)")
colnames(country_all)<-str_replace(colnames(country_all), "water_efficiency_ceo", "Water use efficiency (GNI/m3)")

```

# Get the aggregate values of median/sd for each income group (to use in the table comparison)
```{r}
options(scipen=999) #remove scientific notation

#Short income group name for graphs
country_all$income_red <- ifelse(country_all$income == "High income", "HIC",
                                ifelse(country_all$income ==  "Upper middle income", 'UMIC',
                                       ifelse(country_all$income ==  "Lower middle income", 'LMIC',
                                               ifelse(country_all$income ==  "Low income", 'LIC', 'Other'))))

#Aspirational income group: income group "one level up"
country_all$income_aspiration <- ifelse(country_all$income_red == "HIC", "HIC",
                                ifelse(country_all$income_red == 'UMIC', "HIC", 
                                       ifelse(country_all$income_red == 'LMIC', 'UMIC',
                                               ifelse(country_all$income_red == 'LIC', 'LMIC', 'Other'))))


#Short regional group for graphs
country_all$region_red <- ifelse(country_all$region == "South Asia", "SSA",
                                ifelse(country_all$region ==  "Europe & Central Asia", 'ECA',
                                       ifelse(country_all$region ==  "Middle East & North Africa", 'MENA',
                                              ifelse(country_all$region ==  "Sub-Saharan Africa", 'SSA',
                                                     ifelse(country_all$region ==  "Latin America & Caribbean", 'LAC',
                                                        ifelse(country_all$region ==  "East Asia & Pacific", 'EAP',  
                                               ifelse(country_all$region ==  "North America", 'NAC', 'Other')))))))


#Make people affected by disaster numeric
country_all$`*Pop. affected by disasters %`<-as.numeric(as.character(country_all$`*Pop. affected by disasters %`))


# MEDIAN
income_median <- country_all%>%  group_by(income_red)%>%
  select(-matches('_per'))%>% dplyr::summarise(across(where(is.numeric), list(median= ~median(., na.rm = T)), .names = "{col}"))
income_median<- reshape2::melt(income_median, id.vars=c("income_red"), variable.name="indicator", value.name="median")

#MEAN
income_mean <- country_all%>%group_by(income_red)%>%
  select(-matches('_per'))%>% dplyr::summarise(across(where(is.numeric), list(mean= ~mean(., na.rm = T)), .names = "{col}"))
income_mean<- reshape2::melt(income_mean, id.vars=c("income_red"), variable.name="indicator", value.name="mean")

#SD
income_sd <- country_all%>% group_by(income_red)%>%
  select(-matches('_per'))%>% dplyr::summarise(across(where(is.numeric), list(sd= ~sd(., na.rm = T)), .names = "{col}"))
income_sd<- reshape2::melt(income_sd, id.vars=c("income_red"), variable.name="indicator", value.name="sd")

#Merge MEAN, MEDIAN, SD 
income_info <- merge(income_mean, income_median) %>%  merge(income_sd)

#Get ranges for SD  (Mean) - Later use to estimate if the countries value is one standar deviation above or below, or within one SD of the Mean
income_info$sd_mean_up<-income_info$mean + income_info$sd
income_info$sd_mean_down<-income_info$mean - income_info$sd

##Get ranges for SD  (Median) -Later use to estimate if the countries value is one standar deviation above or below, or within one SD of the Median
income_info$sd_median_up<-income_info$median + income_info$sd
income_info$sd_median_down<-income_info$median - income_info$sd
```

# Prepare data for PERCENTILE RANKING BAR GRAPH
```{r}
#Duplicate a version of country_all for transformation- country_all needs to remain the same to be use in the percentil rank graph
country_all2<-country_all

#Select ranking values
country_all2<-country_all2%>% select(country, iso3, income_red, region_red, Resilience_v0, Resilience_v1, Inclusion_v0, Inclusion_v1, Sustainability_v0, Sustainability_v1, Efficiency_v0, Efficiency_v1)

#Tranform to long format for graph
country_long_complete <- reshape2::melt(country_all2,
        # ID variables - all the variables to keep but not split apart on
    id.vars=c("country", "iso3","income_red", "region_red"),
    variable.name="pilar",
    value.name="percentil"
)

#Get the median value for income group & transform to long format - this would be use for the graph bars 
median_income<- country_all2 %>%
  group_by(income_red)%>%
    dplyr::summarise(across(where(is.numeric), function(x){ median(x, na.rm=TRUE)}))

median_income_long <- reshape2::melt(median_income,
        # ID variables - all the variables to keep but not split apart on
    id.vars=c("income_red"),
    variable.name="pilar",
    value.name="median_income")

#Join data 
country_long_complete<-left_join(country_long_complete, median_income_long, by=c("pilar", "income_red"))
```

# From this point the selection between version 1 or 0 will affect the outcomes 

# Function for PERCENTILE RANKING BAR GRAPH
```{r}
for(i in country){
  #Duplicate  a version of country long for subsetting 
  country_long<-country_long_complete
  
if (version == 0){
  
country_long<-country_long%>% filter(str_detect(pilar, "v0"))
median_income_filter<-median_income_long%>% filter(str_detect(pilar, "v0"))

} else {
country_long<-country_long%>% filter(str_detect(pilar, "v1"))
median_income_filter<-median_income_long %>% filter(str_detect(pilar, "v1"))
}

#Get varible to identify the country in the graph
country_long<-country_long%>%
  mutate(country_ind = ifelse(iso3 == i , 1, 0))

##Get regional group
regional_group_df<-country_long%>%
  filter(iso3 == i)%>%
  select(region_red)

regional_group<-regional_group_df[1,1]

#Filter country and arrange percentiles values for graph (since it is a facet graph, percentil arrange gets messy)
#Establish regional group beforehand
country_long<-country_long%>%
  dplyr::filter(region_red==regional_group)%>%
  dplyr::filter(!is.na(percentil))%>%
  ungroup() %>%
  arrange(pilar, (desc(percentil)))%>%
  mutate(r = row_number())%>%
  mutate(pilar_name = str_replace(pilar, "_v0|_v1", ""))

country_long$pilar_name_f<- factor(country_long$pilar_name, levels= c("Resilience", "Inclusion", "Sustainability", "Efficiency"))

#Once filtered by region, get regional median graph and for the next graph  
country_long<-country_long%>%
  group_by(pilar)%>%
  mutate(median_regional= median(percentil, na.rm=T))

# prepare regional median for next graph 
regional_median<-country_long%>%
  group_by(pilar)%>%
  dplyr::summarise(percentil_median= median(percentil, na.rm=T))%>%
  mutate(group = regional_group)%>%
  select(group, everything())

#Median_income database 
country_long_median<-country_long%>%
  filter(iso3 == i)

  
#Graph regional comparison percentil ranking
reg<-  ggplot(country_long, aes(x = r, y = percentil*100, fill = pilar_name_f, color = as.factor(country_ind), group=income_red)) + 
  geom_col(size=1.2, alpha=0.7)+
  #Blue line REGIONAL MEDIAN -ADD LINE LEGENDS IN PPT
  geom_hline(aes(yintercept = median_regional*100), color="turquoise3", size=1.5)+ 
  #Grey line INCOME MEDIAN- ADD LINE LEGENDS IN PPT
  geom_hline(data=country_long_median, aes(yintercept = median_income*100), color="grey", size=1.5)+ 
  facet_grid(~pilar_name_f, scales = "free")+
  #scale_y_continuous(labels = value, breks= value)+
    labs(y = "Percentil rank in the world",
  title = "")+
theme_minimal()+
  theme(strip.text.x = element_text(size = 19, face = "bold"),
  axis.text.y = element_text(size = 14, hjust = .5, vjust = .5),
  plot.title=element_text(size=14, face = "bold"),
               axis.title.x=element_blank(),
  axis.text.x = element_text(angle = 90, hjust = 1, size= 14),
                 legend.position = "none",
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank())+
  scale_fill_manual(values = c("darkcyan", "red2" ,"darkorange", "darkmagenta"))+
  scale_color_manual(values=c("grey25","greenyellow"))+
  scale_x_continuous(breaks = country_long$r, labels = country_long$country) +
  geom_text(aes(x=r, y=(percentil*100)+3 , label= as.integer(percentil*100)), color="black",alpha=1, size=6, inherit.aes = FALSE )
  
if (version == 0){
ggsave(reg, file=paste0(dir_out, group,'/',i,"_barplot_per_v0.png"), width=25, height=10)
} else {
 ggsave(reg, file=paste0(dir_out, group,'/',i,"_barplot_per_v1.png"), width=25, height=10) 
}

#Rename col, add iso3 and merge bases

colnames(median_income_filter)<-c("group", "pilar", "percentil_median")
median_income_filter$iso3<-"AAAA" # name like this to make sure it mantains graph color order

regional_median$iso3<-"AAAA" # name like this to make sure it mantains graph color order

country_median_filter<-country_long_median%>%
  dplyr::select(country, pilar, percentil, iso3)
colnames(country_median_filter)<-c("group",  "pilar", "percentil_median", "iso3")

#Merge regional median/income median/country median
graph_bar2<-rbind(country_median_filter, median_income_filter, regional_median)

#Prepare for graph
graph_bar2<-graph_bar2%>%
  dplyr::filter(!is.na(percentil_median))%>%
  ungroup() %>%
  arrange(pilar, (desc(percentil_median)))%>%
  mutate(r = row_number())%>%
  mutate(pilar_name = str_replace(pilar, "_v0|_v1", ""))

graph_bar2$pilar_name_f<- factor(graph_bar2$pilar_name, levels= c("Resilience", "Inclusion", "Sustainability", "Efficiency"))

graph2  <-  ggplot(graph_bar2, aes(x = r, y = percentil_median*100, fill = pilar_name_f, color = as.factor(iso3))) + 
  geom_col(size=1.2, alpha=0.7)+
  #Red line (m)
  geom_hline( yintercept = 50 , color="red3", size=1)+ 
  facet_grid(~pilar_name_f, scales = "free")+
  #scale_y_continuous(labels = value, breks= value)+
    labs(y = "Median percentil rank",
  title = "")+
theme_minimal()+
  theme(strip.text.x = element_text(size = 19, face = "bold"),
  axis.text.y = element_text(size = 16, hjust = .5, vjust = .5),
  plot.title=element_text(size=14, face = "bold"),
               axis.title.x=element_blank(),
  axis.text.x = element_text(size= 14),
                 legend.position = "none",
  panel.grid.minor = element_blank(), 
  panel.grid.major = element_blank())+
  scale_fill_manual(values = c("darkcyan", "red2" ,"darkorange", "darkmagenta"))+
  scale_color_manual(values=c("grey25", "green3"))+
  scale_x_continuous(breaks = graph_bar2$r, labels = str_wrap(graph_bar2$group, width = 7)) +
  geom_text(aes(x=r, y=(percentil_median*100)+3 , label= as.integer(percentil_median*100)), color="black",alpha=1, size=6, inherit.aes = FALSE )
  
if (version == 0){
ggsave(graph2, file=paste0(dir_out, group,'/',i,"_barplot_per_group_v0.png"), width=25, height=10)
} else {
 ggsave(graph2, file=paste0(dir_out, group,'/',i,"_barplot_per_group_v1.png"), width=25, height=10) 
}

} 

```


# Loop to prepare data for SCORE PILARS COMPARISON GRAPH - CIRCULAR (PER PILARS)
```{r}
### COUNTRY Percentile DATASET ###

for(i in country){

country_tot<-country_all  
country_tot<- country_tot[country_tot$iso3 == i, ]
country_percent<-country_tot %>% select(matches('_per'))
country_percent <- as.data.frame(t(as.matrix(country_percent)))
country_percent <- country_percent %>% rownames_to_column("indicator")
colnames(country_percent)<-c("indicator", "percentil")
country_percent$indicator<-str_replace(country_percent$indicator, "_per", "")


#### Country Data Raw values ####

country_values<-country_tot %>% select(-matches('_per'))
country_values <- as.data.frame(t(as.matrix(country_values)))
country_values <- country_values %>% rownames_to_column("indicator")
colnames(country_values)<-c("indicator", "raw_value")


#Set indicators categories

efficiency<-c("Agri. land productivity $/ha", "Agri. value added per worker $", "Total GNI/GHG emission","Governance effectivness", "Control of corruption",  "Regulatory quality", "Logistic performance index", "Pop. using internet %", "Water use efficiency (USD/m3)", "Logistic performance index", "*Tenure insecurity %", "Water use efficiency (USD/m3)", "Water use efficiency (GNI/m3)")

sustainability<-c("Adjusted net savings %", "*PM2.5 mean annual exposure mg/m3", "Renewal energy consumption %", "Renewal internal freshwater(pc)", "Water Quality SDG 6.3", "Wastewater treated %", "Waste properly managed %", "*Municipal soild waste (kg/pc/day)", "Biodiversity & Habitat index", "Fisheries index", "*GHG intensity growth rate", "*CO2 emissions (mtr/ton pc)")

inclusion<-c("*Poverty headcount %", "*Gini index", "Immunization DPT %", "Safely managed sanitation %", "Safely managed drinking water %", "Immunization DPT %",  "Secondary school enrollment %", "Human Capital index", 'Account income, poorest 40%', "Female labor part.%", "Women, Business & Law index",  "LGBT acceptance index",  "Most ppl. can be trusted %", "*Refugees & IDPs index", "*Security apparatus index" )

resilience<-c("Food Security Index", "*Risk to wellbeing %", "*Risk to asset %","*Pop. affected by disasters %", "*Rainfall shock exposure %", "*Urban slum population %")


#Assign categories (number set to appear in the RISE order in the graph)

country_percent$category <- ifelse(country_percent$indicator %in% efficiency, '2.Efficiency',
                                   ifelse(country_percent$indicator %in% sustainability, '3.Sustainability',
                                          ifelse(country_percent$indicator %in% resilience, '4.Resilience', 
                                                 ifelse(country_percent$indicator %in% inclusion, '1.Inclusion', 'Other'))))

country_percent <- country_percent%>% filter(category!='Other') 

#Join percentage and raw value
country_percent <-left_join(country_percent, country_values, by="indicator")
country_percent$raw_value<-as.numeric(as.character(country_percent$raw_value))
country_percent$raw_value<-format(round(country_percent$raw_value, 2), nsmall = 2)


# Format score data for graphs
#country_percent <- country_percent[,c(3,1,2,4)]
country_percent$percentil <- as.numeric(as.character(country_percent$percentil))
country_percent$percentil<-country_percent$percentil*100
country_percent <- country_percent[order(country_percent$category),]

#create first databases for percentil ranking (global)

country_percent$percentil<-as.integer(country_percent$percentil)
country_percent<-country_percent%>% select(indicator, percentil, raw_value, category)
write.csv(country_percent,paste0(dir_out, group,'/',i,"_percentil.csv"), row.names = FALSE)


### COUNTRY SCORE DATASET ###

country_score <- read.csv(paste0(dir_int, comparison_score,".csv"))


#Assign names to variables
#Resilience
colnames(country_score)<-str_replace(colnames(country_score), "food_sec", "Food Security Index")
colnames(country_score)<-str_replace(colnames(country_score), "risk_wellbeing", "*Risk to wellbeing %")
colnames(country_score)<-str_replace(colnames(country_score), "risk_to_assets", "*Risk to asset %")
colnames(country_score)<-str_replace(colnames(country_score), "pop_dis", "*Pop. affected by disasters %")
colnames(country_score)<-str_replace(colnames(country_score), "EN.POP.SLUM.UR.ZS", "*Urban slum population %")
colnames(country_score)<-str_replace(colnames(country_score), "rain_exp", "*Rainfall shock exposure %")

#Inclusion
colnames(country_score)<-str_replace(colnames(country_score), "pov_1016", "*Poverty headcount %")
colnames(country_score)<-str_replace(colnames(country_score), "SL.TLF.CACT.FE.ZS", "Female labor part.%")
colnames(country_score)<-str_replace(colnames(country_score), "SH.STA.SMSS.ZS", "Safely managed sanitation %")
colnames(country_score)<-str_replace(colnames(country_score), "SH.H2O.SMDW.ZS", "Safely managed drinking water %")
colnames(country_score)<-str_replace(colnames(country_score), "HD.HCI.OVRL", "Human Capital index")
colnames(country_score)<-str_replace(colnames(country_score), "SI.POV.GINI", "*Gini index")
colnames(country_score)<-str_replace(colnames(country_score), "SE.SEC.ENRR", "Secondary school enrollment %")
colnames(country_score)<-str_replace(colnames(country_score), "SH.IMM.IDPT", "Immunization DPT %")
colnames(country_score)<-str_replace(colnames(country_score), "account.t.d.7", "Account income, poorest 40%")
colnames(country_score)<-str_replace(colnames(country_score), "LGBT_acc", "LGBT acceptance index")
colnames(country_score)<-str_replace(colnames(country_score), "wbl", "Women, Business & Law index")
colnames(country_score)<-str_replace(colnames(country_score), "trust_ppl", "Most ppl. can be trusted %")
colnames(country_score)<-str_replace(colnames(country_score), "ref_idp", "*Refugees & IDPs index")
colnames(country_score)<-str_replace(colnames(country_score), "sec_aparat", "*Security apparatus index")

#Sustainability
#colnames(country_score)<-str_replace(colnames(country_score), "DT.TDS.DECT.GN.ZS", "Total debt service")
colnames(country_score)<-str_replace(colnames(country_score), "NY.ADJ.SVNG.GN.ZS", "Adjusted net savings %")
colnames(country_score)<-str_replace(colnames(country_score), "EN.ATM.PM25.MC.M3", "*PM2.5 mean annual exposure mg/m3")
#colnames(country_score)<-str_replace(colnames(country_score), "forest_loss", "Forest loss")
colnames(country_score)<-str_replace(colnames(country_score), "EG.FEC.RNEW.ZS", "Renewal energy consumption %")
colnames(country_score)<-str_replace(colnames(country_score), "ER.H2O.INTR.PC", "Renewal internal freshwater(pc)")
colnames(country_score)<-str_replace(colnames(country_score), "wat_qua", "Water Quality SDG 6.3")
colnames(country_score)<-str_replace(colnames(country_score), "WWT.new", "Wastewater treated %")
colnames(country_score)<-str_replace(colnames(country_score), "waste_managed", "Waste properly managed %")
colnames(country_score)<-str_replace(colnames(country_score), "waste_rate", "*Municipal soild waste (kg/pc/day)")
colnames(country_score)<-str_replace(colnames(country_score), "BHV.new", "Biodiversity & Habitat index")
colnames(country_score)<-str_replace(colnames(country_score), "FSH.new", "Fisheries index")
colnames(country_score)<-str_replace(colnames(country_score), "GIB.new", "*GHG intensity growth rate")
colnames(country_score)<-str_replace(colnames(country_score), "EN.ATM.CO2E.PC", "*CO2 emissions (mtr/ton pc)")
colnames(country_score)<-str_replace(colnames(country_score), "water_efficiency_FAO", "Water use efficiency (USD/m3)")
colnames(country_score)<-str_replace(colnames(country_score), "water_efficiency_ceo", "Water use efficiency (GNI/m3)")

#Inclusion
colnames(country_score)<-str_replace(colnames(country_score), "agri_land", "Agri. land productivity $/ha")
colnames(country_score)<-str_replace(colnames(country_score), "agri_value", "Agri. value added per worker $")
colnames(country_score)<-str_replace(colnames(country_score), "gini_ghg", "Total GNI/GHG emission")
colnames(country_score)<-str_replace(colnames(country_score), "gov_effect", "Governance effectivness")
colnames(country_score)<-str_replace(colnames(country_score), "cont_corr", "Control of corruption")
colnames(country_score)<-str_replace(colnames(country_score), "reg_qua", "Regulatory quality")
colnames(country_score)<-str_replace(colnames(country_score), "lpi_score", "Logistic performance index")
colnames(country_score)<-str_replace(colnames(country_score), "sdg9_intuse", "Pop. using internet %")
colnames(country_score)<-str_replace(colnames(country_score), "lpi_score", "Logistic performance index")
colnames(country_score)<-str_replace(colnames(country_score), "Tenure.insecurity", "*Tenure insecurity %")


country_score <- country_score[country_score$iso3 == i, ]
country_score <- as.data.frame(t(as.matrix(country_score)))
country_score <- country_score %>% rownames_to_column("indicator")
colnames(country_score)<-c("indicator", "score")
country_score$category <- ifelse(country_score$indicator %in% efficiency, '2.Efficiency',
                                   ifelse(country_score$indicator %in% sustainability, '3.Sustainability',
                                          ifelse(country_score$indicator %in% resilience, '4.Resilience', 
                                                 ifelse(country_score$indicator %in% inclusion, '1.Inclusion', 'Other'))))


country_score <- country_score%>% filter(category!='Other') 

#Join percentage and raw value
country_score <-left_join(country_score, country_values, by="indicator")
country_score$raw_value<-as.numeric(as.character(country_score$raw_value))
country_score$raw_value<-format(round(country_score$raw_value, 2), nsmall = 2)

# Format score data for graphs

country_score$score <- as.numeric(as.character(country_score$score))
country_score$score<-country_score$score*100
country_score <- country_score[order(country_score$category),]

#Create the second database for graph pillars (regional/income)

#Get inversed values for score graph - For the individual pillars graphs we need to get the value of the indicator and the inverse value, to create the circular graph as an stacked plot #in the score_graph_data, score will be the inverse value and 
country_score$score <- with(country_score, (100-score))
country_score$values <- with(country_score, (100-score))

country_score$score <- as.integer(country_score$score)
country_score$values <- as.integer(country_score$values)

write.csv(country_score, paste0(dir_out, group,'/',i,"_score_graphs.csv"), row.names = FALSE)

}
```

# Loop to GET MEDIAN/MEAN and SD values per country for PPT TABLE for the income and aspirational income group
```{r}
for(i in country){

#Get country income group
income_country<-country_all%>% filter(iso3==i)%>% summarise((income_red))
income_country<-income_country[1,1]

#Get country aspiratinal group
income_aspi<-country_all%>% filter(iso3==i)%>% summarise((income_aspiration))
income_aspi<-income_aspi[1,1]


#Use raw data to compare
country_val<- read.csv(file=paste0(dir_out, group,'/',i,"_percentil.csv"), header=TRUE, sep=",")%>%
  select(-percentil)


#country_aspi
income_info_country<-income_info%>%
  filter(income_red == income_country | income_red == income_aspi)

income_info_country<-left_join(income_info_country, country_val, by="indicator")
income_info_country<-income_info_country%>%
  filter(!is.na(category))%>%
  arrange(income_red, category)

income_info_country$raw_value<-as.numeric(as.character(income_info_country$raw_value))

income_info_country<-income_info_country %>% 
 mutate_if(is.numeric, round, digits=1)

#Create categorical category to use the conditional formating in excel:
# 3 indicator above one standard deviation from the mean 
# 2 indicator within one standard deviation from the mean
# 1 indicator below one standad 
# This function also revert the values for indicators in which a higher number means worse performing)
#For MEAN
income_info_country<-income_info_country%>%
 mutate(mean_flag = ifelse(str_detect(indicator, "\\*") & raw_value > sd_mean_up , "1",
                            ifelse(raw_value > sd_mean_up, "3",
                            ifelse(raw_value <= sd_mean_up & raw_value >= sd_mean_down, "2",
                            ifelse(str_detect(indicator, "\\*") & raw_value < sd_mean_down, "3",
                            ifelse(raw_value < sd_mean_down, "1", "Error"))))))
#For MEDIAN 
income_info_country<-income_info_country%>%
 mutate(median_flag = ifelse(str_detect(indicator, "\\*") & raw_value > sd_median_up , "1",
                            ifelse(raw_value > sd_median_up, "3",
                            ifelse(raw_value <= sd_median_up & raw_value >= sd_median_down, "2",
                            ifelse(str_detect(indicator, "\\*") & raw_value < sd_median_down, "3",
                            ifelse(raw_value < sd_median_down, "1", "Error"))))))

#Arrange to easily modify in excel 
income_info_country<-income_info_country%>%
  dplyr::select("category", "income_red", "indicator", "raw_value", "median_flag",  "median", "mean_flag", "mean", "sd", "sd_mean_up", "sd_mean_down", "sd_median_up", "sd_median_down")

write.csv(income_info_country,paste0(dir_out, group,'/',i,"_tables_data.csv"), row.names = FALSE)
}
```

# Loop to prepare data for PERCENTIL RANKING GRAPH - CIRCULAR (ALL PILARS- Global data)
```{r}

for(i in country){
# Load dataset from data generated in the previous section
  country_percent <- read.csv(file=paste0(dir_out, group,'/',i,"_percentil.csv"), header=TRUE, sep=",")

if (version == 0){
  
country_percent<-country_percent%>% filter(indicator %nin%  c("*Security apparatus index", "Waste properly managed %", "Biodiversity & Habitat index", "Fisheries index", "*GHG intensity growth rate", "*CO2 emissions (mtr/ton pc)", "Water use efficiency (USD/m3)"))

} else {
country_percent<-country_percent%>% filter(indicator %nin%  c("Adjusted net savings %", "Water use efficiency (GNI/m3)"))
}

data3<-country_percent

#Arrange data and filter NA
data3 <- data3 %>% 
  filter(!is.na(percentil))%>% 
  arrange(category, percentil)
data3$id <- seq(1, nrow(data3))

#Create labels for each column and angles (no need to adjust. With this method labels are aligned automatically)
label_data3 <- data3
number_of_bar3 <- nrow(label_data3)
angle3 <- 90 - 360 * (label_data3$id-0.5) /number_of_bar3     # I substract 0.5 because the letter must have the angle of the center of the bars. Not extreme right(1) or extreme left (0)
label_data3$hjust <- ifelse(angle3 < -90, 1, 0)
label_data3$angle <- ifelse(angle3 < -90, angle3+180, angle3)

# prepare a data frame for pilars names
base_data3 <- data3 %>% 
  group_by(category) %>% 
  dplyr::summarize(start=min(id), end=max(id)) %>% 
  rowwise() %>% 
  mutate(title=mean(c(start, end)))

#Remove numbers to the  pilar category name 
base_data3$category2<-str_replace(base_data3$category, "1.|2.|3.|4.", "")

#Paste indicators labels with  percentil rank values (ej, 35.- Labor market)
label_data3$test <- paste(data3$percentil, "-", data3$indicator)

com <- ggplot(data3) +      
  
  # Add the stacked bar
  geom_bar(aes(x=as.factor(id), y=percentil, fill=category, colour=category), stat="identity", alpha=0.7, size=0.2) +
  #colors used by the CEO in their first draft of the benchmarking
  #scale_fill_manual(values=c("hotpink1","gold1","steelblue2", "green3")) +
  scale_fill_manual(values=c("red2" ,"darkmagenta", "darkorange","darkcyan"))+
  scale_colour_manual(values=c("black","black", "black","black")) +
  
    geom_label(x = 0, y = -50, label = i, hjust=0.5, fontface="bold", size=7) +
  
  ylim(-50,120) +
  theme_minimal() +
  theme(
    legend.position = "none",
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = margin(-3,-3,-3,-3, "cm") 
  ) +
  coord_polar() +
  
   # Add labels on top of each bar
  geom_text(data=label_data3, aes(x=id, y=percentil+2, label= str_wrap(test, width = 20), hjust=label_data3$hjust), color="black", fontface="bold",alpha=1, size=3.5, angle= label_data3$angle, inherit.aes = FALSE ) +

  # Add base line information
geom_segment(data=base_data3, aes(x = start, y = -5, xend = end, yend = -5), colour = "black", alpha=0.8, size=0.6 , inherit.aes = FALSE )  +
  geom_text(data=base_data3, aes(x = title, y = -18, label=category2), hjust=c(0.5,0.5,0.5,0.5), angle=c(-60, 15, -65, 40), colour = "black", alpha=0.8, size=4, fontface="bold", inherit.aes = FALSE)

if (version == 0){
ggsave(com, file=paste0(dir_out, group,'/',i,"_percentil_global_v0.png"), width=12, height=13)
} else {
 ggsave(com, file=paste0(dir_out, group,'/',i,"_percentil_global_v1.png"), width=12, height=13) 
  }
} 
```
# Graphs per pilars (RISE) - SUSTAINABILITY
```{r}
    ##########
  # Sustainability#    #Different set of indicators for V0 AND V1
    ##########

for(i in country){
# Load dataset with country scores generated in the previous section
  country_score <- read.csv(file=paste0(dir_out, group,'/',i,"_score_graphs.csv"), header=TRUE, sep=",")

if (version == 0){
  
country_score<-country_score%>% filter(indicator %nin%  c("*Security apparatus index", "Waste properly managed %", "Biodiversity & Habitat index", "Fisheries index", "*GHG intensity growth rate", "*CO2 emissions (mtr/ton pc)", "Water use efficiency (USD/m3)"))

} else {
country_score<-country_score%>% filter(indicator %nin%  c("Adjusted net savings %", "Water use efficiency (GNI/m3)"))
  
}

#Split data for graphs 
country_score_graph1 <- country_score %>% filter(category== '3.Sustainability')

data2<-country_score_graph1
data2$order <- seq(1, nrow(data2))

# Move order column to the front so it does not get rejected when transforming to long format (column necessary to keep order of dimensions for the graph)
data2 <- data2 %>% 
  filter(!is.na(score))%>%
  select(order, everything())

# Transform data in a tidy format (long format)
data2 <- stats::reshape(data2, 
                direction = "long",
                varying = c("score", "values"),
                v.names = "value",
                idvar = c("order", "indicator", "category", "raw_value"),
                timevar = "observation",
                times = 1:2)

# Set a number of 'empty bar' to add at the end of each group
empty_bar <- 2
nObsType <- nlevels(as.factor(data2$observation))
to_add <- data.frame( matrix(NA, empty_bar*nlevels(as.factor(data2$category))*nObsType*.5, ncol(data2)))
colnames(to_add) <- colnames(data2)
to_add$category <- rep(levels(as.factor(data2$category)), each=empty_bar*nObsType*.5 )
data2 <- rbind(data2, to_add)

grpid = function(x) match(x, unique(x))
data2 <- data2 %>% mutate(group_id = group_indices(., category) %>% grpid)

#To group inverse and no inverse value
data2<- data2 %>% mutate(group_order=case_when(
  group_id == 1 ~ "A",
  TRUE ~ NA_character_ # all else are NA
))

data2 <- data2[order(data2$indicator),]

data2$id <- rep( seq(1, nrow(data2)/nObsType) , each=nObsType)

#Create labels for each column and angles (no need to adjust. With this method labels are aligned automatically)
label_data2 <- data2 %>% dplyr::group_by(id, indicator, raw_value) %>% dplyr::summarize(tot=sum(value))
number_of_bar2 <- nrow(label_data2)
angle2 <- 90 - 360 * (label_data2$id-0.5) /number_of_bar2     # I substract 0.5 because the letter must have the angle of the center of the bars. Not extreme right(1) or extreme left (0)
label_data2$hjust <- ifelse(angle2 < -90, 1, 0)
label_data2$angle <- ifelse(angle2 < -90, angle2+180, angle2)

# prepare a data frame for base lines
base_data2 <- data2 %>% 
  group_by(group_order) %>% 
  dplyr::summarize(start=min(id), end=max(id) 
            - empty_bar
          ) %>% 
  rowwise() %>% 
  mutate(title=mean(c(start, end)))

# prepare a data frame for grid (scales)
grid_data2 <- base_data2
grid_data2$end <- grid_data2$end[ c( nrow(grid_data2), 1:nrow(grid_data2)-1)] + 1.4
grid_data2$start <- grid_data2$start - .4
#grid_data2 <- grid_data2[-1,]

#Paste categories and raw values
data2$cat <- paste(data2$observation,data2$group_order)
label_data2$ind_value<-paste(label_data2$raw_value, "-", label_data2$indicator)

s <- ggplot(data2) +      
  
  # Add the stacked bar
  geom_bar(aes(x=as.factor(id), y=value, fill=cat, colour=cat), stat="identity", alpha=0.5, size=0.2) +
  #scale_fill_manual(values=c("white","steelblue1")) +
  scale_fill_manual(values=c("white","darkorange")) +
  scale_colour_manual(values=c("black","black")) +

  # Add a val=100/75/50/25 lines. I do it at the beginning to make sur barplots are OVER it.
  #geom_segment(data=grid_data2, aes(x = end, y = 100, xend = start, yend = 100), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data2, aes(x = end, y = 80, xend = start, yend = 80), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data2, aes(x = end, y = 60, xend = start, yend = 60), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data2, aes(x = end, y = 40, xend = start, yend = 40), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data2, aes(x = end, y = 20, xend = start, yend = 20), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  
    geom_label(x = 0, y = 0, label = i, hjust=0.5, fontface="bold", size=10) +
    annotate("text", x = rep(max(data2$id),5), y = c(20, 40, 60, 80, 100), label = c("20", "40", "60", "80", "100") , color="grey", size=5 , angle=0, fontface="bold", hjust=.5) +
  
  ylim(0 , 120) +
  theme_minimal() +
  theme(
    legend.position = "none",
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = margin(-3,-3,-3,-3, "cm") 
  ) +
  coord_polar() +
  
   # Add labels on top of each bar
  
  geom_text(data=label_data2, aes(x=id, y=tot-50, label= str_wrap(ind_value, width = 22), hjust=label_data2$hjust), color="black", fontface="bold",alpha=1, size=4.5, angle= label_data2$angle, inherit.aes = FALSE ) 


if (version == 0){
ggsave(s, file=paste0(dir_out, group,'/',i,"_score_graph_sust_v0.png"), width=10, height=10)
} else {
 ggsave(s, file=paste0(dir_out, group,'/',i,"_score_graph_sust_v1.png"), width=10, height=10) 
  }

} 
```

#Graphs per pilars (RISE) -INCLUSION
```{r}
      ##########
     # Inclusion #    #Different set of indicators for V0 AND V1
      ##########

#detach(package:plyr)
for(i in country){
# Load dataset with country scores generated in the previous section
  country_score <- read.csv(file=paste0(dir_out, group,'/',i,"_score_graphs.csv"), header=TRUE, sep=",")

if (version == 0){
  
country_score<-country_score%>% filter(indicator %nin%  c("*Security apparatus index", "Waste properly managed %", "Biodiversity & Habitat index", "Fisheries index", "*GHG intensity growth rate", "*CO2 emissions (mtr/ton pc)", "Water use efficiency (USD/m3)"))

} else {
country_score<-country_score%>% filter(indicator %nin%  c("Adjusted net savings %", "Water use efficiency (GNI/m3)"))
  
}
##### Inclusion #######

#Split data for graphs 
country_score_graph2 <- country_score %>% filter(category== '1.Inclusion')

data2<-country_score_graph2
data2$order <- seq(1, nrow(data2))

# Move order column to the front so it does not get rejected when transforming to long format (column necessary to keep order of dimensions for the graph)
data2 <- data2 %>% 
  filter(!is.na(score))%>%
  select(order, everything())

# Transform data in a tidy format (long format)
data2 <- stats::reshape(data2, 
                direction = "long",
                varying = c("score", "values"),
                v.names = "value",
                idvar = c("order", "indicator", "category", "raw_value"),
                timevar = "observation",
                times = 1:2)

# Set a number of 'empty bar' to add at the end of each group
empty_bar <- 2
nObsType <- nlevels(as.factor(data2$observation))
to_add <- data.frame( matrix(NA, empty_bar*nlevels(as.factor(data2$category))*nObsType*.5, ncol(data2)))
colnames(to_add) <- colnames(data2)
to_add$category <- rep(levels(as.factor(data2$category)), each=empty_bar*nObsType*.5 )
data2 <- rbind(data2, to_add)

grpid = function(x) match(x, unique(x))
data2 <- data2 %>% mutate(group_id = group_indices(., category) %>% grpid)

#To group inverse and no inverse value
data2<- data2 %>% mutate(group_order=case_when(
  group_id == 1 ~ "A",
  TRUE ~ NA_character_ # all else are NA
))

data2 <- data2[order(data2$indicator),]

data2$id <- rep( seq(1, nrow(data2)/nObsType) , each=nObsType)

#Create labels for each column and angles (no need to adjust. With this method labels are aligned automatically)
label_data2 <- data2 %>% dplyr::group_by(id, indicator, raw_value) %>% dplyr::summarize(tot=sum(value))
number_of_bar2 <- nrow(label_data2)
angle2 <- 90 - 360 * (label_data2$id-0.5) /number_of_bar2     # I substract 0.5 because the letter must have the angle of the center of the bars. Not extreme right(1) or extreme left (0)
label_data2$hjust <- ifelse(angle2 < -90, 1, 0)
label_data2$angle <- ifelse(angle2 < -90, angle2+180, angle2)

# prepare a data frame for base lines
base_data2 <- data2 %>% 
  group_by(group_order) %>% 
  dplyr::summarize(start=min(id), end=max(id) 
            - empty_bar
          ) %>% 
  rowwise() %>% 
  mutate(title=mean(c(start, end)))

# prepare a data frame for grid (scales)
grid_data2 <- base_data2
grid_data2$end <- grid_data2$end[ c( nrow(grid_data2), 1:nrow(grid_data2)-1)] + 1.4
grid_data2$start <- grid_data2$start - .4
#grid_data2 <- grid_data2[-1,]

#Paste categories and raw values
data2$cat <- paste(data2$observation,data2$group_order)
label_data2$ind_value<-paste(label_data2$raw_value, "-", label_data2$indicator)

inc <- ggplot(data2) +      
  
  # Add the stacked bar
  geom_bar(aes(x=as.factor(id), y=value, fill=cat, colour=cat), stat="identity", alpha=0.5, size=0.2) +
  #scale_fill_manual(values=c("white","hotpink1")) +
  scale_fill_manual(values=c("white","red2")) +
  scale_colour_manual(values=c("black","black")) +

  # Add a val=100/75/50/25 lines. I do it at the beginning to make sur barplots are OVER it.
  #geom_segment(data=grid_data2, aes(x = end, y = 100, xend = start, yend = 100), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data2, aes(x = end, y = 80, xend = start, yend = 80), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data2, aes(x = end, y = 60, xend = start, yend = 60), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data2, aes(x = end, y = 40, xend = start, yend = 40), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data2, aes(x = end, y = 20, xend = start, yend = 20), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  
    geom_label(x = 0, y = 0, label = i, hjust=0.5, fontface="bold", size=10) +
    annotate("text", x = rep(max(data2$id),5), y = c(20, 40, 60, 80, 100), label = c("20", "40", "60", "80", "100") , color="grey", size=5 , angle=0, fontface="bold", hjust=.5) +
  
  ylim(0 , 120) +
  theme_minimal() +
  theme(
    legend.position = "none",
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = margin(-3,-3,-3,-3, "cm") 
  ) +
  coord_polar() +
  
   # Add labels on top of each bar
  
  geom_text(data=label_data2, aes(x=id, y=tot-50, label= str_wrap(ind_value, width = 22), hjust=label_data2$hjust), color="black", fontface="bold",alpha=1, size=4.5, angle= label_data2$angle, inherit.aes = FALSE ) 


if (version == 0){
ggsave(inc, file=paste0(dir_out, group,'/',i,"_score_graph_incl_v0.png"), width=10, height=10)
} else {
 ggsave(inc, file=paste0(dir_out, group,'/',i,"_score_graph_incl_v1.png"), width=10, height=10) 
  }
}
```

# Graphs per pilars (RISE) - Efficiency
```{r}
    ##########
# 2. Efficiency  # Same set of indicators for V0 and V1 (still using version control in case it indicators change)
    ##########
#detach(package:plyr)
for(i in country){
# Load dataset with country scores generated in the previous section
  
  country_score <- read.csv(file=paste0(dir_out, group,'/',i,"_score_graphs.csv"), header=TRUE, sep=",")

if (version == 0){
  
country_score<-country_score%>% filter(indicator %nin%  c("*Security apparatus index", "Waste properly managed %", "Biodiversity & Habitat index", "Fisheries index", "*GHG intensity growth rate", "*CO2 emissions (mtr/ton pc)", "Water use efficiency (USD/m3)"))

} else {
country_score<-country_score%>% filter(indicator %nin%  c("Adjusted net savings %", "Water use efficiency (GNI/m3)"))
  
}
##### Inclusion #######

#Split data for graphs 
country_score_graph2 <- country_score %>% filter(category== '2.Efficiency')

data2<-country_score_graph2
data2$order <- seq(1, nrow(data2))

# Move order column to the front so it does not get rejected when transforming to long format (column necessary to keep order of dimensions for the graph)
data2 <- data2 %>% 
  filter(!is.na(score))%>%
  select(order, everything())

# Transform data in a tidy format (long format)
data2 <- stats::reshape(data2, 
                direction = "long",
                varying = c("score", "values"),
                v.names = "value",
                idvar = c("order", "indicator", "category", "raw_value"),
                timevar = "observation",
                times = 1:2)

# Set a number of 'empty bar' to add at the end of each group
empty_bar <- 2
nObsType <- nlevels(as.factor(data2$observation))
to_add <- data.frame( matrix(NA, empty_bar*nlevels(as.factor(data2$category))*nObsType*.5, ncol(data2)))
colnames(to_add) <- colnames(data2)
to_add$category <- rep(levels(as.factor(data2$category)), each=empty_bar*nObsType*.5 )
data2 <- rbind(data2, to_add)

grpid = function(x) match(x, unique(x))
data2 <- data2 %>% mutate(group_id = group_indices(., category) %>% grpid)

#To group inverse and no inverse value
data2<- data2 %>% mutate(group_order=case_when(
  group_id == 1 ~ "A",
  TRUE ~ NA_character_ # all else are NA
))

data2 <- data2[order(data2$indicator),]

data2$id <- rep( seq(1, nrow(data2)/nObsType) , each=nObsType)

#Create labels for each column and angles (no need to adjust. With this method labels are aligned automatically)
label_data2 <- data2 %>% dplyr::group_by(id, indicator, raw_value) %>% dplyr::summarize(tot=sum(value))
number_of_bar2 <- nrow(label_data2)
angle2 <- 90 - 360 * (label_data2$id-0.5) /number_of_bar2     # I substract 0.5 because the letter must have the angle of the center of the bars. Not extreme right(1) or extreme left (0)
label_data2$hjust <- ifelse(angle2 < -90, 1, 0)
label_data2$angle <- ifelse(angle2 < -90, angle2+180, angle2)

# prepare a data frame for base lines
base_data2 <- data2 %>% 
  group_by(group_order) %>% 
  dplyr::summarize(start=min(id), end=max(id) 
            - empty_bar
          ) %>% 
  rowwise() %>% 
  mutate(title=mean(c(start, end)))

# prepare a data frame for grid (scales)
grid_data2 <- base_data2
grid_data2$end <- grid_data2$end[ c( nrow(grid_data2), 1:nrow(grid_data2)-1)] + 1.4
grid_data2$start <- grid_data2$start - .4
#grid_data2 <- grid_data2[-1,]

#Paste categories and raw values
data2$cat <- paste(data2$observation,data2$group_order)
label_data2$ind_value<-paste(label_data2$raw_value, "-", label_data2$indicator)

e <- ggplot(data2) +      
  
  # Add the stacked bar
  geom_bar(aes(x=as.factor(id), y=value, fill=cat, colour=cat), stat="identity", alpha=0.5, size=0.2) +
  #scale_fill_manual(values=c("white","gold1")) +
  scale_fill_manual(values=c("white","darkmagenta")) +
  scale_colour_manual(values=c("black","black")) +

  # Add a val=100/75/50/25 lines. I do it at the beginning to make sur barplots are OVER it.
  #geom_segment(data=grid_data2, aes(x = end, y = 100, xend = start, yend = 100), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data2, aes(x = end, y = 80, xend = start, yend = 80), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data2, aes(x = end, y = 60, xend = start, yend = 60), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data2, aes(x = end, y = 40, xend = start, yend = 40), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data2, aes(x = end, y = 20, xend = start, yend = 20), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  
    geom_label(x = 0, y = 0, label = i, hjust=0.5, fontface="bold", size=10) +
    annotate("text", x = rep(max(data2$id),5), y = c(20, 40, 60, 80, 100), label = c("20", "40", "60", "80", "100") , color="grey", size=5 , angle=0, fontface="bold", hjust=.5) +
  
  ylim(0 , 120) +
  theme_minimal() +
  theme(
    legend.position = "none",
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = margin(-3,-3,-3,-3, "cm") 
  ) +
  coord_polar() +
  
   # Add labels on top of each bar
  
  geom_text(data=label_data2, aes(x=id, y=tot-50, label= str_wrap(ind_value, width = 22), hjust=label_data2$hjust), color="black", fontface="bold",alpha=1, size=4.5, angle= label_data2$angle, inherit.aes = FALSE ) 


if (version == 0){
ggsave(e, file=paste0(dir_out, group,'/',i,"_score_graph_eff_v0.png"), width=10, height=10)
} else {
 ggsave(e, file=paste0(dir_out, group,'/',i,"_score_graph_eff_v1.png"), width=10, height=10) 
  }
}
```
# Graphs per pilars (RISE) - Resilience
```{r}
    ##########
#   RESILIENCE #    # Same set of indicators for V0 and V1 (still using version control in case it indicators change)
    ##########
#detach(package:plyr)
for(i in country){
# Load dataset with country scores generated in the previous section
  country_score <- read.csv(file=paste0(dir_out, group,'/',i,"_score_graphs.csv"), header=TRUE, sep=",")

if (version == 0){
  
country_score<-country_score%>% filter(indicator %nin%  c("*Security apparatus index", "Waste properly managed %", "Biodiversity & Habitat index", "Fisheries index", "*GHG intensity growth rate", "*CO2 emissions (mtr/ton pc)", "Water use efficiency (USD/m3)"))

} else {
country_score<-country_score%>% filter(indicator %nin%  c("Adjusted net savings %", "Water use efficiency (GNI/m3)"))
  
}
##### Inclusion #######

#Split data for graphs 
country_score_graph2 <- country_score %>% filter(category== '4.Resilience')

data2<-country_score_graph2
data2$order <- seq(1, nrow(data2))

# Move order column to the front so it does not get rejected when transforming to long format (column necessary to keep order of dimensions for the graph)
data2 <- data2 %>% 
  filter(!is.na(score))%>%
  select(order, everything())

# Transform data in a tidy format (long format)
data2 <- stats::reshape(data2, 
                direction = "long",
                varying = c("score", "values"),
                v.names = "value",
                idvar = c("order", "indicator", "category", "raw_value"),
                timevar = "observation",
                times = 1:2)

# Set a number of 'empty bar' to add at the end of each group
empty_bar <- 2
nObsType <- nlevels(as.factor(data2$observation))
to_add <- data.frame( matrix(NA, empty_bar*nlevels(as.factor(data2$category))*nObsType*.5, ncol(data2)))
colnames(to_add) <- colnames(data2)
to_add$category <- rep(levels(as.factor(data2$category)), each=empty_bar*nObsType*.5 )
data2 <- rbind(data2, to_add)

grpid = function(x) match(x, unique(x))
data2 <- data2 %>% mutate(group_id = group_indices(., category) %>% grpid)

#To group inverse and no inverse value
data2<- data2 %>% mutate(group_order=case_when(
  group_id == 1 ~ "A",
  TRUE ~ NA_character_ # all else are NA
))

data2 <- data2[order(data2$indicator),]

data2$id <- rep( seq(1, nrow(data2)/nObsType) , each=nObsType)

#Create labels for each column and angles (no need to adjust. With this method labels are aligned automatically)
label_data2 <- data2 %>% dplyr::group_by(id, indicator, raw_value) %>% dplyr::summarize(tot=sum(value))
number_of_bar2 <- nrow(label_data2)
angle2 <- 90 - 360 * (label_data2$id-0.5) /number_of_bar2     # I substract 0.5 because the letter must have the angle of the center of the bars. Not extreme right(1) or extreme left (0)
label_data2$hjust <- ifelse(angle2 < -90, 1, 0)
label_data2$angle <- ifelse(angle2 < -90, angle2+180, angle2)

# prepare a data frame for base lines
base_data2 <- data2 %>% 
  group_by(group_order) %>% 
  dplyr::summarize(start=min(id), end=max(id) 
            - empty_bar
          ) %>% 
  rowwise() %>% 
  mutate(title=mean(c(start, end)))

# prepare a data frame for grid (scales)
grid_data2 <- base_data2
grid_data2$end <- grid_data2$end[ c( nrow(grid_data2), 1:nrow(grid_data2)-1)] + 1.4
grid_data2$start <- grid_data2$start - .4
#grid_data2 <- grid_data2[-1,]

#Paste categories and raw values
data2$cat <- paste(data2$observation,data2$group_order)
label_data2$ind_value<-paste(label_data2$raw_value, "-", label_data2$indicator)

r <- ggplot(data2) +      
  
  # Add the stacked bar
  geom_bar(aes(x=as.factor(id), y=value, fill=cat, colour=cat), stat="identity", alpha=0.5, size=0.2) +
  #scale_fill_manual(values=c("white","green3")) +
  scale_fill_manual(values=c("white","darkcyan")) +
  scale_colour_manual(values=c("black","black")) +

  # Add a val=100/75/50/25 lines. I do it at the beginning to make sur barplots are OVER it.
  #geom_segment(data=grid_data2, aes(x = end, y = 100, xend = start, yend = 100), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data2, aes(x = end, y = 80, xend = start, yend = 80), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data2, aes(x = end, y = 60, xend = start, yend = 60), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data2, aes(x = end, y = 40, xend = start, yend = 40), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data2, aes(x = end, y = 20, xend = start, yend = 20), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  
    geom_label(x = 0, y = 0, label = i, hjust=0.5, fontface="bold", size=10) +
    annotate("text", x = rep(max(data2$id),5), y = c(20, 40, 60, 80, 100), label = c("20", "40", "60", "80", "100") , color="grey", size=5 , angle=0, fontface="bold", hjust=.5) +
  
  ylim(0 , 120) +
  theme_minimal() +
  theme(
    legend.position = "none",
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = margin(-3,-3,-3,-3, "cm") 
  ) +
  coord_polar() +
  
   # Add labels on top of each bar
  
  geom_text(data=label_data2, aes(x=id, y=tot-50, label= str_wrap(ind_value, width = 22), hjust=label_data2$hjust), color="black", fontface="bold",alpha=1, size=4.5, angle= label_data2$angle, inherit.aes = FALSE ) 


if (version == 0){
ggsave(r, file=paste0(dir_out, group,'/',i,"_score_graph_res_v0.png"), width=10, height=10)
} else {
 ggsave(r, file=paste0(dir_out, group,'/',i,"_score_graph_res_v1.png"), width=10, height=10) 
  }
}
```
