---
title: "Benchmarking V3"
author: "Evelyn Sanchez"
date: "10/19/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = "/Users/eves/Dropbox/MENA/")
#knitr::opts_knit$set(root.dir = "C:/Users/####/OneDrive/")
```

#Required libraries
```{r}
library(WDI)
library(plyr)
library(dplyr)
library(readxl)
library(rvest)
library(tidyverse)
library(countrycode)
library(stringr)
```

#Set Directories
Create the following set of folders 
 dir_raw = store all the csv and excel files that cannot be download through web scraping
 dir_int = This folder is the outcome folder for the global results, name it as "Integrated data" to be consistent with the mapping script "Benchmarking_Graphs"
 
```{r}
dir_raw<-"./Data/Benchmarking/SD_Profiles/Raw indicators/" #"./My Files/1.RISE/"
dir_int<- "./Data/Benchmarking/SD_Profiles/Integrated data/" #"./My Files/Integrated data/"
getwd()
```

#Get WDI DATA
```{r}
### WDI INDICATORS ###

#List of WDI indicators used
ind<-c('EN.POP.SLUM.UR.ZS', 'SL.TLF.CACT.FE.ZS', 'SH.STA.SMSS.ZS', 'SH.H2O.SMDW.ZS', 'HD.HCI.OVRL', 'SI.POV.GINI', 'SE.SEC.ENRR', 'SH.IMM.IDPT', 'account.t.d.7', 'NY.ADJ.SVNG.GN.ZS', 'EN.ATM.PM25.MC.M3', 'EG.FEC.RNEW.ZS', 'ER.H2O.INTR.PC', 'EN.ATM.GHGT.KT.CE', 'NY.GNP.MKTP.CD', 'EN.ATM.CO2E.PC')

#Group indicator by year of data (number after ind-indicates the year used)
ind_12<-c('NY.GNP.MKTP.CD', 'EN.ATM.GHGT.KT.CE')
ind_14<-c('EN.POP.SLUM.UR.ZS', 'ER.H2O.INTR.PC')
ind_17<-c('SL.TLF.CACT.FE.ZS', 'SH.STA.SMSS.ZS', 'SH.H2O.SMDW.ZS', 'HD.HCI.OVRL','EN.ATM.PM25.MC.M3', 'NY.ADJ.SVNG.GN.ZS') 
ind_18<-c('SH.IMM.IDPT')
#Most receny year available between 2015 and 2019
ind_15_19<-c('SI.POV.GINI', 'SE.SEC.ENRR')


# Importation and cleaning of each WDI indicator
for(i in ind){
  print(i)
  if (i == 'account.t.d.7'){
  wdi <- WDI(country = "all", indicator = i, start =2000, end =2020, extra = TRUE, cache = NULL)
  wdi<-subset(wdi, !is.na(account.t.d.7))
  wdi <- wdi %>% group_by(iso2c) %>% filter(year==2017)
  wdi <- subset(wdi, select = -c(iso3c, region, income,year,region, capital,longitude,latitude,lending,country))
  colnames(wdi)[colnames(wdi)=="iso2c"] <- "iso3"
  assign(paste('wdi_',i,sep=''),wdi)
  }
  if (i %in% ind_15_19){
  wdi <- WDI(country = "all", indicator = i, start = 2015, end = 2019, extra = TRUE, cache = NULL)
  wdi <- na.omit(wdi)
  wdi <- wdi %>% group_by(iso2c) %>% filter(year==max(year))
  wdi <- subset(wdi, select = -c(iso2c,capital,longitude, income, region,  year, latitude,lending,country))
  colnames(wdi)[colnames(wdi)=="iso3c"] <- "iso3"
  assign(paste('wdi_',i,sep=''),wdi)
  }
  if (i %in% ind_12){
  wdi <- WDI(country = "all", indicator = i, start =2000, end =2020, extra = TRUE, cache = NULL)
  wdi <- wdi %>% group_by(iso2c) %>% filter(year==2012)
  wdi <- na.omit(wdi)
  wdi <- subset(wdi, select = -c(iso2c,capital,year, income, region, longitude,latitude,lending,country))
  colnames(wdi)[colnames(wdi)=="iso3c"] <- "iso3"
  assign(paste('wdi_',i,sep=''),wdi)
  }
  if (i %in% ind_14){
  wdi <- WDI(country = "all", indicator = i, start =2000, end =2020, extra = TRUE, cache = NULL)
  wdi <- na.omit(wdi)
  wdi <- wdi %>% group_by(iso2c) %>% filter(year==2014)
  wdi <- subset(wdi, select = -c(iso2c,capital,longitude,year,region, income,latitude,lending,country))
  colnames(wdi)[colnames(wdi)=="iso3c"] <- "iso3"
  assign(paste('wdi_',i,sep=''),wdi)
  }
  if (i == 'EG.FEC.RNEW.ZS'){
  wdi <- WDI(country = "all", indicator = i, start =2000, end =2020, extra = TRUE, cache = NULL)
  wdi <- wdi %>% group_by(iso2c) %>% filter(year==2015)
  wdi <- na.omit(wdi)
  wdi <- subset(wdi, select = -c(iso2c,capital,longitude,year, region, latitude,lending,country))
  colnames(wdi)[colnames(wdi)=="iso3c"] <- "iso3"
  assign(paste('wdi_',i,sep=''),wdi)
  }
  if (i == 'EN.ATM.CO2E.PC'){
  wdi <- WDI(country = "all", indicator = i, start =2000, end =2020, extra = TRUE, cache = NULL)
  wdi <- wdi %>% group_by(iso2c) %>% filter(year==2016)
  wdi <- na.omit(wdi)
  wdi <- subset(wdi, select = -c(iso2c,capital,longitude,year, region, latitude,lending,country))
  colnames(wdi)[colnames(wdi)=="iso3c"] <- "iso3"
  assign(paste('wdi_',i,sep=''),wdi)
  }
  if (i %in% ind_17){
  wdi <- WDI(country = "all", indicator = i, start =2000, end =2020, extra = TRUE, cache = NULL)
  wdi <- wdi %>% group_by(iso2c) %>% filter(year== 2017)
  wdi <- na.omit(wdi)
  wdi <- subset(wdi, select = -c(iso2c,capital,longitude,year, income, latitude,lending,country))
  colnames(wdi)[colnames(wdi)=="iso3c"] <- "iso3"
  assign(paste('wdi_',i,sep=''),wdi)
  }
  if (i %in% ind_18){
  wdi <- WDI(country = "all", indicator = i, start =2000, end =2020, extra = TRUE, cache = NULL)
  wdi <- wdi %>% group_by(iso2c) %>% filter(year==2018)
  wdi <- na.omit(wdi)
  wdi <- subset(wdi, select = -c(iso2c,capital,longitude,year, income,region, latitude,lending,country))
  colnames(wdi)[colnames(wdi)=="iso3c"] <- "iso3"
  assign(paste('wdi_',i,sep=''),wdi)
    }
}

#Poverty Average 2010- 2016
poverty <- WDI(country = "all", indicator = 'SI.POV.DDAY', start =2010, end =2016, extra = TRUE, cache = NULL)
poverty<- poverty%>%
  group_by(iso3c)%>%
  dplyr::summarize(mean(SI.POV.DDAY, na.rm = TRUE))
  colnames(poverty)<-c("iso3", "pov_1016")    
  
#GNI Data (get all data from 2010 to most recent year to later create water efficiency measure)  
GNI_data <- WDI(country = "all", indicator = 'NY.GNP.MKTP.CD', start =2010, end =2020, extra = TRUE, cache = NULL)
GNI_data <- na.omit(GNI_data)
GNI_data <- subset(GNI_data, select = -c(iso2c,capital,longitude,income,region, latitude,lending,country))
colnames(GNI_data)[colnames(GNI_data)=="iso3c"] <- "iso3"
```


#Import indicators by web scraping 
```{r}
#####  WGI #####
#All indicators from Worldwide Governance Indicators
#website: https://info.worldbank.org/governance/wgi/

#Gov effciency
temp <- tempfile()
download.file("http://info.worldbank.org/governance/wgi/Home/downLoadFile?fileName=wgidataset.xlsx", temp, mode="wb")
effect <- read_excel((temp), sheet = "GovernmentEffectiveness", skip = 14)
effect<-  subset(effect, select= c("Code", "Estimate...117"))   #Estimate...117 for 2018  or Estimate...123 for 2019  
colnames(effect)<-c("iso3", "gov_effect")
effect$gov_effect<- as.numeric(as.character(effect$gov_effect))

#Control of corruption
corr <- read_excel((temp), sheet = "ControlofCorruption", skip = 14)
corr <-  subset(corr, select= c("Code", "Estimate...117"))        #Estimate...117 for 2018  or Estimate...123 for 2019   
colnames(corr)<-c("iso3", "cont_corr")
corr$cont_corr<- as.numeric(as.character(corr$cont_corr))

#RegulatoryQuality
regq <- read_excel((temp), sheet = "RegulatoryQuality", skip = 14)
regq <-  subset(regq, select= c("Code", "Estimate...117"))   #Estimate...117 for 2018  or  Estimate...123 for 2019    
colnames(regq)<-c("iso3", "reg_qua")
regq$reg_qua<- as.numeric(as.character(regq$reg_qua))

###### Population using internet  ######
# SDG INDICATORS data website https://dashboards.sdgindex.org/downloads
temp1 <- tempfile()
download.file("https://sdsna.github.io/SDR2020/SDR2020Database.xlsx", temp1, mode="wb")
internet <- read_excel((temp1), sheet = "Raw Trend Data")
internet<-internet%>%
  select(Country, id, Year,sdg9_intuse)%>%
  group_by(Country)%>%
  filter(Year==2017)    #2017 is the most recent year of the data
colnames(internet)[colnames(internet)=="id"] <- "iso3"
internet<-internet%>%ungroup()%>%select(iso3, sdg9_intuse)

#####  Water efficiency from FAO (data website: http://www.fao.org/sustainable-development-goals/indicators/641/en/) ######
temp2 <- tempfile()
download.file("https://sdlc.fao.org/artifactory/fao-sdg-releases/6.4.1/6_4_1_May_2020.xlsx", temp2, mode="wb")
water_efficiency <- read_excel((temp2))
water_efficiency$iso3<-countrycode(water_efficiency$GeoAreaName, origin = 'country.name', destination = 'iso3c')
water_efficiency<-water_efficiency%>%
  group_by(GeoAreaName)%>%
  filter(TimePeriod==2017)%>%
  ungroup()%>%
  select(iso3, Value)
water_efficiency$Value<-as.character(as.numeric(water_efficiency$Value))
colnames(water_efficiency)[colnames(water_efficiency)=="Value"] <- "water_efficiency_FAO"


##### EPI mesures ######
# data website: https://epi.yale.edu/downloads
# Variables: Biodiverity and Habitat,Wastewater that receives treatment, Fisheries index and Greenhouse gas intensity growth rate) 
temp3 <- tempfile()
download.file("https://epi.yale.edu/downloads/epi2020results20200604.csv", temp3, mode="wb")
epi_indices<-read.csv(temp3)
# 0 in these indicators means no data, so replace 0 with NA
epi_indices<-epi_indices%>%
  select(iso, WWT.new,  BHV.new, FSH.new, GIB.new )%>% 
  mutate_if(is.numeric, ~replace(., . == 0, NA))
colnames(epi_indices)[colnames(epi_indices)=="iso"] <- "iso3"

###### Fragile State Index #######
#data website:  https://fragilestatesindex.org/excel/
temp4 <- tempfile()
download.file("https://fragilestatesindex.org/wp-content/uploads/2020/05/fsi-2020.xlsx", temp4, mode="wb")
frag_index <- read_excel((temp4))
frag_index$iso3<-countrycode(frag_index$Country, origin = 'country.name', destination = 'iso3c')
frag_index<-frag_index%>%select("iso3","C1: Security Apparatus", "S2: Refugees and IDPs")
colnames(frag_index)<-c("iso3", "sec_aparat", "ref_idp" )

###### Women, Business and  Law ###
# data website: https://wbl.worldbank.org/en/wbl-data
temp5 <- tempfile()
download.file("http://pubdocs.worldbank.org/en/625831591105047863/WBL-50YearPanelDetails-Web-01Jun2020.xlsx", temp5, mode="wb")
women <- read_excel(temp5, sheet = "WBL2020", skip= 1)
#Correct country code for West Bank and Gaza
women$Code[women$Economy=="West Bank and Gaza"] <- "PSE"
women<-  subset(women, select= c("Code", "WBL INDEX"))
colnames(women)<-c("iso3", "wbl")
```
#Import indicators in excel and csv datasets
```{r}
#Read csv
temp <- list.files(path= dir_raw, pattern = "*.csv")
  file_names <- make.names(gsub("*.csv", "", temp))
  list2env(
    lapply(setNames(paste0(dir_raw, temp), file_names),
           read.csv), envir = .GlobalEnv)
#Read excel
temp <- list.files(path= dir_raw, pattern = "*.xlsx|*.xls")
temp<-temp[str_detect(temp, "\\~", negate = T)] #To avoid hidden files 
file_names <- make.names(gsub("*.xlsx|*.xls", "", temp))
  list2env(
    lapply(setNames(paste0(dir_raw, temp), file_names),
           read_excel), envir = .GlobalEnv)
  
### Risk Unbreakable dataset #####
#Dataset coming from the WB report "Unbreakable: Building the Resilience of the Poor in the Face of Natural Disasters https://openknowledge.worldbank.org/handle/10986/25335"
# Dataset provided by Stephane Hallegatte GFDRR- WB
Unbreakable_global$iso3<-countrycode(Unbreakable_global$country, origin = 'country.name', destination = 'iso3c')
risk<-  subset(Unbreakable_global, select= c(iso3, risk, risk_to_assets))
risk$risk_wellbeing<-risk$risk*100
risk$risk_to_assets<-risk$risk_to_assets*100
risk$risk<-NULL
  
### Agricultural value per value added per worker
# FAO dataset http://www.fao.org/faostat/en/#data/OE, selected variable: Agriculture value added per worker 
FAOSTAT_data_10.23.2020$iso3<-countrycode(FAOSTAT_data_10.23.2020$Area, origin = 'country.name', destination = 'iso3c')
agri_value<-  subset(FAOSTAT_data_10.23.2020, select= c("iso3", "Value"))
colnames(agri_value)<-c("iso3", "agri_value")
  
### Land tenure insecurity from https://www.prindex.net/data/
Land_tenure$iso3<-countrycode(Land_tenure$Name, origin = 'country.name', destination = 'iso3c')
Land_tenure<-Land_tenure%>%select(iso3, Tenure.insecurity)

### Waste inadequately managed
#Data from the paper: https://www.iswa.org/fileadmin/user_upload/Calendar_2011_03_AMERICANA/Science-2015-Jambeck-768-71__2_.pdf
#Database provided by: Martin Heger, Environmental-MENA-WB
Jambeck_et_al_data$iso3<-countrycode(Jambeck_et_al_data$Country, origin = 'country.name', destination = 'iso3c')
Jambeck_et_al_data$iso3[Jambeck_et_al_data$Country=="Channel Islands"] <- "CHI"
Jambeck_et_al_data<-Jambeck_et_al_data%>%select("% Inadequately managed waste5", "iso3")
colnames(Jambeck_et_al_data)<-c("waste_missmanaged", "iso3")
Jambeck_et_al_data$waste_managed<-100-Jambeck_et_al_data$waste_missmanaged #Get inverse value
Jambeck_et_al_data$waste_missmanaged<-NULL

### Waste generation rate
#Data from the WB Report: What a Waste 2.0 : A Global Snapshot of Solid Waste Management to 2050  https://openknowledge.worldbank.org/handle/10986/30317
#Data available for dowload in the internal Worldbank database (What a waste dataset)
colnames(country_level_data_0)
muni_waste<-country_level_data_0%>%
  select("iso3c", "total_msw_total_msw_generated_tons_year", "population_population_number_of_people")
#Calculate waste rate per capita,per day in kg -original data in tons
muni_waste<-muni_waste%>%
  mutate(waste_rate = 1000*(total_msw_total_msw_generated_tons_year/population_population_number_of_people)/356)
muni_waste<-muni_waste%>%
  select("iso3c", "waste_rate")
colnames(muni_waste)[colnames(muni_waste)=="iso3c"] <- "iso3"

##### Logistic index 
#Data from from WB Logistic Performance Index https://lpi.worldbank.org/ , file name = Aggregated LPI 2012-2018(download from webpage since there is an error in the file when use web scraping)
lpi_aggregated_ranks$iso3<-countrycode(lpi_aggregated_ranks$Country, origin = 'country.name', destination = 'iso3c')
lpi_aggregated_ranks<-lpi_aggregated_ranks%>%select("LPI Score", "iso3")
colnames(lpi_aggregated_ranks)<-c("lpi_score", "iso3")

##### Confidence in gov from Gallup World Values survey
#Dataset provided by Jason Russ, Chief Economist Office - Sustainable Development 
Confidence_The_Government<-Confidence_The_Government[6:8,]
Confidence_The_Government <- as.data.frame(t(as.matrix(Confidence_The_Government)))
Confidence_The_Government<-Confidence_The_Government[-c(1:2),]
Confidence_The_Government$V2 <-as.numeric(as.character(Confidence_The_Government$V2))
Confidence_The_Government$V3 <-as.numeric(as.character(Confidence_The_Government$V3))
Confidence_The_Government<-Confidence_The_Government%>% mutate(conf_gov = V2 + V3)
Confidence_The_Government$iso3<-countrycode(Confidence_The_Government$V1, origin = 'country.name', destination = 'iso3c')
Confidence_The_Government<-Confidence_The_Government%>% select('iso3', 'conf_gov')

##### Trust people from Gallup World Values survey
#Dataset provided by Jason Russ, Chief Economist Office - Sustainable Development 
Most_people_can_be_trusted<-Most_people_can_be_trusted[6:7,]
Most_people_can_be_trusted <- as.data.frame(t(as.matrix(Most_people_can_be_trusted)))
Most_people_can_be_trusted<-Most_people_can_be_trusted[-c(1:2),]
Most_people_can_be_trusted$iso3<-countrycode(Most_people_can_be_trusted$V1, origin = 'country.name', destination = 'iso3c')
Most_people_can_be_trusted<-Most_people_can_be_trusted%>% select('iso3', 'V2')
colnames(Most_people_can_be_trusted)<-c('iso3', 'trust_ppl')
Most_people_can_be_trusted$trust_ppl<-as.numeric(as.character(Most_people_can_be_trusted$trust_ppl))

#### Agr land productivity $, 2016
#Dataset provided by Jason Russ, Chief Economist Office - Sustainable Development. Calculations by the Chief Economist Office use the Gross Production Value and Total Agricultural Land from FAO. 
FAO.land.productivity$iso3<-countrycode(FAO.land.productivity$Country, origin = 'country.name', destination = 'iso3c')
FAO.land.productivity$iso3[FAO.land.productivity$Country=="Channel Islands"] <- "CHI"
FAO.land.productivity<-FAO.land.productivity%>% select('iso3', '2016')
colnames(FAO.land.productivity)<-c('iso3', 'agri_land')

#Water efficiency (Replication of calculation proposed by the Chief Economist Office)
#Use Total water withdrawal indicator from http://www.fao.org/nr/water/aquastat/data/query/results.html (download datas as csv flat file - countries in y axis and values in x axis) - Take most recent year with data since 2010, and used GNI information of the same year. GNI data was already extracted from the WDI
aqua<-aquastat_water_withdraw
aqua<-aqua%>% group_by(Area)%>% filter(Year==max(Year))%>% filter(Year>2009)
aqua$iso3<-countrycode(aqua$Area, origin = 'country.name', destination = 'iso3c')
colnames(aqua)[colnames(aqua)=="Year"] <- "year"
#Merge with GNI data,previously downloaded from the WDI  
aqua<-left_join(aqua,GNI_data, by=c("year", "iso3"))
aqua<-aqua%>%mutate(water_efficiency_ceo= NY.GNP.MKTP.CD/(Value*1000000000))
aqua<-aqua%>%ungroup()%>%
  select("iso3", "water_efficiency_ceo") 

  ####  Indicators provided by the Chief Economist Office - Sustainable Development) ####

#SD GG Diagnostics excel file was provided by Jason Russ, Chief Economist Office - Sustainable Development,  which contains  processed/collected data by the Chief Economist Office the from the following sources:

#LGBT Acceptance - Manually collected from the following PDF, appendix 2 (page 31)  https://williamsinstitute.law.ucla.edu/wp-content/uploads/Global-Acceptance-Index-LGBT-Oct-2019.pdf

#Rainfall shock exposure %
#The source of rainfall shock exposure data is author calculations based on GPW population data and Willmott and Matsuura (2001) weather data, it is estimated based on the average share of the population exposed to a dry rainfall shock (rainfall <1 SD below average) over a 5 year period (2009-2013). 

##Pop affected by disasters %
#Collected data from EMDAT database of all instances of disasters marked as Geophysical, Meteorological, Hydrological, and Climatological. Then for each year, it was estimated the number of people killed or affected by it, and the total damages.

#Water quality
#Data from the WB report: Quality Unknown: The Invisible Water Crisis https://www.worldbank.org/en/news/feature/2019/08/20/quality-unknown. Data not yet available for public release

#Rainfall exposure
#Data from the WB report: Charting a New Path for Water's Future (https://www.worldbank.org/en/news/feature/2017/10/24/uncharted-waters). Data not yet available for public release 

#Forest loss%, 2001-2019
#Data from the Global Forest Watch site https://www.globalforestwatch.org/ #For this indicator, tree cover data in 2020 was collected, later annual tree cover loss from 2001 to 2019 was calculated and and divided it by the 2020 tree cover to get the forest loss %.

#Food security index, 2019
#Data from the https://foodsecurityindex.eiu.com/, cleaned and proceessed by the CEO

ceo_data<-read_excel(paste0(dir_raw, "SD GG Diagnostics - Database V7.xlsx"), sheet = "Master2")
ceo_data <-  subset(ceo_data, select= c("Country Name",  "LGBT acceptance index", "Water quality", "Food security index, 2019", "Forest loss%, 2001-2019", "*Pop affected %", "*Rainfall exp %"))
colnames(ceo_data)<-c("Country",  "LGBT_acc", "wat_qua", "food_sec", "forest_loss", "pop_dis", "rain_exp")
ceo_data$iso3<-countrycode(ceo_data$Country, origin = 'country.name', destination = 'iso3c')

#Multiply by 100 percentage variables
ceo_data$pop_dis<-ceo_data$pop_dis*100
ceo_data$rain_exp<-ceo_data$rain_exp*100
ceo_data$forest_loss<-ceo_data$forest_loss*100

#Correct Kosovo and Channel Islands
ceo_data$iso3[ceo_data$Country=="Kosovo"] <- "XKX"
ceo_data$iso3[ceo_data$Country=="Channel Islands"] <- "CHI"
ceo_data$Country<-NULL

```

#List of countries with their updated income classification and regional group
Some countries had changed income category and WDI hasn't update correctly, so better use the most current country classification (June 2020), available at https://datahelpdesk.worldbank.org/knowledgebase/articles/906519-world-bank-country-and-lending-group
```{r}
#Download country income classification
temp6 <- tempfile()
download.file("http://databank.worldbank.org/data/download/site-content/CLASS.xls", temp6, mode="wb")
income_class <- read_excel(temp6, sheet = 1, skip= 4)%>%
  filter(!is.na(`Income group`))%>%
  filter(`Income group` != "x")%>%
  select("Economy",  "Code", "Region", "Income group")

colnames(income_class)<-c("country", "iso3", "region", "income") 
```

#Merge all datasets
```{r}
#Join all indicators (income classification at the begining, to have countries information first)
ind2 <- list(income_class, wdi_EG.FEC.RNEW.ZS, wdi_EN.POP.SLUM.UR.ZS, wdi_SL.TLF.CACT.FE.ZS, wdi_SH.STA.SMSS.ZS, wdi_SH.H2O.SMDW.ZS, wdi_HD.HCI.OVRL, wdi_SI.POV.GINI, wdi_SE.SEC.ENRR, wdi_SH.IMM.IDPT, wdi_account.t.d.7, wdi_NY.ADJ.SVNG.GN.ZS, wdi_EN.ATM.PM25.MC.M3, wdi_ER.H2O.INTR.PC, wdi_NY.GNP.MKTP.CD, wdi_EN.ATM.GHGT.KT.CE, wdi_EN.ATM.CO2E.PC, poverty, effect, corr, regq, internet, water_efficiency, aqua, epi_indices, frag_index, women, risk, agri_value, Land_tenure, Jambeck_et_al_data, muni_waste, lpi_aggregated_ranks, Confidence_The_Government, Most_people_can_be_trusted, FAO.land.productivity, ceo_data)

#library(plyr)
integrated <- join_all(ind2, type = "left", match = "first") 
integrated <- integrated %>% select(country, everything())

###Create GNI/GHG ######
#NY.GNP.MKTP.CD/ EN.ATM.GHGT.KT.CE
integrated$gini_ghg<-integrated$NY.GNP.MKTP.CD/integrated$EN.ATM.GHGT.KT.CE

#Save database with all countries in the world
write.csv(integrated, paste0(dir_int, "Integrated_v4.csv"), row.names = FALSE)
integrated<-read.csv(paste0(dir_int, "Integrated_v4.csv"))

#The Chief Economist Office selected a list of 167 countries for the benchmarking excercise, base on tests on how some countries values could modify the estimation of regional and world scores.
#From the overall database,  here we filter the list of countries selected by the Chief Economist Office
list_countries<-ceo_data$iso3  
integrated2<-integrated%>%
  filter(iso3 %in% list_countries)

#Clean working space
rm(list=setdiff(ls(), c("dir_int", "dir_raw", "integrated", "integrated2", "ceo_data", "list_countries")))
```

#Create indicators list
Divide indicators in two lists: Two-sided higher value represents good performance or Inverse case: higher value represents bad performance 
We name the indicators only before producing the graphs, otherwise names get corruptued when save it in the csv
```{r}
#Two-sided case: Higher value is better performance, but indicator can take on negative values
#colnames(integrated2)
two_side<-c('country', "iso3", "region", "income",  "food_sec", "SL.TLF.CACT.FE.ZS","SH.H2O.SMDW.ZS", "SH.H2O.SMDW.ZS", "SH.STA.SMSS.ZS", "HD.HCI.OVRL", "SE.SEC.ENRR", "SH.IMM.IDPT", "account.t.d.7", "LGBT_acc", "wbl", "conf_gov", "trust_ppl", "NY.ADJ.SVNG.GN.ZS", "EG.FEC.RNEW.ZS", "ER.H2O.INTR.PC", "wat_qua",  "agri_value", "agri_land", "gini_ghg", "cont_corr", "gov_effect", "reg_qua", "lpi_score", "WWT.new", "waste_managed", "BHV.new", "FSH.new", "sdg9_intuse", "water_efficiency_FAO", "water_efficiency_ceo")

#Inverse case: Higher value is worse performance, (no negative)
inv_side<- c('country', "iso3", "region", "income", "risk_to_assets", "risk_wellbeing", "pop_dis",  "rain_exp", "EN.POP.SLUM.UR.ZS", "pov_1016", "SI.POV.GINI", "EN.ATM.PM25.MC.M3", "forest_loss", "ref_idp", "sec_aparat", "waste_rate", "GIB.new", "EN.ATM.CO2E.PC", "Tenure.insecurity") 
```

# Score Formulas For Income  Groups
Formulas to calculate the score of each country against its income group
```{r}
#detach plyr or the formulas won't work 
detach(package:plyr) 
#Indicators - Higher value = better performance
#score = worst country value (worldwide) - countries value/ worst country value(worldwide) - worst country value from its income group
scores_nor <- function(data, y){
  data <- data[colnames(data) %in% two_side]
  data %>%
    dplyr::mutate(across(where(is.numeric), function(x){
    (min(x, na.rm=TRUE) - x)/
      (min(x, na.rm=TRUE) - max(x[which(.$income == y)], na.rm=TRUE))}))
}

#Indicators- Higher value= worst performance
scores_inv <- function(data, y){
  data <- data[colnames(data) %in% inv_side]
  data %>%
    mutate(across(where(is.numeric), function(x){
    (max(x, na.rm=TRUE) - x)/
      (max(x, na.rm=TRUE) - min(x[which(.$income == y)], na.rm=TRUE))}))
}
```

#Score Formulas for Regional Comparison  
Formulas to calculate the score of each country against its regional group (we don't currently used this output, but it's possible to calculate this scores if desired)
```{r}
#Indicators - Higher value = better performance
scores_reg_nor <- function(data, y){
  data <- data[colnames(data) %in% two_side]
  data %>%
    mutate(across(where(is.numeric), function(x){
    (min(x, na.rm=TRUE) - x)/
      (min(x, na.rm=TRUE) - max(x[which(.$region == y)], na.rm=TRUE))}))
}

#Indicators- Higher value= worst performance
scores_reg_inv <- function(data, y){
  data <- data[colnames(data) %in% inv_side]
  data %>%
    mutate(across(where(is.numeric), function(x){
    (max(x, na.rm=TRUE) - x)/
      (max(x, na.rm=TRUE) - min(x[which(.$region == y)], na.rm=TRUE))}))
}
```

#Calculate Percentile Rank
Calcultaes country percentile value comparing all countries in the dataset
```{r}
#inverse per ranking function
per_inv <- function(x) {
  y = (1- percent_rank(x))
}

#Get percentile for two sided variables (higher value-better performance)
vars_nor<-two_side[-(1:4)]
vars_nor <- setNames(vars_nor, paste0(vars_nor, "_per")) # create new column names
integrated2 <- integrated2 %>% 
  mutate_each_(funs(percent_rank), vars_nor)

#Get percentile for inverse variables (higher value- worse performance)
vars_inv<-inv_side[-(1:4)]
vars_inv <- setNames(vars_inv, paste0(vars_inv, "_per")) # create new column names
integrated2 <- integrated2 %>% 
  mutate_each_(funs(per_inv), vars_inv)

```

#Calculate Scores per Income group (Income group calculation)
We apply score formula per income group and save the data
```{r}
options(scipen=999)

##LMICS## 
integrated_lmics_score<- scores_nor(integrated2, "Lower middle income")  
integrated_lmics_score_neg<-scores_inv(integrated2, "Lower middle income")
#Join scores
integrated_lmics_score<-left_join(integrated_lmics_score,integrated_lmics_score_neg, by=c('country', "iso3", "region", "income"))
#Filter by income group
integrated_lmics_score <- integrated_lmics_score %>% filter(income=='Lower middle income')
# Save 
write.csv(integrated_lmics_score, paste0(dir_int, "DB_SD_lmics_score.csv"), row.names = FALSE)

##UMICS## 
integrated_umics_score<- scores_nor(integrated2, "Upper middle income")  
integrated_umics_score_neg<-scores_inv(integrated2, "Upper middle income")
#Join scores
integrated_umics_score<-left_join(integrated_umics_score,integrated_umics_score_neg, by=c('country', "iso3", "region", "income"))
#Filter by income group
integrated_umics_score <- integrated_umics_score %>% filter(income=='Upper middle income')

# Save 
write.csv(integrated_umics_score, paste0(dir_int, "DB_SD_umics_score.csv"), row.names = FALSE)

#LICS
integrated_lics_score<- scores_nor(integrated2, "Low income")  
integrated_lics_score_neg<-scores_inv(integrated2, "Low income")
#Join scores
integrated_lics_score<-left_join(integrated_lics_score,integrated_lics_score_neg, by=c('country', "iso3", "region", "income"))
#Filter by income group
integrated_lics_score <- integrated_lics_score %>% filter(income=='Low income')

# Save 
write.csv(integrated_lics_score, paste0(dir_int, "DB_SD_lics_score.csv"), row.names = FALSE)

#HICS 
integrated_hics_score<- scores_nor(integrated2, "High income")  
integrated_hics_score_neg<-scores_inv(integrated2, "High income")
#Join scores
integrated_hics_score<-left_join(integrated_hics_score,integrated_hics_score_neg, by=c('country', "iso3", "region", "income"))
#Filter by income group
integrated_hics_score <- integrated_hics_score %>% filter(income=="High income")

# Save 
write.csv(integrated_hics_score, paste0(dir_int, "DB_SD_hics_score.csv"), row.names = FALSE)


##MENA## (no used, only calculated by internal use)
integrated_MENA_score<- scores_reg_nor(integrated2, "Middle East & North Africa")  
integrated_MENA_score_neg<-scores_reg_inv(integrated2, "Middle East & North Africa")
#Join scores
integrated_MENA_score<-left_join(integrated_MENA_score,integrated_MENA_score_neg, by=c('country', "iso3", "region", "income"))
#Filter by income group
integrated_MENA_score <- integrated_MENA_score %>% filter(region=='Middle East & North Africa')
# Save 
write.csv(integrated_MENA_score, paste0(dir_int, "DB_SD_MENA_score.csv"), row.names = FALSE)
```

#From this point the selection of indicators, will produce different results

Two version of the benchmarking are generated with the following code:
##v0 
Refers to a set of indicators selected and vetted by the Chief Economist Office -Sustainable Development (work lead by Jason Daniel Russ)
##v1
Refers to a set of indicators selected by the MENA - Sustainable Development team focusing on Egypt analysis  

#Calculate Pilars aggregate measures from the indicators (Global calculation)
```{r}
integrated3<-integrated2

#####  Resilence   #######
#For Resilience, the same set of indicators are used in the two versions, but for graphing proposes, generate the two variables
#V0
integrated3<-mutate(integrated3, Resilience_v0 = rowMeans(select(integrated3, c("risk_wellbeing_per", "risk_to_assets_per", "food_sec_per", "pop_dis_per", "rain_exp_per", "EN.POP.SLUM.UR.ZS_per")), na.rm = TRUE))
#V1
integrated3<-mutate(integrated3, Resilience_v1 = rowMeans(select(integrated3, c("risk_wellbeing_per", "risk_to_assets_per", "food_sec_per", "pop_dis_per", "rain_exp_per", "EN.POP.SLUM.UR.ZS_per")), na.rm = TRUE))

######  Inclusion   #######

#V0 Indicators not included compared with V1: "sec_aparat" (Security Apparatus) 
integrated3<-mutate(integrated3, Inclusion_v0 = rowMeans(select(integrated3, c("pov_1016_per", 'SL.TLF.CACT.FE.ZS_per',"SH.STA.SMSS.ZS_per", "SH.H2O.SMDW.ZS_per", "HD.HCI.OVRL_per", "SI.POV.GINI_per", "SE.SEC.ENRR_per", "SH.IMM.IDPT_per", "account.t.d.7_per", "LGBT_acc_per", "wbl_per", "trust_ppl_per", "ref_idp_per")), na.rm = TRUE))

#V1
integrated3<-mutate(integrated3, Inclusion_v1 = rowMeans(select(integrated3, c("pov_1016_per", 'SL.TLF.CACT.FE.ZS_per',"SH.STA.SMSS.ZS_per", "SH.H2O.SMDW.ZS_per", "HD.HCI.OVRL_per", "SI.POV.GINI_per", "SE.SEC.ENRR_per", "SH.IMM.IDPT_per", "account.t.d.7_per", "LGBT_acc_per", "wbl_per", "trust_ppl_per", "ref_idp_per", "sec_aparat_per")), na.rm = TRUE))

######   Sustainability  ########

#V0 Indicators not included compared with V1: ,"waste_managed_per, BHV_new_per", "FSH_new_per", "GIB_new_per", "EN.ATM.CO2E.PC_per" 
#Other indicators not included: "forest_loss_per"
integrated3<-mutate(integrated3, Sustainability_v0 = rowMeans(select(integrated3, c("NY.ADJ.SVNG.GN.ZS_per", "EN.ATM.PM25.MC.M3_per", "EG.FEC.RNEW.ZS_per", "ER.H2O.INTR.PC_per","wat_qua_per", "WWT.new_per", "waste_rate_per" )), na.rm = TRUE))

# V1 Indicators not included compared with V0: "NY.ADJ.SVNG.GN.ZS_per"
#Other indicators not included: "forest_loss_per"
integrated3<-mutate(integrated3, Sustainability_v1 = rowMeans(select(integrated3, c("EN.ATM.PM25.MC.M3_per", "EG.FEC.RNEW.ZS_per", "ER.H2O.INTR.PC_per","wat_qua_per", "WWT.new_per", "waste_rate_per", "waste_managed_per", "BHV.new_per", "FSH.new_per", "GIB.new_per", "EN.ATM.CO2E.PC_per")), na.rm = TRUE))

###### Efficiency ##############

#For Efficiency a different version of water efficiency is used in V0 and in V1

#V0 use water_efficiency_ceo - GNI/(waterwithdral*10*9) (calculated in this code- aqua datafram)
integrated3<-mutate(integrated3, Efficiency_v0 = rowMeans(select(integrated3, c("agri_value_per", "agri_land_per", "gini_ghg_per", "gov_effect_per", "cont_corr_per", "reg_qua_per", "lpi_score_per", "sdg9_intuse_per", "water_efficiency_ceo_per", "Tenure.insecurity_per")), na.rm = TRUE))

#v1 use water_efficiency_FAO_per, value added per water withdrawn, expressed in USD/m3 from FAO (details also in this code)
integrated3<-mutate(integrated3, Efficiency_v1 = rowMeans(select(integrated3, c("agri_value_per", "agri_land_per", "gini_ghg_per", "gov_effect_per", "cont_corr_per", "reg_qua_per", "lpi_score_per", "sdg9_intuse_per", "water_efficiency_FAO_per", "Tenure.insecurity_per")), na.rm = TRUE))

#Save all the database with raw values and percentile data (worldwide data)
write.csv(integrated3, paste0(dir_int, "World_SD_values_V4.csv"), row.names = FALSE)
```






