---
title: "Benchmarking_Graphs"
author: "Giuseppe Rossitti"
date: "12/05/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = "C:/Users/####/OneDrive/")
```

```{r}
library(WDI)
library(dplyr)
library(readxl)
library(xml2)
library(rvest)
library(tidyverse)
library(data.table)
library(ggplot2)
library(grid)
library(lattice)
library(survival)
library(Formula)
library(Hmisc)
#detach(package:plyr) 
```

# Set Directories
```{r}
dir_int<-"./Integrated_data/" #Folder with data generated in code Benchmarking_Data_V3
#dir_out<- "./Data/Benchmarking/SD_Profiles/Output/"              
dir_out<-"./Output/"
#In your coumputer, this directory create  separate folders for income group - ex: ./My Files/Output/lmic -./My Files/Output/umic, etc, in oder to save countries info per income group
getwd()
```

# PART 1
This file has been used to hardcode the graphs for the MENA averages for the policy paper



#Set comparators -INCOME GROUP and REGIONAL GROUP and VERSION
```{r}
#Income group (select same category)
group <- 'MENA' ### HERE CHOOSE INCOME GROUP WE WANT TO COMPARE TO FROM ABOVE VARIABES ###

country="MENA"  #use one country for tests

#Set files names to read according to comparison groups

comparison_percentile <- paste0('DB_SD_',group,'_score')
comparison_score <- paste0('DB_SD_',group,'_score')

### Version indicator
#choose 0, 1 or 20. 
#v= 0 Refers to a set of indicators selected and vetted by the Chief Economist Office -Sustainable Development (work lead by Jason Daniel Russ)
# v=1 refers to a set of indicators selected by the MENA - Sustainable Development team focusing on Egypt results 
#Each version would show a different set of indicators
#v=9 refers to a set of indicators selected by the Egyptian MoPED - Ministry of Planning and Economic Development

version <- 2 #  0,1,2 or 9 for MoPED indicators

  perctext <-1.5
  pillartext <- 3
```


#Calculate Pillars aggregate measures from the indicators (Global calculation)

```{r}
#Retreive database with all the variables generated in "Benchmarking_V3"

integrated3 <- read.csv(paste0(dir_int, "World_SD_values_V5.csv"))

# For each version add all indicators

base <- c("country","iso3","income","region")


v2 <- c("pop_dis", "rain_exp", "pov_1016", 'SL.TLF.CACT.FE.ZS', "HD.HCI.OVRL", "SI.POV.GINI", "SE.SEC.ENRR", "SH.IMM.IDPT", "account.t.d.7", "LGBT_acc", "wbl", "ref_idp", "EN.ATM.PM25.MC.M3", "EG.FEC.RNEW.ZS","wat_qua", "WWT.new", "waste_rate", "waste_managed", "BHV.new", "FSH.new", "EN.ATM.CO2E.PC" , "forest_loss", "agri_value", "agri_land", "gdp_ghg", "gov_effect", "cont_corr", "lpi_score", "water_efficiency_GDP", "SG.GEN.PARL.ZS",
"SH.MED.PHYS.ZS", "SH.UHC.SRVS.CV.XD", "acc_sani_SDG", "acc_water_SDG", "rai", "rule_law", "IT.CEL.SETS.P2", "IT.NET.USER.ZS", "rapid_trans", "displaced", "wat_stress_SDG", "glob_hunger_index", "terror", "pop_slums_SDG", "heal_01_NDG", "habi_01_NDG", "habi_02_NDG", "infr_02_NDG", "food_03_NDG", "infr_03_NDG", "heal_03_NDG", "SH.STA.AIRP.P5","SH.STA.WASH.P5","fao_withdraw_pc","ecos_04_NDG","chloroph_SDG","EG.ELC.ACCS.ZS","reg_qua","ghg_pc","pop_epid","patents","IS.SHP.GCNW.XQ","dai", "EG.EGY.PRIM.PP.KD")

v2_per <- paste(v2, "_per", sep='')


# Subset the database based on the indicators used


integrated3 <- subset(integrated3, select = c(base,v2,v2_per))



#Resilience
integrated3<-mutate(integrated3, Resilience_v2 = rowMeans(select(integrated3, c( "pop_dis_per", "rain_exp_per", "pop_epid_per", "pop_slums_SDG_per", "displaced_per" , "terror_per" , "heal_01_NDG_per" , "habi_01_NDG_per",  "habi_02_NDG_per",   "infr_02_NDG_per","infr_03_NDG_per" ,  "food_03_NDG_per",  "SH.MED.PHYS.ZS_per", "heal_03_NDG_per" ,"glob_hunger_index_per","wat_stress_SDG_per" )), na.rm = TRUE))
                                                                 
  
#Inclusion
integrated3<-mutate(integrated3, Inclusion_v2 = rowMeans(select(integrated3, c("pov_1016_per", 'SL.TLF.CACT.FE.ZS_per', "HD.HCI.OVRL_per", "SI.POV.GINI_per", "SE.SEC.ENRR_per", "SH.IMM.IDPT_per", "account.t.d.7_per", "LGBT_acc_per", "wbl_per",  "ref_idp_per", "SG.GEN.PARL.ZS_per","rai_per" ,"acc_sani_SDG_per", "acc_water_SDG_per","SH.UHC.SRVS.CV.XD_per", "EG.ELC.ACCS.ZS_per" )), na.rm = TRUE))

#Sustainability 
integrated3<-mutate(integrated3, Sustainability_v2 = rowMeans(select(integrated3, c("EN.ATM.PM25.MC.M3_per", "EG.FEC.RNEW.ZS_per", "wat_qua_per", "WWT.new_per", "waste_rate_per", "waste_managed_per", "BHV.new_per", "FSH.new_per", "ghg_pc_per", "EN.ATM.CO2E.PC_per" , "forest_loss_per", "SH.STA.AIRP.P5_per" , "SH.STA.WASH.P5_per", "ecos_04_NDG_per", "chloroph_SDG_per", "fao_withdraw_pc_per" )), na.rm = TRUE))

#Efficiency 
integrated3<-mutate(integrated3, Efficiency_v2 = rowMeans(select(integrated3, c("agri_value_per", "agri_land_per", "gdp_ghg_per", "gov_effect_per", "cont_corr_per", "lpi_score_per",  "water_efficiency_GDP_per","rule_law_per" , "IT.CEL.SETS.P2_per", "IT.NET.USER.ZS_per","rapid_trans_per" ,"EG.EGY.PRIM.PP.KD_per" , "reg_qua_per","patents_per","IS.SHP.GCNW.XQ_per","dai_per")), na.rm = TRUE))  

#Save all the database with raw values and percentile data (worldwide data)
write.csv(integrated3, paste0(dir_int, "World_SD_values_V5_index.csv"), row.names = FALSE)
```



# Part II - GRAPHING INDICADORS
If the composition of the pillars for each version doesn't change, start running the code from here.
Last update of the indicators list for the two versions: Feb 26, 2021


#Dataset creation 
```{r}
# Load country dataset to create list of countries per income group that we will used in the loop

country_estimates_global <- read.csv(paste0(dir_int,"World_SD_values_V5_index.csv"))

# Lower MICS
country_estimates <- country_estimates_global %>% filter(income=='Lower middle income')
lmics <- unique(country_estimates$iso3)
lmics <- as.character(lmics)

# Low income
country_estimates <- country_estimates_global %>% filter(income=='Low income')
lics <- unique(country_estimates$iso3)
lics <- as.character(lics)

# Upper MICS
country_estimates <- country_estimates_global %>% filter(income=='Upper middle income')
umics <- unique(country_estimates$iso3)
umics <- as.character(umics)

# High Income
country_estimates <- country_estimates_global %>% filter(income=='High income')
hics <- unique(country_estimates$iso3)
hics <- as.character(hics)

```




# Country Percentil dataset: clean and prepare 
Here we rename the variables of the raw values and the percentile ranking (all variables from the two versions)
```{r}
### COUNTRY Percentile DATASET ### 
###         World              ###

#Load raw and percentile value data generated before 
country_all <- read.csv(paste0(dir_int,"World_SD_values_V5_index.csv"))


##country_all$pop_dis<-as.numeric(as.character(country_all$pop_dis))
##country_all$pop_dis<-format(round(country_all$pop_dis, 2), nsmall = 2)


#Resilience
colnames(country_all)<-str_replace(colnames(country_all), "glob_hunger_index", "(R3) *Global Hunger Index")
colnames(country_all)<-str_replace(colnames(country_all), "terror", "(R3) *Deaths from conflict and terrorism (per 100,000)")
colnames(country_all)<-str_replace(colnames(country_all), "pop_dis", "(R1) *Population affected by disasters %")
colnames(country_all)<-str_replace(colnames(country_all), "pop_slums_SDG", "(R3) *Proportion of urban population living in slums")
colnames(country_all)<-str_replace(colnames(country_all), "rain_exp", "(R1) *Rainfall shock exposure %")
colnames(country_all)<-str_replace(colnames(country_all), "pop_epid", "(R3) *Population exposed to epidemics (per 100,000)")
colnames(country_all)<-str_replace(colnames(country_all), "heal_01_NDG", "(R2) *Projected change of deaths from climate change induced diseases")
colnames(country_all)<-str_replace(colnames(country_all), "habi_01_NDG", "(R2) *Projected change of warm periods")
colnames(country_all)<-str_replace(colnames(country_all), "habi_02_NDG", "(R2) *Projected change of flood hazard")
colnames(country_all)<-str_replace(colnames(country_all), "heal_03_NDG", "(R4) *Dependency on external resource for health services")
colnames(country_all)<-str_replace(colnames(country_all), "food_03_NDG", "(R4) *Food import dependency")
colnames(country_all)<-str_replace(colnames(country_all), "infr_02_NDG", "(R2) *Projected change of sea level rise impacts")
colnames(country_all)<-str_replace(colnames(country_all), "infr_03_NDG", "(R4) *Dependency on imported energy")
colnames(country_all)<-str_replace(colnames(country_all), "displaced", "(R1) *IDPs due to natural disasters (cases per 100,000)")
colnames(country_all)<-str_replace(colnames(country_all), "wat_stress_SDG", "(R1) *Water Stress SDG 6.4")
colnames(country_all)<-str_replace(colnames(country_all), "SH.MED.PHYS.ZS", "(R4) Physicians (per 1,000 people)")


#Inclusion
colnames(country_all)<-str_replace(colnames(country_all), "pov_1016", "(I1) *Extreme poverty headcount %")
colnames(country_all)<-str_replace(colnames(country_all), "SL.TLF.CACT.FE.ZS", "(I2) Female labor participation %")
colnames(country_all)<-str_replace(colnames(country_all), "HD.HCI.OVRL", "(I3) Human Capital Index")
colnames(country_all)<-str_replace(colnames(country_all), "SI.POV.GINI", "(I1) *Gini Index")
colnames(country_all)<-str_replace(colnames(country_all), "SE.SEC.ENRR", "(I3) Secondary school enrollment %")
colnames(country_all)<-str_replace(colnames(country_all), "SH.IMM.IDPT", "(I3) Immunization DPT %")
colnames(country_all)<-str_replace(colnames(country_all), "account.t.d.7", "(I1) Account ownership (poorest 40%)")
colnames(country_all)<-str_replace(colnames(country_all), "LGBT_acc", "(I2) LGBT Acceptance Index")
colnames(country_all)<-str_replace(colnames(country_all), "wbl", "(I2) Women, Business & Law Index")
colnames(country_all)<-str_replace(colnames(country_all), "ref_idp", "(I1) *Refugees & IDPs index")
colnames(country_all)<-str_replace(colnames(country_all), "SG.GEN.PARL.ZS", "(I2) Women in national parliaments %")
colnames(country_all)<-str_replace(colnames(country_all), "EG.ELC.ACCS.ZS", "(I4) Access to electricity %")
colnames(country_all)<-str_replace(colnames(country_all), "acc_sani_SDG", "(I4) Basic access to sanitation %")
colnames(country_all)<-str_replace(colnames(country_all), "acc_water_SDG", "(I4) Basic access to water %")
colnames(country_all)<-str_replace(colnames(country_all), "rai", "(I4) Rural Access Index")
colnames(country_all)<-str_replace(colnames(country_all), "SH.UHC.SRVS.CV.XD", "(I3) Universal health coverage (UHC) index %")



#Sustainability
colnames(country_all)<-str_replace(colnames(country_all), "EN.ATM.PM25.MC.M3", "(S1) *PM2.5 mean annual exposure (\U00B5g/m3)")
colnames(country_all)<-str_replace(colnames(country_all), "forest_loss", "(S4) *Forest loss %")
colnames(country_all)<-str_replace(colnames(country_all), "EG.FEC.RNEW.ZS", "(S3) Renewable energy consumption %")
colnames(country_all)<-str_replace(colnames(country_all), "wat_qua", "(S3) Water Quality SDG 6.3")
colnames(country_all)<-str_replace(colnames(country_all), "WWT.new", "(S2) Wastewater treated (primary) %")
colnames(country_all)<-str_replace(colnames(country_all), "waste_managed", "(S2) Solid waste properly disposed %")
colnames(country_all)<-str_replace(colnames(country_all), "waste_rate", "(S2) *Municipal solid waste (kg/pc/day)")
colnames(country_all)<-str_replace(colnames(country_all), "BHV.new", "(S4) Biodiversity Habitat Index")
colnames(country_all)<-str_replace(colnames(country_all), "FSH.new", "(S4) Fisheries Index")
colnames(country_all)<-str_replace(colnames(country_all), "ghg_pc", "(S1) *GHG emissions per capita (% change)")
colnames(country_all)<-str_replace(colnames(country_all), "EN.ATM.CO2E.PC", "(S1) *CO2 emissions (MT pc)")
colnames(country_all)<-str_replace(colnames(country_all), "ecos_04_NDG", "(S3) *Ecological Footprint")
colnames(country_all)<-str_replace(colnames(country_all), "fao_withdraw_pc", "(S3) *Water withdrawal per capita (m3/year pc)")
colnames(country_all)<-str_replace(colnames(country_all), "chloroph_SDG", "(S4) *Chlorophyll-a deviations in coastal water %")
colnames(country_all)<-str_replace(colnames(country_all), "SH.STA.AIRP.P5", "(S1) *Mortality due to air pollution (per 100,000)")
colnames(country_all)<-str_replace(colnames(country_all), "SH.STA.WASH.P5", "(S2) *Mortality due to unsafe WASH services (per 100,000)")


#Efficiency
colnames(country_all)<-str_replace(colnames(country_all), "agri_land", "(E4) Agri. land productivity ($/ha)")
colnames(country_all)<-str_replace(colnames(country_all), "agri_value", "(E1) Agri. value added per worker")
colnames(country_all)<-str_replace(colnames(country_all), "gdp_ghg", "(E4) Total GDP/GHG emissions")
colnames(country_all)<-str_replace(colnames(country_all), "gov_effect", "(E2) Governance effectiveness")
colnames(country_all)<-str_replace(colnames(country_all), "cont_corr", "(E2) Control of corruption")
colnames(country_all)<-str_replace(colnames(country_all), "reg_qua", "(E2) Regulatory quality")
colnames(country_all)<-str_replace(colnames(country_all), "lpi_score", "(E1) Logistic Performance Index")
colnames(country_all)<-str_replace(colnames(country_all), "IT.NET.USER.ZS", "(E3) Individuals using internet %")
colnames(country_all)<-str_replace(colnames(country_all), "IT.CEL.SETS.P2", "(E3) Mobile cellular subscriptions (per 100 people)")
colnames(country_all)<-str_replace(colnames(country_all), "rule_law", "(E2) Rule of law")
colnames(country_all)<-str_replace(colnames(country_all), "rapid_trans", "(E3) Rapid transit to resident ratio (km/million)")
colnames(country_all)<-str_replace(colnames(country_all), "EG.EGY.PRIM.PP.KD", "(E4) *Energy intensity (MJ/$)")
colnames(country_all)<-str_replace(colnames(country_all), "patents", "(E1) Patents (per 100,000 people)")  
colnames(country_all)<-str_replace(colnames(country_all), "dai", "(E1) Digital Penetration Index")  
colnames(country_all)<-str_replace(colnames(country_all), "water_efficiency_GDP", "(E4) Water productivity (GDP/m3)")
colnames(country_all)<-str_replace(colnames(country_all), "IS.SHP.GCNW.XQ", "(E3) Shipping connectivity index")



```

# Get the aggregate values of median/sd for each income group (to use in the table comparison we will create in excel)
```{r}
options(scipen=999) #remove scientific notation

#Short income group name for graphs
country_all$income_red <- ifelse(country_all$income == "High income", "HIC",
                                ifelse(country_all$income ==  "Upper middle income", 'UMIC',
                                       ifelse(country_all$income ==  "Lower middle income", 'LMIC',
                                               ifelse(country_all$income ==  "Low income", 'LIC', 'Other'))))

#Aspirational income group: income group "one level up"
country_all$income_aspiration <- ifelse(country_all$income_red == "HIC", "HIC",
                                ifelse(country_all$income_red == 'UMIC', "HIC", 
                                       ifelse(country_all$income_red == 'LMIC', 'UMIC',
                                               ifelse(country_all$income_red == 'LIC', 'LMIC', 'Other'))))


#Short regional group for graphs
country_all$region_red <- ifelse(country_all$region == "South Asia", "SA",
                                ifelse(country_all$region ==  "Europe & Central Asia", 'ECA',
                                       ifelse(country_all$region ==  "Middle East & North Africa", 'MENA',
                                              ifelse(country_all$region ==  "Sub-Saharan Africa", 'SSA',
                                                     ifelse(country_all$region ==  "Latin America & Caribbean", 'LAC',
                                                        ifelse(country_all$region ==  "East Asia & Pacific", 'EAP',  
                                               ifelse(country_all$region ==  "North America", 'NAC', 'Other')))))))


# MEDIAN
income_median <- country_all%>%  group_by(region_red)%>%
  select(-matches('_per'))%>% dplyr::summarise(across(where(is.numeric), list(median= ~median(., na.rm = T)), .names = "{col}"))
income_median<- reshape2::melt(income_median, id.vars=c("region_red"), variable.name="indicator", value.name="median")

#MEAN
income_mean <- country_all%>%group_by(region_red)%>%
  select(-matches('_per'))%>% dplyr::summarise(across(where(is.numeric), list(mean= ~mean(., na.rm = T)), .names = "{col}"))
income_mean<- reshape2::melt(income_mean, id.vars=c("region_red"), variable.name="indicator", value.name="mean")

#SD
income_sd <- country_all%>% group_by(region_red)%>%
  select(-matches('_per'))%>% dplyr::summarise(across(where(is.numeric), list(sd= ~sd(., na.rm = T)), .names = "{col}"))
income_sd<- reshape2::melt(income_sd, id.vars=c("region_red"), variable.name="indicator", value.name="sd")

#Merge MEAN, MEDIAN, SD 
income_info <- merge(income_mean, income_median) %>%  merge(income_sd)

#Get ranges for SD  (Mean) - Later use to estimate if the countries value is one standar deviation above or below, or within one SD of the Mean
income_info$sd_mean_up<-income_info$mean + income_info$sd
income_info$sd_mean_down<-income_info$mean - income_info$sd

##Get ranges for SD  (Median) -Later use to estimate if the countries value is one standar deviation above or below, or within one SD of the Median
income_info$sd_median_up<-income_info$median + income_info$sd
income_info$sd_median_down<-income_info$median - income_info$sd
```

# Prepare data for PERCENTILE RANKING BAR GRAPH
```{r}
#Duplicate a version of country_all for transformation- country_all needs to remain the same to be use in the percentile rank graph

country_all2<-country_all

#Select ranking values
country_all2<-country_all2%>% select(country, iso3, income_red, region_red, paste0("Resilience_v",version), paste0("Inclusion_v",version), paste0("Sustainability_v",version), paste0("Efficiency_v",version))

#Transform to long format for graph
country_long_complete <- reshape2::melt(country_all2,
        # ID variables - all the variables to keep but not split apart on
    id.vars=c("country", "iso3","income_red", "region_red"),
    variable.name="pillar",
    value.name="percentil"
)

#Get the median value for income group & transform to long format - this would be use for the graph bars 
median_income<- country_all2 %>%
  group_by(income_red)%>%
    dplyr::summarise(across(where(is.numeric), function(x){ median(x, na.rm=TRUE)}))

median_income_long <- reshape2::melt(median_income,
        # ID variables - all the variables to keep but not split apart on
    id.vars=c("income_red"),
    variable.name="pillar",
    value.name="median_income")

#Join data 
country_long_complete<-left_join(country_long_complete, median_income_long, by=c("pillar", "income_red"))
```

# From this point the selection between versions will affect the outcomes 

#Function for PERCENTILE RANKING BAR GRAPH -
```{r}
for(i in country){
  #Duplicate  a version of country long for subsetting 
  country_long<-country_long_complete

  country_long<-country_long%>% filter(str_detect(pillar, paste0("v",version)))
  median_income_filter<-median_income_long%>% filter(str_detect(pillar, paste0("v",version)))


#Get varible to identify the country in the graph
country_long<-country_long%>%
  mutate(country_ind = ifelse(iso3 == i , 1, 0))

##Get regional group
regional_group_df<-country_long%>%
  filter(iso3 == i)%>%
  select(region_red)

regional_group<-regional_group_df[1,1]

#Filter country and arrange percentiles values for graph (since it is a facet graph, percentile arrangement gets messy)
#Establish regional group beforehand
country_long<-country_long%>%
  dplyr::filter(region_red=="MENA")%>%
  dplyr::filter(!is.na(percentil))%>%
  ungroup() %>%
  arrange(pillar, (desc(percentil)))%>%
  mutate(r = row_number())%>%
  mutate(pillar_name = str_replace(pillar, "_v0|_v1|_v2|_v9", ""))

country_long$pillar_name_f<- factor(country_long$pillar_name, levels= c("Resilience", "Inclusion", "Sustainability", "Efficiency"))

#Once filtered by region, get regional median graph and for the next graph  
country_long<-country_long%>%
  group_by(pillar)%>%
  mutate(median_regional= median(percentil, na.rm=T))

# prepare regional median for next graph 
regional_median<-country_long%>%
  group_by(pillar)%>%
  dplyr::summarise(percentil_median= median(percentil, na.rm=T))%>%
  mutate(group = "MENA")%>%
  select(group, everything())


#Rename col, add iso3 and merge bases

colnames(median_income_filter)<-c("group", "pillar", "percentil_median")


country_median_filter<-country_long_median%>%
  dplyr::select(country, pillar, percentil, iso3)
colnames(country_median_filter)<-c("group",  "pillar", "percentil_median", "iso3")


#Merge regional median/income median/country median
graph_bar2<-rbind(median_income_filter, regional_median)


#Prepare for graph
graph_bar2<-graph_bar2%>%
  dplyr::filter(!is.na(percentil_median))%>%
  ungroup() %>%
  arrange(pillar, (desc(percentil_median)))%>%
  mutate(r = row_number())%>%
  mutate(pillar_name = str_replace(pillar, "_v0|_v1|_v2|_v9", ""))

graph_bar2$pillar_name_f<- factor(graph_bar2$pillar_name, levels= c("Resilience", "Inclusion", "Sustainability", "Efficiency"))

graph_bar2<-graph_bar2%>%
  mutate(mena = ifelse(group == "MENA" , 1, 0))

graph2  <-  ggplot(graph_bar2, aes(x = r, y = percentil_median*100, fill = pillar_name_f, color = as.factor(mena))) + 
  geom_col(size=1.2, alpha=0.7)+
  #Red line (m)
  geom_hline( yintercept = 50 , color="red3", size=1)+ 
  facet_grid(~pillar_name_f, scales = "free")+
  #scale_y_continuous(labels = value, breks= value)+
    labs(y = "Median percentile rank",
  title = "")+
theme_minimal()+
  theme(strip.text.x = element_text(size = 19, face = "bold"),
  axis.text.y = element_text(size = 16, hjust = .5, vjust = .5),
  plot.title=element_text(size=14, face = "bold"),
               axis.title.x=element_blank(),
  axis.text.x = element_text(size= 14),
                 legend.position = "none",
  panel.grid.minor = element_blank(), 
  panel.grid.major = element_blank())+
  scale_fill_manual(values = c("darkcyan", "red2" ,"goldenrod1", "darkmagenta"))+
  scale_color_manual(values=c("grey25", "green3"))+
  scale_x_continuous(breaks = graph_bar2$r, labels = str_wrap(graph_bar2$group, width = 7)) +
  geom_text(aes(x=r, y=(percentil_median*100)+3 , label= as.integer(percentil_median*100)), color="black",alpha=1, size=6, inherit.aes = FALSE )
  
ggsave(graph2, file=paste0(dir_out, group,'/',"MENA_barplot_per_group.pdf"), width=25, height=10)


## Replicate graph with world regions instead of income groups


#Get the median value for income group & transform to long format - this would be use for the graph bars 
median_reg<- country_all2 %>%
  group_by(region_red)%>%
    dplyr::summarise(across(where(is.numeric), function(x){ median(x, na.rm=TRUE)}))

median_reg_long <- reshape2::melt(median_reg,
        # ID variables - all the variables to keep but not split apart on
    id.vars=c("region_red"),
    variable.name="pillar",
    value.name="median_income")

colnames(median_reg_long)<-c("group", "pillar", "percentil_median")


#Merge regional median/income median/country median
graph_bar3<-median_reg_long


graph_bar3<-graph_bar3%>%
  mutate(mena = ifelse(group == "MENA" , 1, 0))



#Prepare for graph
graph_bar3<-graph_bar3%>%
  dplyr::filter(!is.na(percentil_median))%>%
  ungroup() %>%
  arrange(pillar, (desc(percentil_median)))%>%
  mutate(r = row_number())%>%
  mutate(pillar_name = str_replace(pillar, "_v0|_v1|_v2|_v9", ""))

graph_bar3$pillar_name_f<- factor(graph_bar3$pillar_name, levels= c("Resilience", "Inclusion", "Sustainability", "Efficiency"))

graph_bar3<-graph_bar3%>%
  mutate(mena = ifelse(group == "MENA" , 1, 0))

graph3  <-  ggplot(graph_bar3, aes(x = r, y = percentil_median*100, fill = pillar_name_f, color = as.factor(mena))) + 
  geom_col(size=1.2, alpha=0.7)+
  #Red line (m)
  geom_hline( yintercept = 50 , color="red3", size=1)+ 
  facet_grid(~pillar_name_f, scales = "free")+
  #scale_y_continuous(labels = value, breks= value)+
    labs(y = "Median percentile rank",
  title = "")+
theme_minimal()+
  theme(strip.text.x = element_text(size = 19, face = "bold"),
  axis.text.y = element_text(size = 16, hjust = .5, vjust = .5),
  plot.title=element_text(size=14, face = "bold"),
               axis.title.x=element_blank(),
  axis.text.x = element_text(size= 14),
                 legend.position = "none",
  panel.grid.minor = element_blank(), 
  panel.grid.major = element_blank())+
  scale_fill_manual(values = c("darkcyan", "red2" ,"goldenrod1", "darkmagenta"))+
  scale_color_manual(values=c("grey25", "green3"))+
  scale_x_continuous(breaks = graph_bar3$r, labels = str_wrap(graph_bar3$group, width = 7)) +
  geom_text(aes(x=r, y=(percentil_median*100)+3 , label= as.integer(percentil_median*100)), color="black",alpha=1, size=6, inherit.aes = FALSE )
  
ggsave(graph3, file=paste0(dir_out, group,'/',"MENA_barplot_per_region.pdf"), width=25, height=10)




## Replicate graph with sub-regions instead of income groups

country_all3 <- country_all2 

country_all3 <- country_all3 %>%
  filter(region_red=="MENA")

subreg <- c("North Africa","Bab-el-Mandeb","North Africa","Other","Mashreq","Other","Mashreq","GCC","Mashreq",
            "North Africa","Other","North Africa","GCC","GCC","GCC","Mashreq","North Africa",
            "GCC","Mashreq","Bab-el-Mandeb")

country_all3 <- cbind(country_all3,subreg)

country_all3 <- country_all3 %>%
  filter(subreg!="Other")


#Get the median value for income group & transform to long format - this would be use for the graph bars 
median_subreg<- country_all3 %>%
  group_by(subreg)%>%
    dplyr::summarise(across(where(is.numeric), function(x){ median(x, na.rm=TRUE)}))


median_subreg_long <- reshape2::melt(median_subreg,
        # ID variables - all the variables to keep but not split apart on
    id.vars=c("subreg"),
    variable.name="pillar",
    value.name="median_income")



colnames(median_subreg_long)<-c("group", "pillar", "percentil_median")


#Merge regional median/income median/country median
graph_bar4<- rbind(median_subreg_long,regional_median[,1:3])


graph_bar4<-graph_bar4%>%
  mutate(mena = ifelse(group == "MENA" , 1, 0))



#Prepare for graph
graph_bar4<-graph_bar4%>%
  dplyr::filter(!is.na(percentil_median))%>%
  ungroup() %>%
  arrange(pillar, (desc(percentil_median)))%>%
  mutate(r = row_number())%>%
  mutate(pillar_name = str_replace(pillar, "_v0|_v1|_v2|_v9", ""))

graph_bar4$pillar_name_f<- factor(graph_bar4$pillar_name, levels= c("Resilience", "Inclusion", "Sustainability", "Efficiency"))

graph_bar4<-graph_bar4%>%
  mutate(mena = ifelse(group == "MENA" , 1, 0))

graph4  <-  ggplot(graph_bar4, aes(x = r, y = percentil_median*100, fill = pillar_name_f, color = "black")) + 
  geom_col(size=1.2, alpha=0.7)+
  #Red line (m)
  geom_hline( yintercept = 50 , color="red3", size=1)+ 
  facet_grid(~pillar_name_f, scales = "free")+
  #scale_y_continuous(labels = value, breks= value)+
    labs(y = "Median percentile rank",
  title = "")+
theme_minimal()+
  theme(strip.text.x = element_text(size = 19, face = "bold"),
  axis.text.y = element_text(size = 16, hjust = .5, vjust = .5),
  plot.title=element_text(size=14, face = "bold"),
               axis.title.x=element_blank(),
  axis.text.x = element_text(size= 14),
                 legend.position = "none",
  panel.grid.minor = element_blank(), 
  panel.grid.major = element_blank())+
  scale_fill_manual(values = c("darkcyan", "red2" ,"goldenrod1", "darkmagenta"))+
  scale_color_manual(values=c("grey25", "green3"))+
  scale_x_continuous(breaks = graph_bar4$r, labels = str_wrap(graph_bar4$group, width = 7)) +
  geom_text(aes(x=r, y=(percentil_median*100)+3 , label= as.integer(percentil_median*100)), color="black",alpha=1, size=6, inherit.aes = FALSE )
  
ggsave(graph4, file=paste0(dir_out, group,'/',"MENA_barplot_per_subregion.pdf"), width=25, height=10)






} 

```






# Loop to prepare data for SCORE PILLARS COMPARISON GRAPH - CIRCULAR (PER PILLARS)
```{r}
### COUNTRY Percentile DATASET ###


median_reg_indi<- country_all %>%
  group_by(region_red)%>%
    dplyr::summarise(across(where(is.numeric), function(x){ median(x, na.rm=TRUE)}))

median_reg_indi<-median_reg_indi%>%
  filter(region_red == "MENA")


atatat <- data.frame("MENA region","MENA","Upper middle income","Middle East & North Africa","UMIC","HIC")
colnames(atatat) <- c("country","iso3","income","region","income_red","income_aspiration")

median_reg_indi <- cbind(median_reg_indi,atatat)


country_all <- rbind(country_all, median_reg_indi)

country <- "MENA"

for(i in country){

country_tot<-country_all  
country_tot<- country_tot[country_tot$iso3 == i, ]
country_percent<-country_tot %>% select(matches('_per'))
country_percent <- as.data.frame(t(as.matrix(country_percent)))
country_percent <- country_percent %>% rownames_to_column("indicator")
colnames(country_percent)<-c("indicator", "percentil")
country_percent$indicator<-str_replace(country_percent$indicator, "_per", "")


#### Country Data Raw values ####

country_values<-country_tot %>% select(-matches('_per'))
country_values <- as.data.frame(t(as.matrix(country_values)))
country_values <- country_values %>% rownames_to_column("indicator")
colnames(country_values)<-c("indicator", "raw_value")


#Set indicators categories

efficiency<-c("Agri. land productivity ($/ha)", "Agri. value added per worker", "Total GDP/GHG emissions","Governance effectiveness", "Control of corruption", "Logistic Performance Index", "Pop. using internet %", "Water use efficiency (USD/m3)", "Logistic Performance Index", "*Tenure insecurity %", "Water use efficiency (USD/m3)", "Water use efficiency (GDP/m3)", "Gov spending on essential services, education %", "*Gross debt (% GDP)", "Budget balance (% GDP)", "Tax revenues (% tot revenues)", "*Capital stock (% GDP)","(E4) Agri. land productivity ($/ha)", "(E1) Agri. value added per worker", "(E4) Total GDP/GHG emissions", "(E2) Governance effectiveness", "(E2) Control of corruption", "(E2) Regulatory quality", "(E1) Logistic Performance Index", "(E3) Individuals using internet %", "(E3) Mobile cellular subscriptions (per 100 people)", "(E2) Rule of law", "(E3) Rapid transit to resident ratio (km/million)", "(E4) *Energy intensity (MJ/$)", "(E1) Patents (per 100,000 people)", "(E1) Digital Penetration Index", "(E4) Water productivity (GDP/m3)","(E3) Shipping connectivity index", "(E1) Global Competitiveness Index", "(E4) *Maternal mortality (per 100,000 live births)")

sustainability<-c("Adjusted net savings %", "*PM2.5 mean annual exposure (\U00B5g/m3)", "Renewable energy consumption %", "Renewable internal freshwater (m3 pc)", "Water Quality SDG 6.3", "Wastewater treated (primary) %", "Solid waste properly disposed %", "*Municipal solid waste (kg/pc/day)", "Biodiversity Habitat Index", "Fisheries Index", "GHG intensity growth rate", "*CO2 emissions (MT pc)", "*Forest loss %", "*CO2 emissions (kg/$GDP)","(S1) *PM2.5 mean annual exposure (\U00B5g/m3)", "(S4) *Forest loss %", "(S3) Renewable energy consumption %","(S2) Wastewater treated (primary) %","(S2) Solid waste properly disposed %","(S2) *Municipal solid waste (kg/pc/day)","(S4) Biodiversity Habitat Index","(S4) Fisheries Index", "(S1) *GHG emissions per capita (% change)", "(S1) *CO2 emissions (MT pc)","(S3) *Ecological Footprint","(S3) *Water withdrawal per capita (m3/year pc)","(S4) *Chlorophyll-a deviations in coastal water %","(S1) *Mortality due to air pollution (per 100,000)","(S2) *Mortality due to unsafe WASH services (per 100,000)", "(S3) Water Quality SDG 6.3")

inclusion<-c("*Extreme poverty headcount %", "*Gini Index", "Immunization DPT %", "Safely managed sanitation %", "Safely managed drinking water %", "Immunization DPT %",  "Secondary school enrollment %", "Human Capital Index", "Account ownership (poorest 40%)", "Female labor participation %", "Women, Business & Law Index",  "LGBT Acceptance Index",  "Most ppl. can be trusted %", "*Refugees & IDPs index", "*Security apparatus index", "Confidence in the government",  "*Poverty headcount %", "Women in national parliaments %", "Women in managerial positions %", "Women account ownership %", "Access to electricity %", "Population covered by social insurance %", "Women literacy rate %", "Youth NEET %","SMEs owned by women %", "(I1) *Extreme poverty headcount %", "SL.TLF.CACT.FE.ZS", "(I2) Female labor participation %", "(I3) Human Capital Index", "(I1) *Gini Index","(I3) Secondary school enrollment %", "(I3) Immunization DPT %", "(I1) Account ownership (poorest 40%)","(I2) LGBT Acceptance Index"
, "(I2) Women, Business & Law Index", "(I1) *Refugees & IDPs index", "(I2) Women in national parliaments %", "(I4) Access to electricity %", "(I4) Basic access to sanitation %", "(I4) Basic access to water %", "(I4) Rural Access Index", "(I3) Universal health coverage (UHC) index %", "Basic access to sanitation %", "Basic access to water %" )

resilience<-c("Food Security Index", "*Risk to wellbeing %", "*Risk to asset %","*Population affected by disasters %", "*Rainfall shock exposure %", "*Urban slum population %","*Mortality road traffic injury (per 100,000)", "GDP per capita growth (annual %)", "*Unemployment (% labor force)",  "*Inflation, consumer prices (annual %)", "*Hepatitis B prevalence %","(R3) *Global Hunger Index", "(R3) *Deaths from conflict and terrorism (per 100,000)", "(R1) *Population affected by disasters %","(R3) *Proportion of urban population living in slums", "(R1) *Rainfall shock exposure %", "(R3) *Population exposed to epidemics (per 100,000)", "(R2) *Projected change of deaths from climate change induced diseases", "habi_01_NDG", "(R2) *Projected change of warm periods", "(R2) *Projected change of flood hazard", "(R4) *Dependency on external resource for health services", "(R4) *Food import dependency", "(R2) *Projected change of sea level rise impacts", "(R4) *Dependency on imported energy", "(R1) *IDPs due to natural disasters (cases per 100,000)", "(R1) *Water Stress SDG 6.4", "(R4) Physicians (per 1,000 people)")

#Assign categories (number set to appear in the RISE order in the graph)

country_percent$category <- ifelse(country_percent$indicator %in% efficiency, '4.Efficiency',
                                   ifelse(country_percent$indicator %in% sustainability, '3.Sustainability',
                                          ifelse(country_percent$indicator %in% resilience, '1.Resilience', 
                                                 ifelse(country_percent$indicator %in% inclusion, '2.Inclusion', 'Other'))))


country_percent <- country_percent%>% filter(category!='Other') 

#Join percentage and raw value
country_percent <-left_join(country_percent, country_values, by="indicator")
country_percent$raw_value<-as.numeric(as.character(country_percent$raw_value))
country_percent$raw_value<-format(round(country_percent$raw_value, 2), nsmall = 2)


# Format score data for graphs
#country_percent <- country_percent[,c(3,1,2,4)]
country_percent$percentil <- as.numeric(as.character(country_percent$percentil))
country_percent$percentil<-country_percent$percentil*100
country_percent <- country_percent[order(country_percent$category),]

#create first databases for percentile ranking (global)

country_percent$percentil<-as.integer(country_percent$percentil)
country_percent<-country_percent%>% select(indicator, percentil, raw_value, category)
write.csv(country_percent,paste0(dir_out, group,'/',i,"_percentil.csv"), row.names = FALSE)
}



### COUNTRY SCORE DATASET ###

country_score <- read.csv(paste0(dir_int, "DB_SD_all_score.csv"))


#Subset Country score to include only variables for the version in question

country_score <- subset(country_score, select = c(base,v2))


### Names include subcategory for alphabetical order  
  
#Resilience
colnames(country_score)<-str_replace(colnames(country_score), "glob_hunger_index", "(R3) *Global Hunger Index")
colnames(country_score)<-str_replace(colnames(country_score), "terror", "(R3) *Deaths from conflict and terrorism (per 100,000)")
colnames(country_score)<-str_replace(colnames(country_score), "pop_dis", "(R1) *Population affected by disasters %")
colnames(country_score)<-str_replace(colnames(country_score), "pop_slums_SDG", "(R3) *Proportion of urban population living in slums")
colnames(country_score)<-str_replace(colnames(country_score), "rain_exp", "(R1) *Rainfall shock exposure %")
colnames(country_score)<-str_replace(colnames(country_score), "pop_epid", "(R3) *Population exposed to epidemics (per 100,000)")
colnames(country_score)<-str_replace(colnames(country_score), "heal_01_NDG", "(R2) *Projected change of deaths from climate change induced diseases")
colnames(country_score)<-str_replace(colnames(country_score), "habi_01_NDG", "(R2) *Projected change of warm periods")
colnames(country_score)<-str_replace(colnames(country_score), "habi_02_NDG", "(R2) *Projected change of flood hazard")
colnames(country_score)<-str_replace(colnames(country_score), "heal_03_NDG", "(R4) *Dependency on external resource for health services")
colnames(country_score)<-str_replace(colnames(country_score), "food_03_NDG", "(R4) *Food import dependency")
colnames(country_score)<-str_replace(colnames(country_score), "infr_02_NDG", "(R2) *Projected change of sea level rise impacts")
colnames(country_score)<-str_replace(colnames(country_score), "infr_03_NDG", "(R4) *Dependency on imported energy")
colnames(country_score)<-str_replace(colnames(country_score), "displaced", "(R1) *IDPs due to natural disasters (cases per 100,000)")
colnames(country_score)<-str_replace(colnames(country_score), "wat_stress_SDG", "(R1) *Water Stress SDG 6.4")
colnames(country_score)<-str_replace(colnames(country_score), "SH.MED.PHYS.ZS", "(R4) Physicians (per 1,000 people)")


#Inclusion
colnames(country_score)<-str_replace(colnames(country_score), "pov_1016", "(I1) *Extreme poverty headcount %")
colnames(country_score)<-str_replace(colnames(country_score), "SL.TLF.CACT.FE.ZS", "(I2) Female labor participation %")
colnames(country_score)<-str_replace(colnames(country_score), "HD.HCI.OVRL", "(I3) Human Capital Index")
colnames(country_score)<-str_replace(colnames(country_score), "SI.POV.GINI", "(I1) *Gini Index")
colnames(country_score)<-str_replace(colnames(country_score), "SE.SEC.ENRR", "(I3) Secondary school enrollment %")
colnames(country_score)<-str_replace(colnames(country_score), "SH.IMM.IDPT", "(I3) Immunization DPT %")
colnames(country_score)<-str_replace(colnames(country_score), "account.t.d.7", "(I1) Account ownership (poorest 40%)")
colnames(country_score)<-str_replace(colnames(country_score), "LGBT_acc", "(I2) LGBT Acceptance Index")
colnames(country_score)<-str_replace(colnames(country_score), "wbl", "(I2) Women, Business & Law Index")
colnames(country_score)<-str_replace(colnames(country_score), "ref_idp", "(I1) *Refugees & IDPs index")
colnames(country_score)<-str_replace(colnames(country_score), "SG.GEN.PARL.ZS", "(I2) Women in national parliaments %")
colnames(country_score)<-str_replace(colnames(country_score), "EG.ELC.ACCS.ZS", "(I4) Access to electricity %")
colnames(country_score)<-str_replace(colnames(country_score), "acc_sani_SDG", "(I4) Basic access to sanitation %")
colnames(country_score)<-str_replace(colnames(country_score), "acc_water_SDG", "(I4) Basic access to water %")
colnames(country_score)<-str_replace(colnames(country_score), "rai", "(I4) Rural Access Index")
colnames(country_score)<-str_replace(colnames(country_score), "SH.UHC.SRVS.CV.XD", "(I3) Universal health coverage (UHC) index %")



#Sustainability
colnames(country_score)<-str_replace(colnames(country_score), "EN.ATM.PM25.MC.M3", "(S1) *PM2.5 mean annual exposure (\U00B5g/m3)")
colnames(country_score)<-str_replace(colnames(country_score), "forest_loss", "(S4) *Forest loss %")
colnames(country_score)<-str_replace(colnames(country_score), "EG.FEC.RNEW.ZS", "(S3) Renewable energy consumption %")
colnames(country_score)<-str_replace(colnames(country_score), "wat_qua", "(S3) Water Quality SDG 6.3")
colnames(country_score)<-str_replace(colnames(country_score), "WWT.new", "(S2) Wastewater treated (primary) %")
colnames(country_score)<-str_replace(colnames(country_score), "waste_managed", "(S2) Solid waste properly disposed %")
colnames(country_score)<-str_replace(colnames(country_score), "waste_rate", "(S2) *Municipal solid waste (kg/pc/day)")
colnames(country_score)<-str_replace(colnames(country_score), "BHV.new", "(S4) Biodiversity Habitat Index")
colnames(country_score)<-str_replace(colnames(country_score), "FSH.new", "(S4) Fisheries Index")
colnames(country_score)<-str_replace(colnames(country_score), "ghg_pc", "(S1) *GHG emissions per capita (% change)")
colnames(country_score)<-str_replace(colnames(country_score), "EN.ATM.CO2E.PC", "(S1) *CO2 emissions (MT pc)")
colnames(country_score)<-str_replace(colnames(country_score), "ecos_04_NDG", "(S3) *Ecological Footprint")
colnames(country_score)<-str_replace(colnames(country_score), "fao_withdraw_pc", "(S3) *Water withdrawal per capita (m3/year pc)")
colnames(country_score)<-str_replace(colnames(country_score), "chloroph_SDG", "(S4) *Chlorophyll-a deviations in coastal water %")
colnames(country_score)<-str_replace(colnames(country_score), "SH.STA.AIRP.P5", "(S1) *Mortality due to air pollution (per 100,000)")
colnames(country_score)<-str_replace(colnames(country_score), "SH.STA.WASH.P5", "(S2) *Mortality due to unsafe WASH services (per 100,000)")


#Efficiency
colnames(country_score)<-str_replace(colnames(country_score), "agri_land", "(E4) Agri. land productivity ($/ha)")
colnames(country_score)<-str_replace(colnames(country_score), "agri_value", "(E1) Agri. value added per worker")
colnames(country_score)<-str_replace(colnames(country_score), "gdp_ghg", "(E4) Total GDP/GHG emissions")
colnames(country_score)<-str_replace(colnames(country_score), "gov_effect", "(E2) Governance effectiveness")
colnames(country_score)<-str_replace(colnames(country_score), "cont_corr", "(E2) Control of corruption")
colnames(country_score)<-str_replace(colnames(country_score), "reg_qua", "(E2) Regulatory quality")
colnames(country_score)<-str_replace(colnames(country_score), "lpi_score", "(E1) Logistic Performance Index")
colnames(country_score)<-str_replace(colnames(country_score), "IT.NET.USER.ZS", "(E3) Individuals using internet %")
colnames(country_score)<-str_replace(colnames(country_score), "IT.CEL.SETS.P2", "(E3) Mobile cellular subscriptions (per 100 people)")
colnames(country_score)<-str_replace(colnames(country_score), "rule_law", "(E2) Rule of law")
colnames(country_score)<-str_replace(colnames(country_score), "rapid_trans", "(E3) Rapid transit to resident ratio (km/million)")
colnames(country_score)<-str_replace(colnames(country_score), "EG.EGY.PRIM.PP.KD", "(E4) *Energy intensity (MJ/$)")
colnames(country_score)<-str_replace(colnames(country_score), "patents", "(E1) Patents (per 100,000 people)")  
colnames(country_score)<-str_replace(colnames(country_score), "dai", "(E1) Digital Penetration Index")  
colnames(country_score)<-str_replace(colnames(country_score), "water_efficiency_GDP", "(E4) Water productivity (GDP/m3)")
colnames(country_score)<-str_replace(colnames(country_score), "IS.SHP.GCNW.XQ", "(E3) Shipping connectivity index")

  


mean_reg_score<- country_score %>%
  group_by(region)%>%
    dplyr::summarise(across(where(is.numeric), function(x){mean(x, na.rm=TRUE)}))

mean_reg_score <- mean_reg_score %>%
  filter(region=='Middle East & North Africa')


atatat <- data.frame("MENA region","MENA","Upper middle income")
colnames(atatat) <- c("country","iso3","income")

mean_reg_score <- cbind(mean_reg_score,atatat)


country_score <- rbind(country_score, mean_reg_score)


for(i in country){
country_score <- country_score[country_score$iso3 == "MENA", ]
country_score <- as.data.frame(t(as.matrix(country_score)))
country_score <- country_score %>% rownames_to_column("indicator")
colnames(country_score)<-c("indicator", "score")
country_score$category <- ifelse(country_score$indicator %in% efficiency, '4.Efficiency',
                                   ifelse(country_score$indicator %in% sustainability, '3.Sustainability',
                                          ifelse(country_score$indicator %in% resilience, '1.Resilience', 
                                                 ifelse(country_score$indicator %in% inclusion, '2.Inclusion', 'Other'))))



country_score <- country_score%>% filter(category!='Other') 

#Join percentage and raw value
country_score <-left_join(country_score, country_values, by="indicator")
country_score$raw_value<-as.numeric(as.character(country_score$raw_value))
country_score$raw_value<-format(round(country_score$raw_value, 2), nsmall = 2)

# Format score data for graphs

country_score$score <- as.numeric(as.character(country_score$score))
country_score$score<-country_score$score*100
country_score <- country_score[order(country_score$category),]

#Create the second database for graph pillars (regional/income)

#Get inverse values for score graph - For the individual pillars graphs we need to get the value of the indicator and the inverse value, to create the circular graph as an stacked plot #in the score_graph_data, score will be the inverse value and 
country_score$score <- with(country_score, (100-score))
country_score$values <- with(country_score, (100-score))

country_score$score <- as.integer(country_score$score)
country_score$values <- as.integer(country_score$values)

write.csv(country_score, paste0(dir_out, group,'/',"MENA_score_graphs.csv"), row.names = FALSE)

}
```


<!-- # Loop to GET MEDIAN/MEAN and SD values per MENA region to compare with ECA and SA median -->
<!-- ```{r} -->
<!-- #Use raw data to compare -->
<!-- country_val<- read.csv(file=paste0(dir_out, group,'/',"MENA","_percentil.csv"), header=TRUE, sep=",")%>% -->
<!--   select(-percentil) -->


<!-- #country_aspi -->
<!-- income_info_country<-income_info%>% -->
<!--   filter(region_red == "SA" | region_red == "ECA") -->

<!-- income_info_country<-left_join(income_info_country, country_val, by="indicator") -->
<!-- income_info_country<-income_info_country%>% -->
<!--   filter(!is.na(category))%>% -->
<!--   arrange(region_red, category) -->

<!-- income_info_country$raw_value<-as.numeric(as.character(income_info_country$raw_value)) -->

<!-- income_info_country<-income_info_country %>%  -->
<!--  mutate_if(is.numeric, round, digits=1) -->

<!-- #Create categorical category to use the conditional formatting in excel: -->
<!-- # 3 indicator above one standard deviation from the mean  -->
<!-- # 2 indicator within one standard deviation from the mean -->
<!-- # 1 indicator below one standard deviation  -->
<!-- # This function also revert the values for indicators in which a higher number means worse performing) -->
<!-- #For MEAN -->
<!-- income_info_country<-income_info_country%>% -->
<!--  mutate(mean_flag = ifelse(str_detect(indicator, "\\*") & raw_value > sd_mean_up , "1", -->
<!--                             ifelse(raw_value > sd_mean_up, "3", -->
<!--                             ifelse(raw_value <= sd_mean_up & raw_value >= sd_mean_down, "2", -->
<!--                             ifelse(str_detect(indicator, "\\*") & raw_value < sd_mean_down, "3", -->
<!--                             ifelse(raw_value < sd_mean_down, "1", "Error")))))) -->
<!-- #For MEDIAN  -->
<!-- income_info_country<-income_info_country%>% -->
<!--  mutate(median_flag = ifelse(str_detect(indicator, "\\*") & raw_value > sd_median_up , "1", -->
<!--                             ifelse(raw_value > sd_median_up, "3", -->
<!--                             ifelse(raw_value <= sd_median_up & raw_value >= sd_median_down, "2", -->
<!--                             ifelse(str_detect(indicator, "\\*") & raw_value < sd_median_down, "3", -->
<!--                             ifelse(raw_value < sd_median_down, "1", "Error")))))) -->

<!-- #Arrange to easily modify in excel  -->
<!-- income_info_country<-income_info_country%>% -->
<!--   dplyr::select("category", "region_red", "indicator", "raw_value", "median_flag",  "median") -->

<!-- write.csv(income_info_country,paste0(dir_out, group,'/',"MENA_tables_data.csv"), row.names = FALSE) -->


<!-- ``` -->

# Loop to prepare data for PERCENTIL RANKING GRAPH - CIRCULAR (ALL PILLARS- Global data)
```{r}

# Load dataset from data generated in the previous section
  country_percent <- read.csv(file=paste0(dir_out, group,'/',"MENA_percentil.csv"), header=TRUE, sep=",")

  
  
data3<-country_percent

#Arrange data and filter NA
data3 <- data3 %>% 
  filter(!is.na(percentil))%>% 
  arrange(category, percentil)
data3$id <- seq(1, nrow(data3))

#Create labels for each column and angles (no need to adjust. With this method labels are aligned automatically)
label_data3 <- data3
number_of_bar3 <- nrow(label_data3)
angle3 <- 90 - 360 * (label_data3$id-0.5) /number_of_bar3     # I substract 0.5 because the letter must have the angle of the center of the bars. Not extreme right(1) or extreme left (0)
label_data3$hjust <- ifelse(angle3 < -90, 1, 0)
label_data3$angle <- ifelse(angle3 < -90, angle3+180, angle3)

# prepare a data frame for pillars names
base_data3 <- data3 %>% 
  group_by(category) %>% 
  dplyr::summarize(start=min(id), end=max(id)) %>% 
  rowwise() %>% 
  mutate(title=mean(c(start, end)))

#Remove numbers to the  pillar category name 
base_data3$category2<-str_replace(base_data3$category, "1.|2.|3.|4.", "")

#Paste indicators labels with  percentil rank values (ej, 35.- Labor market)
label_data3$test <- paste(data3$percentil, "-", data3$indicator)

com <- ggplot(data3) +      
  
  # Add the stacked bar
  geom_bar(aes(x=as.factor(id), y=percentil, fill=category, colour=category), stat="identity", alpha=0.7, size=0.2) +
  #colors used by the CEO in their first draft of the benchmarking
  #scale_fill_manual(values=c("hotpink1","gold1","steelblue2", "green3")) +
  scale_fill_manual(values=c("red2" ,"darkmagenta", "goldenrod1","darkcyan"))+
  scale_colour_manual(values=c("black","black", "black","black")) +
  
    geom_label(x = 0, y = -50, label = i, hjust=0.5, fontface="bold", size=7) +
  
  ylim(-50,120) +
  theme_minimal() +
  theme(
    legend.position = "none",
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = margin(-3,-3,-3,-3, "cm") 
  ) +
  coord_polar() +
  
  ####Remember to put a if that makes it smaller for v2  PLACEHOLDER 
  
   # Add labels on top of each bar
  geom_text(data=label_data3, aes(x=id, y=percentil+2, label= str_wrap(test, width = 20), hjust=label_data3$hjust), color="black", fontface="bold",alpha=1, size=perctext, angle= label_data3$angle, inherit.aes = FALSE ) +

  # Add base line information
geom_segment(data=base_data3, aes(x = start, y = -5, xend = end, yend = -5), colour = "black", alpha=0.8, size=0.6 , inherit.aes = FALSE )  +
  geom_text(data=base_data3, aes(x = title, y = -18, label=category2), hjust=c(0.5,0.5,0.5,0.5), angle=c(-60, 15, -65, 40), colour = "black", alpha=0.8, size=4, fontface="bold", inherit.aes = FALSE)


ggsave(com, file=paste0(dir_out, group,'/',"MENA_percentil_global.pdf"), width=12, height=13)

```



#Graphs per pillars (RISE) - SUSTAINABILITY
```{r}
    ##########
  # Sustainability#    #Different set of indicators for V0 AND V1
    ##########

for(i in country){
# Load dataset with country scores generated in the previous section
  country_score <- read.csv(file=paste0(dir_out, group,'/',i,"_score_graphs.csv"), header=TRUE, sep=",")
  

#Split data for graphs 
country_score_graph1 <- country_score %>% filter(category== '3.Sustainability')

data2<-country_score_graph1
data2$order <- seq(1, nrow(data2))

# Move order column to the front so it does not get rejected when transforming to long format (column necessary to keep order of dimensions for the graph)
data2 <- data2 %>% 
  filter(!is.na(score))%>%
  select(order, everything())

# Transform data in a tidy format (long format)
data2 <- stats::reshape(data2, 
                direction = "long",
                varying = c("score", "values"),
                v.names = "value",
                idvar = c("order", "indicator", "category", "raw_value"),
                timevar = "observation",
                times = 1:2)

# Set a number of 'empty bar' to add at the end of each group
empty_bar <- 2
nObsType <- nlevels(as.factor(data2$observation))
to_add <- data.frame( matrix(NA, empty_bar*nlevels(as.factor(data2$category))*nObsType*.5, ncol(data2)))
colnames(to_add) <- colnames(data2)
to_add$category <- rep(levels(as.factor(data2$category)), each=empty_bar*nObsType*.5 )
data2 <- rbind(data2, to_add)

grpid = function(x) match(x, unique(x))
data2 <- data2 %>% mutate(group_id = group_indices(., category) %>% grpid)

#To group inverse and no inverse value
data2<- data2 %>% mutate(group_order=case_when(
  group_id == 1 ~ "A",
  TRUE ~ NA_character_ # all else are NA
))

data2 <- data2[order(data2$indicator),]

data2$id <- rep( seq(1, nrow(data2)/nObsType) , each=nObsType)

#Create labels for each column and angles (no need to adjust. With this method labels are aligned automatically)
label_data2 <- data2 %>% dplyr::group_by(id, indicator, raw_value) %>% dplyr::summarize(tot=sum(value))
number_of_bar2 <- nrow(label_data2)
angle2 <- 90 - 360 * (label_data2$id-0.5) /number_of_bar2     # I substract 0.5 because the letter must have the angle of the center of the bars. Not extreme right(1) or extreme left (0)
label_data2$hjust <- ifelse(angle2 < -90, 1, 0)
label_data2$angle <- ifelse(angle2 < -90, angle2+180, angle2)

# prepare a data frame for base lines
base_data2 <- data2 %>% 
  group_by(group_order) %>% 
  dplyr::summarize(start=min(id), end=max(id) 
            - empty_bar
          ) %>% 
  rowwise() %>% 
  mutate(title=mean(c(start, end)))

# prepare a data frame for grid (scales)
grid_data2 <- base_data2
grid_data2$end <- grid_data2$end[ c( nrow(grid_data2), 1:nrow(grid_data2)-1)] + 1.4
grid_data2$start <- grid_data2$start - .4
#grid_data2 <- grid_data2[-1,]

#Paste categories and raw values

data2$inv  <- ifelse(grepl("\\) \\*",data2$indicator), 1, 0)
data2$inv[is.na(data2$indicator)] <- NA

data2$cat <- paste(data2$observation,data2$group_order,data2$inv)

label_data2$ind_value<-paste(label_data2$raw_value, "-", label_data2$indicator)



s <- ggplot(data2) +      
  
  # Add the stacked bar
  geom_bar(aes(x=as.factor(id), y=value, fill=cat, colour=cat), stat="identity", alpha=0.5, size=0.2) +
  #scale_fill_manual(values=c("white","steelblue1")) +
  scale_fill_manual(values=c("white","white","goldenrod1","lightgoldenrod1")) +
  scale_colour_manual(values=c("black","black","black","black")) +

  # Add a val=100/75/50/25 lines. I do it at the beginning to make sur barplots are OVER it.
  #geom_segment(data=grid_data2, aes(x = end, y = 100, xend = start, yend = 100), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data2, aes(x = end, y = 80, xend = start, yend = 80), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data2, aes(x = end, y = 60, xend = start, yend = 60), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data2, aes(x = end, y = 40, xend = start, yend = 40), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data2, aes(x = end, y = 20, xend = start, yend = 20), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  
    geom_label(x = 0, y = 0, label = i, hjust=0.5, fontface="bold", size=10) +
    annotate("text", x = rep(max(data2$id),5), y = c(20, 40, 60, 80, 100), label = c("20", "40", "60", "80", "100") , color="grey", size=5 , angle=0, fontface="bold", hjust=.5) +
  
  ylim(0 , 120) +
  theme_minimal() +
  theme(
    legend.position = "none",
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = margin(-3,-3,-3,-3, "cm") 
  ) +
  coord_polar() +
  
   # Add labels on top of each bar
  
  geom_text(data=label_data2, aes(x=id, y=tot-50, label= str_wrap(ind_value, width = 22), hjust=label_data2$hjust), color="black", fontface="bold",alpha=1, size=pillartext, angle= label_data2$angle, inherit.aes = FALSE ) 


ggsave(s, file=paste0(dir_out, group,'/',i,"_score_graph_sust.png"), width=10, height=10)
ggsave(s, file=paste0(dir_out, group,'/',i,"_score_graph_sust.pdf"), width=10, height=10)


}
```


# Graphs per pillars (RISE) -INCLUSION
```{r}
      ##########
     # Inclusion #    #Different set of indicators for V0 AND V1
      ##########

#detach(package:plyr)
  
for(i in country){
# Load dataset with country scores generated in the previous section
  country_score <- read.csv(file=paste0(dir_out, group,'/',i,"_score_graphs.csv"), header=TRUE, sep=",")



#Split data for graphs 
country_score_graph2 <- country_score %>% filter(category== '2.Inclusion')

data2<-country_score_graph2
data2$order <- seq(1, nrow(data2))

# Move order column to the front so it does not get rejected when transforming to long format (column necessary to keep order of dimensions for the graph)
data2 <- data2 %>% 
  filter(!is.na(score))%>%
  select(order, everything())

# Transform data in a tidy format (long format)
data2 <- stats::reshape(data2, 
                direction = "long",
                varying = c("score", "values"),
                v.names = "value",
                idvar = c("order", "indicator", "category", "raw_value"),
                timevar = "observation",
                times = 1:2)

# Set a number of 'empty bar' to add at the end of each group
empty_bar <- 2
nObsType <- nlevels(as.factor(data2$observation))
to_add <- data.frame( matrix(NA, empty_bar*nlevels(as.factor(data2$category))*nObsType*.5, ncol(data2)))
colnames(to_add) <- colnames(data2)
to_add$category <- rep(levels(as.factor(data2$category)), each=empty_bar*nObsType*.5 )
data2 <- rbind(data2, to_add)

grpid = function(x) match(x, unique(x))
data2 <- data2 %>% mutate(group_id = group_indices(., category) %>% grpid)

#To group inverse and no inverse value
data2<- data2 %>% mutate(group_order=case_when(
  group_id == 1 ~ "A",
  TRUE ~ NA_character_ # all else are NA
))

data2 <- data2[order(data2$indicator),]

data2$id <- rep( seq(1, nrow(data2)/nObsType) , each=nObsType)

#Create labels for each column and angles (no need to adjust. With this method labels are aligned automatically)
label_data2 <- data2 %>% dplyr::group_by(id, indicator, raw_value) %>% dplyr::summarize(tot=sum(value))
number_of_bar2 <- nrow(label_data2)
angle2 <- 90 - 360 * (label_data2$id-0.5) /number_of_bar2     # I substract 0.5 because the letter must have the angle of the center of the bars. Not extreme right(1) or extreme left (0)
label_data2$hjust <- ifelse(angle2 < -90, 1, 0)
label_data2$angle <- ifelse(angle2 < -90, angle2+180, angle2)

# prepare a data frame for base lines
base_data2 <- data2 %>% 
  group_by(group_order) %>% 
  dplyr::summarize(start=min(id), end=max(id) 
            - empty_bar
          ) %>% 
  rowwise() %>% 
  mutate(title=mean(c(start, end)))

# prepare a data frame for grid (scales)
grid_data2 <- base_data2
grid_data2$end <- grid_data2$end[ c( nrow(grid_data2), 1:nrow(grid_data2)-1)] + 1.4
grid_data2$start <- grid_data2$start - .4
#grid_data2 <- grid_data2[-1,]

#Paste categories and raw values
data2$inv  <- ifelse(grepl("\\) \\*",data2$indicator), 1, 0)
data2$inv[is.na(data2$indicator)] <- NA

data2$cat <- paste(data2$observation,data2$group_order,data2$inv)
label_data2$ind_value<-paste(label_data2$raw_value, "-", label_data2$indicator)

inc <- ggplot(data2) +      
  
  # Add the stacked bar
  geom_bar(aes(x=as.factor(id), y=value, fill=cat, colour=cat), stat="identity", alpha=0.5, size=0.2) +
  #scale_fill_manual(values=c("white","hotpink1")) +
  scale_fill_manual(values=c("white","white","red2","coral")) +
  scale_colour_manual(values=c("black","black","black","black")) +

  # Add a val=100/75/50/25 lines. I do it at the beginning to make sur barplots are OVER it.
  #geom_segment(data=grid_data2, aes(x = end, y = 100, xend = start, yend = 100), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data2, aes(x = end, y = 80, xend = start, yend = 80), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data2, aes(x = end, y = 60, xend = start, yend = 60), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data2, aes(x = end, y = 40, xend = start, yend = 40), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data2, aes(x = end, y = 20, xend = start, yend = 20), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  
    geom_label(x = 0, y = 0, label = i, hjust=0.5, fontface="bold", size=10) +
    annotate("text", x = rep(max(data2$id),5), y = c(20, 40, 60, 80, 100), label = c("20", "40", "60", "80", "100") , color="grey", size=5 , angle=0, fontface="bold", hjust=.5) +
  
  ylim(0 , 120) +
  theme_minimal() +
  theme(
    legend.position = "none",
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = margin(-3,-3,-3,-3, "cm") 
  ) +
  coord_polar() +
  
   # Add labels on top of each bar
  
  geom_text(data=label_data2, aes(x=id, y=tot-50, label= str_wrap(ind_value, width = 22), hjust=label_data2$hjust), color="black", fontface="bold",alpha=1, size=pillartext, angle= label_data2$angle, inherit.aes = FALSE ) 


ggsave(inc, file=paste0(dir_out, group,'/',i,"_score_graph_incl.png"), width=10, height=10)
ggsave(inc, file=paste0(dir_out, group,'/',i,"_score_graph_incl.pdf"), width=10, height=10)

}

```


# Graphs per pillars (RISE) - Efficiency
```{r}
    ##########
# 2. Efficiency  # Same set of indicators for V0 and V1 (still using version control in case the indicators change)
    ##########
#detach(package:plyr)
  
for(i in country){
# Load dataset with country scores generated in the previous section
  country_score <- read.csv(file=paste0(dir_out, group,'/',i,"_score_graphs.csv"), header=TRUE, sep=",")




#Split data for graphs 
country_score_graph2 <- country_score %>% filter(category== '4.Efficiency')

data2<-country_score_graph2
data2$order <- seq(1, nrow(data2))

# Move order column to the front so it does not get rejected when transforming to long format (column necessary to keep order of dimensions for the graph)
data2 <- data2 %>% 
  filter(!is.na(score))%>%
  select(order, everything())

# Transform data in a tidy format (long format)
data2 <- stats::reshape(data2, 
                direction = "long",
                varying = c("score", "values"),
                v.names = "value",
                idvar = c("order", "indicator", "category", "raw_value"),
                timevar = "observation",
                times = 1:2)

# Set a number of 'empty bar' to add at the end of each group
empty_bar <- 2
nObsType <- nlevels(as.factor(data2$observation))
to_add <- data.frame( matrix(NA, empty_bar*nlevels(as.factor(data2$category))*nObsType*.5, ncol(data2)))
colnames(to_add) <- colnames(data2)
to_add$category <- rep(levels(as.factor(data2$category)), each=empty_bar*nObsType*.5 )
data2 <- rbind(data2, to_add)

grpid = function(x) match(x, unique(x))
data2 <- data2 %>% mutate(group_id = group_indices(., category) %>% grpid)

#To group inverse and no inverse value
data2<- data2 %>% mutate(group_order=case_when(
  group_id == 1 ~ "A",
  TRUE ~ NA_character_ # all else are NA
))

data2 <- data2[order(data2$indicator),]

data2$id <- rep( seq(1, nrow(data2)/nObsType) , each=nObsType)

#Create labels for each column and angles (no need to adjust. With this method labels are aligned automatically)
label_data2 <- data2 %>% dplyr::group_by(id, indicator, raw_value) %>% dplyr::summarize(tot=sum(value))
number_of_bar2 <- nrow(label_data2)
angle2 <- 90 - 360 * (label_data2$id-0.5) /number_of_bar2     # I substract 0.5 because the letter must have the angle of the center of the bars. Not extreme right(1) or extreme left (0)
label_data2$hjust <- ifelse(angle2 < -90, 1, 0)
label_data2$angle <- ifelse(angle2 < -90, angle2+180, angle2)

# prepare a data frame for base lines
base_data2 <- data2 %>% 
  group_by(group_order) %>% 
  dplyr::summarize(start=min(id), end=max(id) 
            - empty_bar
          ) %>% 
  rowwise() %>% 
  mutate(title=mean(c(start, end)))

# prepare a data frame for grid (scales)
grid_data2 <- base_data2
grid_data2$end <- grid_data2$end[ c( nrow(grid_data2), 1:nrow(grid_data2)-1)] + 1.4
grid_data2$start <- grid_data2$start - .4
#grid_data2 <- grid_data2[-1,]

#Paste categories and raw values
data2$inv  <- ifelse(grepl("\\) \\*",data2$indicator), 1, 0)
data2$inv[is.na(data2$indicator)] <- NA

data2$cat <- paste(data2$observation,data2$group_order,data2$inv)
label_data2$ind_value<-paste(label_data2$raw_value, "-", label_data2$indicator)

e <- ggplot(data2) +      
  
  # Add the stacked bar
  geom_bar(aes(x=as.factor(id), y=value, fill=cat, colour=cat), stat="identity", alpha=0.5, size=0.2) +
  #scale_fill_manual(values=c("white","gold1")) +
  scale_fill_manual(values=c("white","white","darkmagenta","plum")) +
  scale_colour_manual(values=c("black","black","black","black")) +

  # Add a val=100/75/50/25 lines. I do it at the beginning to make sur barplots are OVER it.
  #geom_segment(data=grid_data2, aes(x = end, y = 100, xend = start, yend = 100), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data2, aes(x = end, y = 80, xend = start, yend = 80), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data2, aes(x = end, y = 60, xend = start, yend = 60), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data2, aes(x = end, y = 40, xend = start, yend = 40), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data2, aes(x = end, y = 20, xend = start, yend = 20), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  
    geom_label(x = 0, y = 0, label = i, hjust=0.5, fontface="bold", size=10) +
    annotate("text", x = rep(max(data2$id),5), y = c(20, 40, 60, 80, 100), label = c("20", "40", "60", "80", "100") , color="grey", size=5 , angle=0, fontface="bold", hjust=.5) +
  
  ylim(0 , 120) +
  theme_minimal() +
  theme(
    legend.position = "none",
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = margin(-3,-3,-3,-3, "cm") 
  ) +
  coord_polar() +
  
   # Add labels on top of each bar
  
  geom_text(data=label_data2, aes(x=id, y=tot-50, label= str_wrap(ind_value, width = 22), hjust=label_data2$hjust), color="black", fontface="bold",alpha=1, size=pillartext, angle= label_data2$angle, inherit.aes = FALSE ) 


ggsave(e, file=paste0(dir_out, group,'/',i,"_score_graph_eff.png"), width=10, height=10)
ggsave(e, file=paste0(dir_out, group,'/',i,"_score_graph_eff.pdf"), width=10, height=10)

}
```



#Graphs per pillars (RISE) - Resilience
```{r}
    ##########
#   RESILIENCE #    # Same set of indicators for V0 and V1 (still using version control in case it indicators change)
    ##########
#detach(package:plyr)
  
for(i in country){
# Load dataset with country scores generated in the previous section
  country_score <- read.csv(file=paste0(dir_out, group,'/',i,"_score_graphs.csv"), header=TRUE, sep=",")

  
  
##### Resilience #######

#Split data for graphs 
country_score_graph2 <- country_score %>% filter(category== '1.Resilience')

data2<-country_score_graph2
data2$order <- seq(1, nrow(data2))

# Move order column to the front so it does not get rejected when transforming to long format (column necessary to keep order of dimensions for the graph)
data2 <- data2 %>% 
  filter(!is.na(score))%>%
  select(order, everything())

# Transform data in a tidy format (long format)
data2 <- stats::reshape(data2, 
                direction = "long",
                varying = c("score", "values"),
                v.names = "value",
                idvar = c("order", "indicator", "category", "raw_value"),
                timevar = "observation",
                times = 1:2)

# Set a number of 'empty bar' to add at the end of each group
empty_bar <- 2
nObsType <- nlevels(as.factor(data2$observation))
to_add <- data.frame( matrix(NA, empty_bar*nlevels(as.factor(data2$category))*nObsType*.5, ncol(data2)))
colnames(to_add) <- colnames(data2)
to_add$category <- rep(levels(as.factor(data2$category)), each=empty_bar*nObsType*.5 )
data2 <- rbind(data2, to_add)

grpid = function(x) match(x, unique(x))
data2 <- data2 %>% mutate(group_id = group_indices(., category) %>% grpid)

#To group inverse and no inverse value
data2<- data2 %>% mutate(group_order=case_when(
  group_id == 1 ~ "A",
  TRUE ~ NA_character_ # all else are NA
))

data2 <- data2[order(data2$indicator),]

data2$id <- rep( seq(1, nrow(data2)/nObsType) , each=nObsType)

#Create labels for each column and angles (no need to adjust. With this method labels are aligned automatically)
label_data2 <- data2 %>% dplyr::group_by(id, indicator, raw_value) %>% dplyr::summarize(tot=sum(value))
number_of_bar2 <- nrow(label_data2)
angle2 <- 90 - 360 * (label_data2$id-0.5) /number_of_bar2     # I substract 0.5 because the letter must have the angle of the center of the bars. Not extreme right(1) or extreme left (0)
label_data2$hjust <- ifelse(angle2 < -90, 1, 0)
label_data2$angle <- ifelse(angle2 < -90, angle2+180, angle2)

# prepare a data frame for base lines
base_data2 <- data2 %>% 
  group_by(group_order) %>% 
  dplyr::summarize(start=min(id), end=max(id) 
            - empty_bar
          ) %>% 
  rowwise() %>% 
  mutate(title=mean(c(start, end)))

# prepare a data frame for grid (scales)
grid_data2 <- base_data2
grid_data2$end <- grid_data2$end[ c( nrow(grid_data2), 1:nrow(grid_data2)-1)] + 1.4
grid_data2$start <- grid_data2$start - .4
#grid_data2 <- grid_data2[-1,]

#Paste categories and raw values
data2$inv  <- ifelse(grepl("\\) \\*",data2$indicator), 1, 0)
data2$inv[is.na(data2$indicator)] <- NA

data2$cat <- paste(data2$observation,data2$group_order,data2$inv)

label_data2$ind_value<-paste(label_data2$raw_value, "-", label_data2$indicator)

r <- ggplot(data2) +      
  
  # Add the stacked bar
  geom_bar(aes(x=as.factor(id), y=value, fill=cat, colour=cat), stat="identity", alpha=0.5, size=0.2) +
  #scale_fill_manual(values=c("white","green3")) +
  scale_fill_manual(values=c("white","white","darkcyan","lightblue2")) +
  scale_colour_manual(values=c("black","black","black","black")) +

  # Add a val=100/75/50/25 lines. I do it at the beginning to make sur barplots are OVER it.
  #geom_segment(data=grid_data2, aes(x = end, y = 100, xend = start, yend = 100), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data2, aes(x = end, y = 80, xend = start, yend = 80), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data2, aes(x = end, y = 60, xend = start, yend = 60), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data2, aes(x = end, y = 40, xend = start, yend = 40), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data2, aes(x = end, y = 20, xend = start, yend = 20), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  
    geom_label(x = 0, y = 0, label = i, hjust=0.5, fontface="bold", size=10) +
    annotate("text", x = rep(max(data2$id),5), y = c(20, 40, 60, 80, 100), label = c("20", "40", "60", "80", "100") , color="grey", size=5 , angle=0, fontface="bold", hjust=.5) +
  
  ylim(0 , 120) +
  theme_minimal() +
  theme(
    legend.position = "none",
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = margin(-3,-3,-3,-3, "cm") 
  ) +
  coord_polar() +
  
   # Add labels on top of each bar
  
  geom_text(data=label_data2, aes(x=id, y=tot-50, label= str_wrap(ind_value, width = 22), hjust=label_data2$hjust), color="black", fontface="bold",alpha=1, size=pillartext, angle= label_data2$angle, inherit.aes = FALSE ) 


ggsave(r, file=paste0(dir_out, group,'/',i,"_score_graph_res.png"), width=10, height=10)
ggsave(r, file=paste0(dir_out, group,'/',i,"_score_graph_res.pdf"), width=10, height=10)

}

```


#Density plot for Morocco in IDP due to natural disasters
```{r}

country_all <- read.csv(paste0(dir_int,"World_SD_values_V5_index",version,".csv"))

ddd <- country_all %>% filter(income=="Lower middle income")

# compute mean salary
mean_var <- ddd %>% 
  pull(displaced) %>% 
  mean(na.rm=T) %>%
  signif(6)

med_var <- ddd %>% 
  pull(displaced) %>% 
  median(na.rm=T) %>%
  signif(6)


r <- ggplot(ddd, aes(x=displaced)) +
    geom_density(alpha=.5, fill="tomato3") +
    geom_vline(xintercept=mean_var,  colour="tomato2",linetype="dashed", size=1) +
      geom_vline(xintercept=med_var,  colour="tomato1",linetype="dashed", size=1) +
   geom_text(size=4,aes(x=mean_var+80, label=paste0("Mean\n",mean_var), y=0.003)) +
  geom_text(size=4,aes(x=med_var+80, label=paste0("Median\n",med_var), y=0.004)) +
    xlab("IDPs due to natural disasters (cases per 100,000)") +
  theme_minimal()


ggsave(r, file=paste0(dir_out,'/',"MAR_idpdistasters.png"), width=16, height=8)


```